---
title: "ASE Definition Comparison: Site-Level Analysis"

format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    theme: cosmo
    embed-resources: true
    fig-width: 9
    fig-height: 6
execute:
  warning: false
  message: false
  echo: true
---

# Overview

This document implements the pre-specified analysis for the ASE Definition Comparison study. Sites should run this document from top to bottom without modification. All outputs are saved to the directory specified by `output_directory` in `clif_config.json` for return to the coordinating center.

**Study Question:** Does hospital-level lactate ordering intensity explain the gap between core and extended CDC Adult Sepsis Event (ASE) rates?

**Design:**

- **Exposure:** Lactate ordering intensity (orders per 1,000 patient-days), hospital-year level
- **Outcome:** Two separate binary logistic models on one-row-per-hospitalization data:
  - **Model A:** `sepsis_core` (1) vs `no_sepsis` (0)
  - **Model B:** `sepsis_extended` (1) vs `no_sepsis` (0)
- **Primary estimand:** Contrast between `lactate_vol_scaled` coefficient in Model B minus Model A — does the gap between definitions widen at higher-testing hospitals?
- **Contrast SE:** Conservative approximation `sqrt(Var_B + Var_A)` — assumes independence between models; slightly wider than exact SE since positive cross-model covariance is not subtracted
**Required data file:** `analysis_dataset.parquet` in the `phi_directory` specified in `clif_config.json`


---

# Section 0 — Setup

```{r setup}
library(tidyverse)
library(lme4)       # glmer() — binary logistic with RE (multi-hospital path)
library(sandwich)   # vcovCL() — clustered SEs (single-hospital path)
library(lmtest)     # coeftest()
library(jsonlite)
library(arrow)
library(here)
library(broom)
library(broom.mixed)  # tidy() for glmerMod objects (glmer path)
library(scales)
library(knitr)
library(patchwork)  # combine panels for fig_framing_comparison

set.seed(20240101)

# ── Site configuration (from clif_config.json) ────────────────────────────────
config     <- fromJSON(here("clif_config.json"))
SITE_ID    <- config$site_name
DATA_PATH  <- here(config$phi_directory, "analysis_dataset.parquet")
OUTPUT_DIR <- here(config$output_directory)
# ─────────────────────────────────────────────────────────────────────────────

# Create output directories
dir.create(file.path(OUTPUT_DIR, "figures"),     showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "tables"),      showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "diagnostics"), showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "models"),      showWarnings = FALSE, recursive = TRUE)

# ── Helper functions ──────────────────────────────────────────────────────────

# Fit a single binary logistic model (glmer or glm) with consistent error/warning handling. Returns NULL on error.
# warn_var:   name of variable in parent frame to store convergence warning
fit_binary <- function(formula, data, model_path, warn_var = "fit_warning") {
  assign(warn_var, NULL, envir = parent.frame())

  if (model_path == "glmer") {
    withCallingHandlers(
      tryCatch(
        glmer(formula, data = data, family = binomial,
              control = glmerControl(optimizer = "bobyqa",
                                     optCtrl   = list(maxfun = 2e5))),
        error = function(e) { warning(e$message); NULL }
      ),
      warning = function(w) {
        assign(warn_var, w$message, envir = parent.frame(3))
        message(warn_var, " WARNING: ", w$message)
        invokeRestart("muffleWarning")
      }
    )
  } else {
    tryCatch(
      glm(formula, data = data, family = binomial),
      error = function(e) { warning(e$message); NULL }
    )
  }
}

# Extract vcov from a fitted model.
# glmer: model-based vcov from GLMM likelihood (fixed effects only).
# glm:   cluster-robust HC0 vcov via sandwich::vcovCL on hospitalization_id.
#        Subsets cluster vector to rows actually used in model fit (NA-safe).
get_model_vcov <- function(model, model_path, data) {
  if (model_path == "glmer") {
    as.matrix(vcov(model))
  } else {
    used_rows <- as.integer(rownames(model.frame(model)))
    sandwich::vcovCL(model,
                     cluster = data$hospitalization_id[used_rows],
                     type    = "HC0")
  }
}

# Tidy a fitted glmer or glm model into a clean data frame.
# Returns NULL if model is NULL.
#   SEs are model-based from the GLMM likelihood; vcov_mat is still returned by get_model_vcov() and used downstream in compute_contrast().

tidy_binary <- function(model, vcov_mat) {
  if (is.null(model)) return(NULL)

  if (inherits(model, "glmerMod")) {
    broom.mixed::tidy(model, effects = "fixed") %>%
      select(term, estimate, std.error, statistic, p.value) %>%
      mutate(conf.low  = estimate - 1.96 * std.error,
             conf.high = estimate + 1.96 * std.error)
  } else {
    broom::tidy(lmtest::coeftest(model, vcov = vcov_mat)) %>%
      mutate(conf.low  = estimate - 1.96 * std.error,
             conf.high = estimate + 1.96 * std.error)
  }
}

# Compute primary contrast from two tidy coefficient tables.
# contrast = lactate_vol_scaled coef(model_b) - coef(model_a)
compute_contrast <- function(coef_a, coef_b, vcov_a, vcov_b,
                             lactate_term = "lactate_vol_scaled") {
  if (is.null(coef_a) || is.null(coef_b)) return(NULL)

  est_a <- coef_a %>% filter(term == lactate_term) %>% pull(estimate)
  est_b <- coef_b %>% filter(term == lactate_term) %>% pull(estimate)

  if (length(est_a) == 0 || length(est_b) == 0) {
    warning("compute_contrast: '", lactate_term, "' not found in one or both models.")
    return(NULL)
  }

  contrast_est <- est_b - est_a

  # SE from vcov diagonal — conservative (ignores cross-model covariance)
  var_a <- tryCatch(vcov_a[lactate_term, lactate_term],
                    error = function(e) NA_real_)
  var_b <- tryCatch(vcov_b[lactate_term, lactate_term],
                    error = function(e) NA_real_)
  contrast_se <- sqrt(var_a + var_b)

  tibble(
    contrast_estimate    = contrast_est,
    contrast_se          = contrast_se,
    contrast_ci_low      = contrast_est - 1.96 * contrast_se,
    contrast_ci_high     = contrast_est + 1.96 * contrast_se,
    contrast_z           = contrast_est / contrast_se,
    contrast_p           = 2 * pnorm(abs(contrast_est / contrast_se),
                                     lower.tail = FALSE),
    se_approximation     = "conservative — cross-model covariance not subtracted",
    lactate_coef_model_a = est_a,
    lactate_coef_model_b = est_b
  )
}

# Add standard metadata columns to a tidy coefficient table
add_metadata <- function(coef_df, model_version, site_id, n_hospitals,
                         n_hospitalizations, lactate_center, lactate_scale,
                         year_center, centering_method, zero_var_covariates,
                         warn_a = NULL, warn_b = NULL) {
  coef_df %>%
    mutate(
      site_id               = site_id,
      model_version         = model_version,
      n_hospitals           = n_hospitals,
      n_hospitalizations    = n_hospitalizations,
      lactate_mean          = lactate_center,
      lactate_sd            = lactate_scale,
      year_center           = year_center,
      centering_method      = centering_method,
      dropped_covariates    = paste(zero_var_covariates, collapse = ", "),
      convergence_warn_a    = !is.null(warn_a),
      convergence_warn_b    = !is.null(warn_b)
    )
}

# Helper: write CSV only if object is non-null and non-empty.
# Emits a loud warning when skipped rather than failing silently — a missing
# export file should always be traceable to a printed reason, not discovered
# later during a pre-distribution review (see SA2b, internal run 2026).
write_if <- function(x, path) {
  if (!is.null(x) && is.data.frame(x) && nrow(x) > 0) {
    write_csv(x, path)
  } else {
    warning("write_if: skipped writing ", basename(path),
            " — object is NULL, not a data frame, or zero-row.")
  }
}

# Extract between-hospital random-intercept variance from a glmer fit.
# Returns a one-row tibble with RE sigma^2 and sigma (SD).
# glm path (single-hospital): returns a stub row with NAs and re_available = FALSE.
# Used for two-level heterogeneity reporting at the coordinating center:
#   - Within-site between-hospital variance (this export, multi-hospital sites)
#   - Between-site variance (from meta-analytic pooling of contrast estimates)
extract_re_variance <- function(model, model_label, model_path, site_id) {
  if (model_path == "glmer" && !is.null(model)) {
    vc      <- as.data.frame(VarCorr(model))
    re_row  <- vc[vc$grp == "hospital_id_deident", ]
    tibble(
      site_id      = site_id,
      model_label  = model_label,
      re_sigma2    = if (nrow(re_row) > 0) re_row$vcov[1]  else NA_real_,
      re_sigma     = if (nrow(re_row) > 0) re_row$sdcor[1] else NA_real_,
      re_available = nrow(re_row) > 0
    )
  } else {
    tibble(
      site_id      = site_id,
      model_label  = model_label,
      re_sigma2    = NA_real_,
      re_sigma     = NA_real_,
      re_available = FALSE
    )
  }
}

# Load data
df_raw <- read_parquet(DATA_PATH)

cat("Data loaded:", nrow(df_raw), "rows,", ncol(df_raw), "columns\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")
```

---

# Section 1 — Data Quality Checks

```{r data-quality}
# 1.1 Overall structure
cat("Rows:", nrow(df_raw), "\n")
cat("Columns:", ncol(df_raw), "\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")

# 1.2 Missing data
missing_summary <- df_raw %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(pct_missing = round(n_missing / nrow(df_raw) * 100, 1)) %>%
  filter(n_missing > 0)

cat("\nMissing data summary (variables with any missing):\n")
print(missing_summary)

baseline_completeness <- df_raw %>%
  summarise(
    n                     = n(),
    age_miss              = sum(is.na(age)),
    sex_miss              = sum(is.na(sex)),
    cci_miss              = sum(is.na(cci)),
    sofa_miss             = sum(is.na(worst_sofa_admission_to_24h)),
    hosp_type_miss        = sum(is.na(hospital_type)),
    lactate_vol_miss      = sum(is.na(lactate_order_per_1000_patient_days)),
    year_miss             = sum(is.na(year)),
    ASE_miss              = sum(is.na(ASE)),
    defined_w_lactic_miss = sum(is.na(defined_w_lactic)),
    race_eth_miss         = sum(is.na(race_category) |
                                    tolower(race_category) %in%
                                      c("unknown", "not reported", "nan") |
                                    is.na(ethnicity_category) |
                                    tolower(ethnicity_category) %in%
                                      c("unknown", "not reported", "other", "nan")),
    lactate_window_miss   = sum(is.na(lactate_ordered_in_window)),
    los_miss              = sum(is.na(hospital_los_days)),
    in_hosp_death_miss    = sum(is.na(in_hospital_death))
  )

kable(baseline_completeness, caption = "Baseline completeness — key analysis variables")
# Export deferred to Section 6.2 (SITE_ID-prefixed write) — do not write here,
# this was previously duplicating the file under an un-prefixed name.

# 1.3 Structure
cat("\nData structure:\n")
str(df_raw)

# 1.4 Two-row structure check (expected pre-pivot)
row_counts <- df_raw %>%
  count(hospitalization_id) %>%
  count(n, name = "n_encounters")

cat("\nRows per hospitalization_id in raw data (expect all = 2):\n")
kable(row_counts, caption = "Expected: all hospitalizations should have exactly 2 rows")
```

---

# Section 2 — Derived Variables & Wide Format Pivot

```{r analysis-parameters}
# Analysis parameters — modify only with PI approval and SAP amendment ─────────
MIN_HOSP_YEAR_N <- 100  # Minimum hospitalizations per hospital-year for inclusion.
                        # Hospital-years below this threshold are excluded before
                        # all downstream analyses. Pre-specified in SAP §2.3.
cat(paste("Minimum hospital-year N threshold:", MIN_HOSP_YEAR_N, "\n"))
```

```{r derived-variables}
# 2.1 Pivot to wide — one row per hospitalization ──────────────────────────────
# patient_group:
#   sepsis_core         ASE=1 core AND ASE=1 extended (logically required)
#   sepsis_extended     ASE=0 core, ASE=1 extended — captured only by lactate criterion
#   no_sepsis           ASE=0 both definitions
#   check_data_quality  ASE=1 core, ASE=0 extended — logically impossible; flagged then dropped

df_wide <- df_raw %>%
  select(hospitalization_id, hospital_id, defined_w_lactic, ASE,
         lactate_order_per_1000_patient_days, worst_sofa_admission_to_24h,
         age, sex, cci, race_category, ethnicity_category, race_ethnicity,
         hospital_type, year, hospitalizations_from_ed_per_year,
         any_lactate_ordered_whole_hospitalization, lactate_ordered_in_window,
         hospital_los_days, had_icu, icu_los_days, in_hospital_death) %>%
  pivot_wider(
    id_cols      = c(hospitalization_id, hospital_id,
                     lactate_order_per_1000_patient_days,
                     worst_sofa_admission_to_24h, age, sex, cci,
                     race_category, ethnicity_category, race_ethnicity,
                     hospital_type, year, hospitalizations_from_ed_per_year,
                     any_lactate_ordered_whole_hospitalization,
                     lactate_ordered_in_window, hospital_los_days,
                     had_icu, icu_los_days, in_hospital_death),
    names_from   = defined_w_lactic,
    values_from  = ASE,
    names_prefix = "ASE_def_"
  ) %>%
  mutate(
    patient_group = case_when(
      ASE_def_0 == 1 & ASE_def_1 == 1 ~ "sepsis_core",
      ASE_def_0 == 0 & ASE_def_1 == 1 ~ "sepsis_extended",
      ASE_def_0 == 0 & ASE_def_1 == 0 ~ "no_sepsis",
      ASE_def_0 == 1 & ASE_def_1 == 0 ~ "check_data_quality",
      TRUE                             ~ NA_character_
    )
  )

cat("Wide format: one row per hospitalization\n")
cat("Total hospitalizations:", nrow(df_wide), "\n")

# 2.2 QC table — flag check_data_quality before exclusion ──────────────────────
n_check_dq <- sum(df_wide$patient_group == "check_data_quality", na.rm = TRUE)
cat(paste("\ncheck_data_quality encounters:", n_check_dq, "\n"))

qc_primary <- df_wide %>%
  mutate(patient_group = factor(patient_group,
                                levels = c("no_sepsis", "sepsis_core",
                                           "sepsis_extended", "check_data_quality"))) %>%
  count(patient_group, .drop = FALSE) %>%
  mutate(
    framing               = "primary_mutually_exclusive",
    pct                   = round(n / sum(n) * 100, 2),
    included_in_analysis  = patient_group != "check_data_quality"
  )

qc_alt <- df_wide %>%
  mutate(patient_group_alt = case_when(
           patient_group == "check_data_quality" ~ "check_data_quality",
           patient_group == "no_sepsis"          ~ "no_sepsis",
           TRUE                                  ~ "ase_extended_any"
         ),
         patient_group_alt = factor(patient_group_alt,
                                    levels = c("no_sepsis", "ase_extended_any",
                                               "check_data_quality"))) %>%
  count(patient_group_alt, .drop = FALSE) %>%
  rename(patient_group = patient_group_alt) %>%
  mutate(
    framing               = "alt_extended_def1",
    pct                   = round(n / sum(n) * 100, 2),
    included_in_analysis  = patient_group != "check_data_quality"
  )

qc_table <- bind_rows(qc_primary, qc_alt) %>%
  select(framing, patient_group, n, pct, included_in_analysis)

kable(qc_table, caption = "Patient group distribution including QC flag (pre-exclusion), primary + alt framing")
write_csv(qc_table,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_02_patient_group_qc.csv")))

if (n_check_dq > 0)
  warning(n_check_dq, " check_data_quality encounters excluded. ",
          "Review data pipeline if unexpectedly large.")

# 2.3 Exclude check_data_quality and set factor levels ─────────────────────────
df <- df_wide %>%
  filter(patient_group != "check_data_quality") %>%
  mutate(
    patient_group  = factor(patient_group,
                            levels = c("no_sepsis", "sepsis_core", "sepsis_extended")),
    # Alt framing grouping, matching Section 4b's alternative Model B definition
    # (ASE_def_1==1 vs no_sepsis): collapses sepsis_core + sepsis_extended into
    # one "meets any extended-definition criterion" group. 
    
    patient_group_alt = factor(
      ifelse(patient_group == "no_sepsis", "no_sepsis", "ase_extended_any"),
      levels = c("no_sepsis", "ase_extended_any")
    ),
    hospital_type  = factor(hospital_type, levels = c("community", "academic")),
    sex            = factor(sex,           levels = c("Male", "Female")),
    year_f         = factor(year),
  
    
    race_eth_model = case_when(
      is.na(ethnicity_category) |
        tolower(ethnicity_category) %in% c("unknown", "not reported",
                                            "other", "nan")           ~ NA_character_,
      is.na(race_category) |
        tolower(race_category) %in% c("unknown", "not reported",
                                       "nan")                          ~ NA_character_,
      tolower(ethnicity_category) == "hispanic"                        ~ "Hispanic",
      tolower(ethnicity_category) %in% c("non-hispanic",
                                          "not hispanic") &
        tolower(race_category) == "white"                              ~ "NH_White",
      tolower(ethnicity_category) %in% c("non-hispanic",
                                          "not hispanic") &
        tolower(race_category) %in% c("black or african american",
                                       "black", "african american",
                                       "black or african-american")    ~ "NH_Black",
      tolower(ethnicity_category) %in% c("non-hispanic",
                                          "not hispanic") &
        tolower(race_category) == "asian"                              ~ NA_character_,
      tolower(ethnicity_category) %in% c("non-hispanic",
                                          "not hispanic")              ~ NA_character_,
      TRUE                                                             ~ NA_character_
    ),
    race_eth_model = factor(race_eth_model,
                            levels = c("NH_White", "NH_Black", "Hispanic"))
  )

cat(paste("Analytic dataset after exclusions:", nrow(df), "hospitalizations\n"))

# race_eth_model distribution check
cat("\nrace_eth_model distribution (derived from race_category + ethnicity_category):\n")
df %>%
  count(race_eth_model, .drop = FALSE) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  print(n = 10)

# 2.4 Minimum hospital-year volume threshold ────────────────────────────────────

hosp_year_n <- df %>%
  count(hospital_id, year, name = "n_hosp_year")

excluded_hosp_years <- hosp_year_n %>%
  filter(n_hosp_year < MIN_HOSP_YEAR_N)

if (nrow(excluded_hosp_years) > 0) {
  cat(paste0("\nHospital-year threshold exclusions (N < ",
             MIN_HOSP_YEAR_N, "):\n"))
  cat(paste0("  Excluded: ", nrow(excluded_hosp_years),
             " hospital-year(s), ",
             sum(excluded_hosp_years$n_hosp_year), " hospitalizations\n"))
  cat(paste0("  Retained: ",
             nrow(hosp_year_n) - nrow(excluded_hosp_years),
             " of ", nrow(hosp_year_n), " hospital-years\n"))
  print(excluded_hosp_years)
} else {
  cat(paste0("\nAll hospital-years meet minimum threshold (N >= ",
             MIN_HOSP_YEAR_N, "). No exclusions.\n"))
}

df <- df %>%
  left_join(hosp_year_n, by = c("hospital_id", "year")) %>%
  filter(n_hosp_year >= MIN_HOSP_YEAR_N) %>%
  select(-n_hosp_year)

cat(paste("Analytic dataset after hospital-year threshold:",
          nrow(df), "hospitalizations\n"))

# 2.5 ASE flag consistency cross-check ─────────────────────────────────────────
# Expected patterns:
#   sepsis_extended + window_lactate=0 → IMPOSSIBLE: classified as lactate-only
#     ASE but no lactate drawn in window. Flag as data quality concern.
#   sepsis_extended + window_lactate=1 → Expected ~100% of sepsis_extended.
#   sepsis_core    + window_lactate=0 → Fine: qualified via core criteria; no
#     window lactate drawn or ordered outside window.
#   sepsis_core    + window_lactate=1 → Fine: core criteria met; lactate also
#     drawn in window (overlap patients — both pathways active).
#   no_sepsis      + window_lactate=0 → Structural non-observability: lactate
#     criterion could never have been triggered regardless of result.
#   no_sepsis      + window_lactate=1 → True negative opportunity: lactate
#     drawn in window but result did not meet criterion (or was not elevated).
```

```{r ase-flag-crosscheck}
# Cross-tab: patient_group × lactate_ordered_in_window
flag_crosscheck <- df %>%
  count(patient_group, lactate_ordered_in_window) %>%
  group_by(patient_group) %>%
  mutate(
    pct    = round(n / sum(n) * 100, 1),
    cell   = paste0(n, " (", pct, "%)")
  ) %>%
  ungroup() %>%
  select(patient_group, lactate_ordered_in_window, cell) %>%
  pivot_wider(
    names_from   = lactate_ordered_in_window,
    values_from  = cell,
    names_prefix = "window_lactate_"
  ) %>%
  mutate(
    total = df %>%
      count(patient_group) %>%
      pull(n)
  )

kable(flag_crosscheck,
      caption = paste0(
        "ASE group × lactate_ordered_in_window cross-check. ",
        "sepsis_extended patients in window_lactate_0 column indicate a ",
        "data quality concern — lactate-only ASE without window lactate draw."
      ))

# Flag: sepsis_extended patients with no window lactate
n_extended_no_window <- df %>%
  filter(patient_group == "sepsis_extended",
         lactate_ordered_in_window == 0) %>%
  nrow()

if (n_extended_no_window > 0) {
  warning(
    n_extended_no_window,
    " sepsis_extended patients have lactate_ordered_in_window == 0. ",
    "These patients are classified as lactate-only ASE but have no lactate ",
    "draw recorded in the ±2 day ASE window. Review upstream phenotyping — ",
    "possible window definition mismatch between compute_ase() and ",
    "lactate_ordered_in_window derivation."
  )

  
  extended_no_window_diag <- df %>%
    filter(patient_group == "sepsis_extended",
           lactate_ordered_in_window == 0) %>%
    mutate(
      likely_cause = if_else(
        any_lactate_ordered_whole_hospitalization == 1,
        "window_boundary_mismatch_lactate_drawn_elsewhere_in_hosp",
        "no_lactate_order_in_hospitalization_at_all_check_compute_ase"
      )
    ) %>%
    select(hospitalization_id, hospital_id, year,
           any_lactate_ordered_whole_hospitalization,
           lactate_ordered_in_window, likely_cause)

  cat("\nBreakdown of sepsis_extended/no-window-lactate cases by likely cause:\n")
  print(table(extended_no_window_diag$likely_cause))

} else {
  cat("ASE flag check PASSED: all sepsis_extended patients have window lactate draw.\n")
}

# Mechanism stratification summary — no_sepsis subgroups
mech_summary <- df %>%
  filter(patient_group == "no_sepsis") %>%
  count(lactate_ordered_in_window) %>%
  mutate(
    subgroup = case_when(
      lactate_ordered_in_window == 0 ~ "Structural non-observability (lactate not drawn in window)",
      lactate_ordered_in_window == 1 ~ "True negative opportunity (lactate drawn, criterion not met)"
    ),
    pct = round(n / sum(n) * 100, 1)
  ) %>%
  select(subgroup, n, pct)

cat("\nno_sepsis mechanism breakdown:\n")
kable(mech_summary,
      caption = paste0(
        "no_sepsis patients stratified by window lactate observability. ",
        "Structural non-observability = lactate criterion could never have ",
        "been triggered. True negative = lactate drawn but result did not ",
        "meet criterion."
      ))

# Overlap diagnostic: sepsis_core patients with window lactate (both pathways)
n_core_with_window_lactate <- df %>%
  filter(patient_group == "sepsis_core",
         lactate_ordered_in_window == 1) %>%
  nrow()

n_core_total <- sum(df$patient_group == "sepsis_core")

cat(paste0(
  "\nsepsis_core overlap check: ",
  n_core_with_window_lactate, " of ", n_core_total,
  " (", round(n_core_with_window_lactate / n_core_total * 100, 1), "%)",
  " core patients also had lactate drawn in window",
  " — these are the Section 4c overlap group candidates.\n"
))

# 2.6 Collinearity diagnostic: lactate volume vs year ──────────────────────────
# Computed at hospital-year level (one observation per hospital-year).
# Patient-level computation inflates N artificially — every patient in a
# hospital-year shares the same lactate_order value, so the effective N
# is the number of distinct hospital-year combinations, not hospitalizations.
cor_lactate_year_data <- df %>%
  distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
  filter(!is.na(lactate_order_per_1000_patient_days))

cor_lactate_year <- cor(cor_lactate_year_data$lactate_order_per_1000_patient_days,
                        cor_lactate_year_data$year)

cat(paste("\nPearson r (lactate_order_per_1000_patient_days ~ year, hospital-year level):",
          round(cor_lactate_year, 3), "\n"))
cat(paste("N hospital-year obs used for r:", nrow(cor_lactate_year_data), "\n"))
if (abs(cor_lactate_year) > 0.7)
  warning("r > 0.7 — strong collinearity. Review SA3 (centered lactate) carefully.")

# 2.7 Hospital count and modeling path ─────────────────────────────────────────
n_hospitals      <- n_distinct(df$hospital_id)
re_structure     <- ifelse(n_hospitals >= 2, "glmer_re",            "glm_clustered_se")
model_path       <- ifelse(n_hospitals >= 2, "glmer",               "glm")
interaction_type <- ifelse(n_hospitals >= 2, "between_hospital",    "within_hospital_temporal")

cat(paste("Number of hospitals:", n_hospitals, "\n"))
cat(paste("Modeling path:", re_structure, "\n"))
cat(paste("Interaction type:", interaction_type, "\n"))

# 2.8 Within-year centering for SA3 ───────────────────────────────────────────
if (n_hospitals >= 2) {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    group_by(year) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    ) %>%
    ungroup()
  centering_method <- "within_year"
} else {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    )
  centering_method <- "grand_mean"
  cat("Single-hospital site: grand-mean centering used for SA3.\n")
}

df <- df %>%
  left_join(
    hospital_year_stats %>%
      select(hospital_id, year, lactate_volume_centered, lactate_volume_year_mean),
    by = c("hospital_id", "year")
  )

n_missing_centered <- sum(is.na(df$lactate_volume_centered))
if (n_missing_centered > 0)
  warning(n_missing_centered, " rows missing lactate_volume_centered after join. ",
          "SA3 will run on reduced sample.")

cat(paste("Centering method:", centering_method, "\n"))

# 2.9 Hospital de-identification ───────────────────────────────────────────────
hosp_crosswalk <- df %>%
  distinct(hospital_id) %>%
  arrange(hospital_id) %>%
  mutate(hospital_id_deident = row_number())

cat("\nHospital de-identification crosswalk (local reference — not exported):\n")
print(hosp_crosswalk)
cat("DO NOT share hospital identity mapping with the coordinating center.\n")

df <- df %>% left_join(hosp_crosswalk, by = "hospital_id")
cat(paste("De-identified IDs assigned:", n_distinct(df$hospital_id_deident), "hospitals\n"))
```

```{r hosp-year-crosstab}
# 2.10 Patient group composition by hospital-year ───────────────────────────────
crosstab_primary <- df %>%
  count(hospital_id_deident, year, patient_group) %>%
  group_by(hospital_id_deident, year) %>%
  mutate(total_hosp_year = sum(n),
         pct             = round(n / total_hosp_year * 100, 1),
         framing         = "primary_mutually_exclusive") %>%
  ungroup() %>%
  rename(group = patient_group)

crosstab_alt <- df %>%
  count(hospital_id_deident, year, patient_group_alt) %>%
  group_by(hospital_id_deident, year) %>%
  mutate(total_hosp_year = sum(n),
         pct             = round(n / total_hosp_year * 100, 1),
         framing         = "alt_extended_def1") %>%
  ungroup() %>%
  rename(group = patient_group_alt)

hosp_year_group_crosstab <- bind_rows(crosstab_primary, crosstab_alt) %>%
  select(hospital_id_deident, year, framing, group, n, total_hosp_year, pct) %>%
  arrange(hospital_id_deident, year, framing, group)

kable(hosp_year_group_crosstab,
      caption = paste0(
        "Patient group composition by hospital-year, primary + alt framing. ",
        "sepsis_extended proportion > 50% of total ASE-positive patients ",
        "is flagged as anomalous (primary framing only, see flag below)."
      ))

# Flag anomalous hospital-years
n_ase_hosp_year <- df %>%
  filter(patient_group != "no_sepsis") %>%
  count(hospital_id_deident, year, patient_group) %>%
  group_by(hospital_id_deident, year) %>%
  mutate(pct_of_ase = n / sum(n) * 100) %>%
  ungroup()

flagged_hosp_years <- n_ase_hosp_year %>%
  filter(patient_group == "sepsis_extended", pct_of_ase > 50)

if (nrow(flagged_hosp_years) > 0) {
  warning(nrow(flagged_hosp_years),
          " hospital-year(s) have sepsis_extended > 50% of total ASE. ",
          "Review upstream phenotyping for these hospital-years.")
  cat("\nFlagged hospital-years:\n")
  print(flagged_hosp_years)
} else {
  cat("Hospital-year group composition check PASSED: no anomalous sepsis_extended proportions.\n")
}

# Export
write_csv(hosp_year_group_crosstab,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_04_patient_group_hosp_year_crosstab.csv")))
```

---

# Section 3 — Descriptive Statistics

```{r descriptives}
# 3.1 Cohort summary
cohort_summary <- df %>%
  summarise(
    n_hospitalizations  = n(),
    n_hospitals         = n_distinct(hospital_id_deident),
    n_years             = n_distinct(year),
    year_range          = paste(min(year), max(year), sep = "-"),
    median_age          = median(age,  na.rm = TRUE),
    pct_female          = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
    median_cci          = median(cci,  na.rm = TRUE),
    pct_academic        = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1),
    n_sepsis_core       = sum(patient_group == "sepsis_core"),
    n_sepsis_extended   = sum(patient_group == "sepsis_extended"),
    n_no_sepsis         = sum(patient_group == "no_sepsis"),
    pct_sepsis_core     = round(mean(patient_group == "sepsis_core")     * 100, 1),
    pct_sepsis_extended = round(mean(patient_group == "sepsis_extended") * 100, 1)
  )

kable(cohort_summary, caption = "Overall cohort summary")

# 3.2 Patient group distribution — long format, primary + alt framing
group_summary_primary <- df %>%
  count(patient_group) %>%
  mutate(pct = round(n / sum(n) * 100, 1),
         framing = "primary_mutually_exclusive") %>%
  rename(group = patient_group)

group_summary_alt <- df %>%
  count(patient_group_alt) %>%
  mutate(pct = round(n / sum(n) * 100, 1),
         framing = "alt_extended_def1") %>%
  rename(group = patient_group_alt)

group_summary <- bind_rows(group_summary_primary, group_summary_alt) %>%
  select(framing, group, n, pct)

kable(group_summary, caption = "Patient group distribution (analytic dataset), primary + alt framing")

# 3.3 ASE rate by year
ase_rate_by_year <- df %>%
  group_by(year) %>%
  summarise(
    n                   = n(),
    n_sepsis_core       = sum(patient_group == "sepsis_core"),
    n_sepsis_extended   = sum(patient_group == "sepsis_extended"),
    pct_sepsis_core     = round(mean(patient_group == "sepsis_core")     * 100, 1),
    pct_sepsis_extended = round(mean(patient_group == "sepsis_extended") * 100, 1),
    gap_pct_points      = pct_sepsis_extended - pct_sepsis_core,
    .groups             = "drop"
  )

kable(ase_rate_by_year, caption = "ASE rate by year and definition")

# 3.4 Hospital-year lactate volume summary (year-level)
hosp_year_summary <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days) %>%
  group_by(year) %>%
  summarise(
    n_hospitals      = n(),
    mean_lactate_vol = round(mean(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    sd_lactate_vol   = round(sd(lactate_order_per_1000_patient_days,   na.rm = TRUE), 1),
    min_lactate_vol  = round(min(lactate_order_per_1000_patient_days,  na.rm = TRUE), 1),
    max_lactate_vol  = round(max(lactate_order_per_1000_patient_days,  na.rm = TRUE), 1),
    .groups          = "drop"
  )

kable(hosp_year_summary, caption = "Hospital-year lactate volume summary")

# 3.5 Clinical profile by patient group (sepsis cases only)
# Shared summary builder so primary (sepsis_core, sepsis_extended) and alt
# (ase_extended_any, the combined group) framings compute identical metrics
# from one definition instead of two copies of this block drifting apart.
clinical_profile_summary <- function(data, group_var) {
  data %>%
    group_by({{ group_var }}) %>%
    summarise(
      n                    = n(),
      median_age           = median(age, na.rm = TRUE),
      pct_female           = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
      median_cci           = median(cci, na.rm = TRUE),
      median_sofa_24h      = median(worst_sofa_admission_to_24h, na.rm = TRUE),
      pct_academic         = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1),
      # Race/ethnicity — model levels
      pct_nh_white         = round(mean(race_eth_model == "NH_White",  na.rm = TRUE) * 100, 1),
      pct_nh_black         = round(mean(race_eth_model == "NH_Black",  na.rm = TRUE) * 100, 1),
      pct_hispanic         = round(mean(race_eth_model == "Hispanic",  na.rm = TRUE) * 100, 1),
      # Descriptive only — NH_Asian and NH_Other excluded from adjusted models
      # for cross-site consistency; reported here for Table 1
      pct_nh_asian         = round(mean(!is.na(race_category) &
                                          tolower(ethnicity_category) %in%
                                            c("non-hispanic", "not hispanic") &
                                          tolower(race_category) == "asian",
                                        na.rm = TRUE) * 100, 1),
      pct_nh_other         = round(mean(!is.na(race_category) &
                                          tolower(ethnicity_category) %in%
                                            c("non-hispanic", "not hispanic") &
                                          !tolower(race_category) %in%
                                            c("white", "black or african american",
                                              "black", "african american",
                                              "black or african-american", "asian",
                                              "unknown", "not reported", "nan"),
                                        na.rm = TRUE) * 100, 1),
      pct_race_eth_missing = round(mean(is.na(race_eth_model)) * 100, 1),
      median_hospital_los  = median(hospital_los_days, na.rm = TRUE),
      pct_had_icu          = round(mean(had_icu == 1, na.rm = TRUE) * 100, 1),
      median_icu_los       = median(icu_los_days[had_icu == 1], na.rm = TRUE),
      pct_in_hosp_death    = round(mean(in_hospital_death == 1, na.rm = TRUE) * 100, 1),
      .groups              = "drop"
    ) %>%
    rename(group = {{ group_var }}) %>%
    pivot_longer(-group, names_to = "metric", values_to = "value")
}

group_clinical_primary <- df %>%
  filter(patient_group %in% c("sepsis_core", "sepsis_extended")) %>%
  clinical_profile_summary(patient_group) %>%
  mutate(framing = "primary_mutually_exclusive")

# Alt framing: the single combined "meets any extended-definition criterion"
# group, for comparison against the primary core/extended split
group_clinical_alt <- df %>%
  filter(patient_group_alt == "ase_extended_any") %>%
  clinical_profile_summary(patient_group_alt) %>%
  mutate(framing = "alt_extended_def1")

group_clinical <- bind_rows(group_clinical_primary, group_clinical_alt) %>%
  select(framing, group, metric, value)

kable(group_clinical, caption = "Clinical profile by patient group (sepsis cases only), primary + alt framing, long format")

# 3.6 Hospital-year lactate detail (one row per hospital per year)
hosp_year_detail <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days) %>%
  arrange(hospital_id_deident, year) %>%
  rename(lactate_vol = lactate_order_per_1000_patient_days)

kable(hosp_year_detail, caption = "Hospital-year lactate volume detail (de-identified)")

# 3.7 Hospital-year ASE rates (one row per hospital per year)
# Long format: primary framing carries both patient groups plus the core/extended
# applies with only one non-reference group, so that column is NA for alt rows).
hosp_year_ase_primary <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    n_hospitalizations = n(),
    n_group             = sum(patient_group == "sepsis_extended"),
    n_group_core        = sum(patient_group == "sepsis_core"),
    pct_group           = round(mean(patient_group == "sepsis_extended") * 100, 1),
    pct_group_core      = round(mean(patient_group == "sepsis_core")     * 100, 1),
    gap_pct_points       = pct_group - pct_group_core,
    .groups              = "drop"
  ) %>%
  mutate(framing = "primary_mutually_exclusive", group = "sepsis_extended")

hosp_year_ase_alt <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    n_hospitalizations = n(),
    n_group             = sum(patient_group_alt == "ase_extended_any"),
    pct_group           = round(mean(patient_group_alt == "ase_extended_any") * 100, 1),
    .groups              = "drop"
  ) %>%
  mutate(framing = "alt_extended_def1", group = "ase_extended_any",
         n_group_core = NA_integer_, pct_group_core = NA_real_,
         gap_pct_points = NA_real_)

hosp_year_ase <- bind_rows(hosp_year_ase_primary, hosp_year_ase_alt) %>%
  select(hospital_id_deident, year, framing, group, n_hospitalizations,
         n_group, pct_group, n_group_core, pct_group_core, gap_pct_points) %>%
  arrange(hospital_id_deident, year, framing)

kable(hosp_year_ase, caption = "Hospital-year ASE rates, primary + alt framing (de-identified)")
```

```{r fig-lactate-trend, fig.height=5.5}
# 3.8 Figure: Lactate ordering intensity over time
hosp_year_plot_data <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days)

site_mean_by_year <- hosp_year_plot_data %>%
  group_by(year) %>%
  summarise(site_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
            .groups = "drop")

ase_rate_plot <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    rate_core     = mean(patient_group == "sepsis_core",     na.rm = TRUE),
    rate_extended = mean(patient_group == "sepsis_extended", na.rm = TRUE),
    .groups = "drop"
  )

lactate_range <- range(hosp_year_plot_data$lactate_order_per_1000_patient_days, na.rm = TRUE)
scale_factor  <- diff(lactate_range)
scale_offset  <- lactate_range[1]

fig_lactate_trend <- ggplot() +
  geom_line(data  = hosp_year_plot_data,
            aes(x = year, y = lactate_order_per_1000_patient_days,
                group = hospital_id_deident),
            color = "steelblue", alpha = 0.45, linewidth = 0.6) +
  geom_point(data = hosp_year_plot_data,
             aes(x = year, y = lactate_order_per_1000_patient_days,
                 group = hospital_id_deident),
             color = "steelblue", alpha = 0.45, size = 1.2) +
  geom_line(data  = site_mean_by_year,
            aes(x = year, y = site_mean),
            color = "steelblue", linewidth = 1.2) +
  geom_point(data = site_mean_by_year,
             aes(x = year, y = site_mean),
             color = "steelblue", size = 2.2) +
  geom_line(data  = ase_rate_plot,
            aes(x = year, y = rate_core * scale_factor + scale_offset,
                group = hospital_id_deident),
            color = "firebrick", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  geom_line(data  = ase_rate_plot,
            aes(x = year, y = rate_extended * scale_factor + scale_offset,
                group = hospital_id_deident),
            color = "darkorange", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  scale_y_continuous(
    name     = "Lactate Orders per 1,000 Patient-Days",
    sec.axis = sec_axis(transform = ~ (. - scale_offset) / scale_factor,
                        name      = "ASE Rate (proportion)")
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Lactate Ordering Intensity and ASE Rate Over Time (", SITE_ID, ")"),
       subtitle = "Blue = lactate volume (solid = site mean); Red dashed = core ASE rate; Orange dashed = extended ASE rate",
       x = "Year") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        axis.title.y.left  = element_text(color = "steelblue"),
        axis.text.y.left   = element_text(color = "steelblue"),
        axis.title.y.right = element_text(color = "firebrick"),
        axis.text.y.right  = element_text(color = "firebrick"))

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig1_lactate_ase_trend.png")),
       plot = fig_lactate_trend, width = 9, height = 5.5, dpi = 300)
fig_lactate_trend
```

```{r fig-ase-gap}
# 3.9 Figure: ASE rate gap over time
ase_gap_by_hosp_year <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    pct_core     = mean(patient_group == "sepsis_core",     na.rm = TRUE) * 100,
    pct_extended = mean(patient_group == "sepsis_extended", na.rm = TRUE) * 100,
    gap          = pct_extended - pct_core,
    .groups      = "drop"
  )

fig_ase_gap <- ggplot() +
  { if (n_hospitals > 1)
    geom_line(data  = ase_gap_by_hosp_year,
              aes(x = year, y = gap, group = hospital_id_deident),
              color = "grey65", alpha = 0.5, linewidth = 0.6)
  } +
  geom_line(data  = ase_rate_by_year,
            aes(x = year, y = gap_pct_points),
            color = "darkorchid", linewidth = 1.2) +
  geom_point(data = ase_rate_by_year,
             aes(x = year, y = gap_pct_points),
             color = "darkorchid", size = 2.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Extended vs Core ASE Rate Gap Over Time (", SITE_ID, ")"),
       subtitle = "Gap = extended minus core ASE rate (pp)\nGrey = individual hospitals; Purple = site mean",
       x = "Year", y = "ASE Rate Gap (percentage points)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"), panel.grid.minor = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig2_ase_rate_gap.png")),
       plot = fig_ase_gap, width = 8, height = 5, dpi = 300)
fig_ase_gap
```

```{r fig-group-dist}
# 3.10 Figure: Patient group distribution

fig_group_dist <- group_summary %>%
  filter(framing == "primary_mutually_exclusive") %>%
  mutate(patient_group = factor(group,
                                levels = c("no_sepsis", "sepsis_core", "sepsis_extended"),
                                labels = c("No Sepsis", "Core Sepsis", "Extended Only"))) %>%
  ggplot(aes(x = patient_group, y = pct, fill = patient_group)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = paste0(pct, "%\n(n=", scales::comma(n), ")")),
            vjust = -0.4, size = 3.5) +
  scale_fill_manual(values = c("No Sepsis"     = "grey75",
                               "Core Sepsis"   = "firebrick",
                               "Extended Only" = "darkorange")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  labs(title    = paste0("Patient Group Distribution (", SITE_ID, ")"),
       subtitle = paste0("N = ", scales::comma(nrow(df)), " unique encounters"),
       x = NULL, y = "Percentage of Encounters (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        panel.grid.major.x = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig3_patient_group_distribution.png")),
       plot = fig_group_dist, width = 7, height = 5, dpi = 300)
fig_group_dist
```

```{r fig-clinical-profile}
# 3.11 Figure: Clinical profile comparison
# group_clinical is long format (framing x group x metric x value) as of the
# alt-framing update — this figure compares the two primary-framing groups
# (sepsis_core vs sepsis_extended); the alt framing's single combined group
# has nothing to contrast against here.
group_clinical_primary_wide <- group_clinical %>%
  filter(framing == "primary_mutually_exclusive",
         metric %in% c("median_age", "pct_female", "median_cci", "median_sofa_24h")) %>%
  pivot_wider(id_cols = group, names_from = metric, values_from = value)

if (nrow(group_clinical_primary_wide) == 2) {
  fig_clinical_profile <- group_clinical_primary_wide %>%
    mutate(patient_group = factor(group,
                                  levels = c("sepsis_core", "sepsis_extended"),
                                  labels = c("Core Sepsis", "Extended Only"))) %>%
    select(patient_group, median_age, pct_female, median_cci, median_sofa_24h) %>%
    pivot_longer(-patient_group, names_to = "variable", values_to = "value") %>%
    mutate(variable = recode(variable,
                             "median_age"     = "Median Age (years)",
                             "pct_female"     = "Female (%)",
                             "median_cci"     = "Median CCI",
                             "median_sofa_24h" = "Median SOFA (0-24h)")) %>%
    ggplot(aes(x = value, y = variable, color = patient_group, shape = patient_group)) +
    geom_point(size = 4) +
    scale_color_manual(values = c("Core Sepsis"   = "firebrick",
                                  "Extended Only" = "darkorange")) +
    labs(title    = paste0("Clinical Profile: Core vs Extended-Only Sepsis (", SITE_ID, ")"),
         subtitle = "Median values; Extended-only = meets ASE criteria via lactate criterion only",
         x = "Value", y = NULL, color = NULL, shape = NULL) +
    facet_wrap(~ variable, scales = "free_x", ncol = 2) +
    theme_minimal(base_size = 13) +
    theme(plot.title       = element_text(face = "bold"),
          panel.grid.minor = element_blank(),
          legend.position  = "bottom",
          strip.text       = element_text(face = "bold"))

  ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig4_clinical_profile.png")),
         plot = fig_clinical_profile, width = 8, height = 6, dpi = 300)
  fig_clinical_profile
} else {
  cat("NOTE: Clinical profile figure skipped — one or both sepsis groups absent.\n")
  fig_clinical_profile <- NULL
}
```

---

# Section 4 — Primary Analysis

Two separate binary logistic models. Both fit on the wide-format dataset (one row per hospitalization). `sepsis_extended` cases excluded from Model A; `sepsis_core` cases excluded from Model B.

- **Multi-hospital:** `glmer` with `(1 | hospital_id_deident)`, model-based SEs
- **Single-hospital:** `glm` with sandwich cluster-robust SEs on `hospitalization_id`
- **Primary contrast:** `lactate_vol_scaled` coefficient, Model B minus Model A

```{r primary-analysis}
# 4.1 Prepare model dataset
year_center <- round(mean(df$year, na.rm = TRUE), 2)

df_model <- df %>%
  mutate(
    lactate_vol_scaled = scale(lactate_order_per_1000_patient_days)[, 1],
    year_centered      = year - year_center
  )

lactate_center <- round(attr(scale(df$lactate_order_per_1000_patient_days),
                              "scaled:center"), 2)
lactate_scale  <- round(attr(scale(df$lactate_order_per_1000_patient_days),
                              "scaled:scale"),  2)
cat(paste("Lactate scaling: mean =", lactate_center, "| SD =", lactate_scale, "\n"))
cat(paste("Year centering offset:", year_center, "\n"))

# 4.2 Zero-variance covariate check
zero_var_covariates <- c("worst_sofa_admission_to_24h", "age", "sex", "cci",
                         "race_eth_model", "hospital_type", "year_centered",
                         "hospitalizations_from_ed_per_year") %>%
  purrr::keep(~ {
    col <- df_model[[.x]]
    if (is.factor(col)) nlevels(droplevels(col)) < 2
    else length(unique(col[!is.na(col)])) < 2
  })

if (length(zero_var_covariates) > 0) {
  warning("Zero-variance covariates dropped: ",
          paste(zero_var_covariates, collapse = ", "))
} else {
  cat("No zero-variance covariates detected.\n")
}

covariate_terms <- setdiff(
  c("worst_sofa_admission_to_24h", "age", "sex", "cci",
    "race_eth_model", "hospital_type", "year_centered",
    "hospitalizations_from_ed_per_year"),
  zero_var_covariates
)

# 4.3 Build formulas
# Model A: sepsis_core vs no_sepsis (excludes sepsis_extended)
# Model B: sepsis_extended vs no_sepsis (excludes sepsis_core)
# RE term added only for glmer path
re_term        <- if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL
fixed_rhs      <- c("lactate_vol_scaled", covariate_terms, re_term)
formula_model_a <- reformulate(fixed_rhs, response = "outcome_a")
formula_model_b <- reformulate(fixed_rhs, response = "outcome_b")

cat(paste("Model formula RHS:", deparse(reformulate(fixed_rhs)), "\n"))
cat(paste("Modeling path:", re_structure, "\n"))

# 4.4 Prepare binary outcome datasets
df_model_a <- df_model %>%
  filter(patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_model_b <- df_model %>%
  filter(patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

cat(paste("Model A sample (core vs no_sepsis): n =",
          nrow(df_model_a), "hospitalizations\n"))
cat(paste("Model B sample (extended vs no_sepsis): n =",
          nrow(df_model_b), "hospitalizations\n"))

# 4.5 Fit models
warn_primary_a <- NULL
warn_primary_b <- NULL

model_a <- fit_binary(formula_model_a, df_model_a, model_path,
                      warn_var = "warn_primary_a")
model_b <- fit_binary(formula_model_b, df_model_b, model_path,
                      warn_var = "warn_primary_b")

cat(paste("Model A fit:", ifelse(is.null(model_a), "FAILED", "OK"), "\n"))
cat(paste("Model B fit:", ifelse(is.null(model_b), "FAILED", "OK"), "\n"))

# 4.6 Extract coefficients
vcov_a <- if (!is.null(model_a)) get_model_vcov(model_a, model_path, df_model_a) else NULL
vcov_b <- if (!is.null(model_b)) get_model_vcov(model_b, model_path, df_model_b) else NULL

coef_a_raw <- tidy_binary(model_a, vcov_a)
coef_b_raw <- tidy_binary(model_b, vcov_b)

metadata_args <- list(
  site_id            = SITE_ID,
  n_hospitals        = n_hospitals,
  n_hospitalizations = nrow(df_model),
  lactate_center     = lactate_center,
  lactate_scale      = lactate_scale,
  year_center        = year_center,
  centering_method   = centering_method,
  zero_var_covariates = zero_var_covariates,
  warn_a             = warn_primary_a,
  warn_b             = warn_primary_b
)

coef_a <- if (!is.null(coef_a_raw))
  do.call(add_metadata, c(list(coef_df = coef_a_raw,
                                model_version = paste0(re_structure, "_model_a_core_vs_nosepsis")),
                           metadata_args))

coef_b <- if (!is.null(coef_b_raw))
  do.call(add_metadata, c(list(coef_df = coef_b_raw,
                                model_version = paste0(re_structure, "_model_b_extended_vs_nosepsis")),
                           metadata_args))

# Combine for export
coef_primary <- bind_rows(
  if (!is.null(coef_a)) mutate(coef_a, model_label = "model_a_core_vs_nosepsis"),
  if (!is.null(coef_b)) mutate(coef_b, model_label = "model_b_extended_vs_nosepsis")
)

if (nrow(coef_primary) > 0) {
  cat("\nPrimary model — lactate_vol_scaled coefficients:\n")
  kable(coef_primary %>%
          filter(term == "lactate_vol_scaled") %>%
          select(model_label, estimate, std.error, statistic, p.value,
                 conf.low, conf.high),
        digits = 4,
        caption = "Primary models — lactate_vol_scaled by model (log-OR scale)")
}

# 4.7 Primary contrast
contrast_primary <- compute_contrast(coef_a_raw, coef_b_raw, vcov_a, vcov_b)

if (!is.null(contrast_primary)) {
  contrast_primary <- contrast_primary %>%
    mutate(
      site_id            = SITE_ID,
      model_version      = re_structure,
      n_hospitals        = n_hospitals,
      n_hospitalizations = nrow(df_model),
      blup_available     = (model_path == "glmer"),
      convergence_warn_a = !is.null(warn_primary_a),
      convergence_warn_b = !is.null(warn_primary_b)
    )
  cat("\nPrimary contrast (Model B minus Model A lactate coefficient):\n")
  kable(contrast_primary, digits = 4,
        caption = "Primary estimand — contrast on lactate_vol_scaled")
} else {
  warning("Primary contrast could not be computed — one or both models failed.")
}
```

```{r hospital-level-export}
# 4.8 Hospital-level BLUP export
# Multi-hospital: BLUPs from glmer ranef() for both models.
# Single-hospital: one-row stub, blup_available = FALSE.
# All IDs de-identified. No hospital metadata exported.

if (model_path == "glmer" &&
    !is.null(model_a) && !is.null(model_b) &&
    !is.null(contrast_primary)) {

  blup_df <- tryCatch({
    blup_a <- ranef(model_a)$hospital_id_deident %>%
      rownames_to_column("hospital_id_deident") %>%
      rename(blup_a = `(Intercept)`) %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    blup_b <- ranef(model_b)$hospital_id_deident %>%
      rownames_to_column("hospital_id_deident") %>%
      rename(blup_b = `(Intercept)`) %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    hosp_n <- df_model %>%
      group_by(hospital_id_deident) %>%
      summarise(n_hospitalizations_hospital = n(), .groups = "drop") %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    blup_a %>%
      left_join(blup_b, by = "hospital_id_deident") %>%
      left_join(hosp_n, by = "hospital_id_deident") %>%
      mutate(
        fixef_contrast         = contrast_primary$contrast_estimate,
        # Hospital-specific contrast = fixef contrast + blup_b - blup_a
        hosp_contrast_estimate = fixef_contrast + blup_b - blup_a,
        blup_available         = TRUE,
        blup_se_note           = "approximate — posterior variance not extracted; use for forest plot only",
        site_id                = SITE_ID,
        model_version          = re_structure
      )
  },
  error = function(e) {
    warning("BLUP extraction failed: ", e$message)
    NULL
  })

} else if (model_path == "glm" && !is.null(contrast_primary)) {

  blup_df <- tibble(
    hospital_id_deident         = 1L,
    blup_a                      = NA_real_,
    blup_b                      = NA_real_,
    fixef_contrast              = contrast_primary$contrast_estimate,
    hosp_contrast_estimate      = contrast_primary$contrast_estimate,
    n_hospitalizations_hospital = nrow(df_model),
    blup_available              = FALSE,
    blup_se_note                = "single-hospital — no shrinkage; use fixef_contrast for forest plot",
    site_id                     = SITE_ID,
    model_version               = re_structure
  )

} else {
  blup_df <- NULL
  warning("Hospital-level export could not be generated.")
}

if (!is.null(blup_df)) {
  cat("\nHospital-level export:\n")
  kable(blup_df, digits = 4,
        caption = "Hospital-level estimates (de-identified)")
}

# 4.9 RE variance export (primary models) ──────────────────────────────────────
# Between-hospital random intercept variance from glmer (multi-hospital path).
# Single-hospital path returns NA stubs so all sites return this file uniformly.
# Coordinating center combines within-site RE variance (this file) with
# between-site variance from meta-analytic pooling for two-level heterogeneity.
re_var_primary <- bind_rows(
  extract_re_variance(model_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("\nBetween-hospital RE variance — primary models:\n")
print(re_var_primary)
```

---

# Section 4b — Alternative Contrast: Non-Mutually-Exclusive Extended Framing

```{r alt-framing-check}
# ─────────────────────────────────────────────────────────────────────────────
# This section fits an alternative Model B to produce a directionality check
# on the primary contrast estimand.
#
# PRIMARY framing (Section 4):
#   Model A: sepsis_core      vs no_sepsis  (positive group = ASE_def_0==1)
#   Model B: sepsis_extended  vs no_sepsis  (positive group = lactate-only marginal,
#                                            ASE_def_0==0 AND ASE_def_1==1)
#   Contrast = Beta_B - Beta_A
#   Answers: does lactate ordering intensity predict reclassification into
#            the marginal lactate-only group?
#
# ALTERNATIVE framing (this section):
#   Model A: identical to primary — no refitting needed; reuses model_a / vcov_a
#   Model B: ASE_def_1==1 vs no_sepsis (positive group = sepsis_core + sepsis_extended,
#            i.e., everyone meeting the 6-criterion extended definition)
#   Contrast = Beta_B_alt - Beta_A
#   Answers: does lactate ordering intensity widen the overall gap between the
#            extended and core definitions? (policy-level question)
#
# Comparing the two contrasts reveals whether the direction is stable across
# how the extended group is bounded. If both are the same sign, the directional
# finding is not sensitive to the mutual-exclusivity assumption. If they diverge,
# the marginal lactate-only cases are driving a different signal than the
# combined extended population.
# ─────────────────────────────────────────────────────────────────────────────

cat("Fitting alternative Model B: ASE_def_1==1 (sepsis_core + sepsis_extended) vs no_sepsis\n")
cat("Model A reused from Section 4 without refitting.\n\n")

# Full analytic cohort; outcome = 1 for anyone meeting the 6-criterion definition
df_model_b_alt <- df_model %>%
  mutate(outcome_b_alt = as.integer(patient_group != "no_sepsis"))

cat(paste("Alternative Model B: n =", nrow(df_model_b_alt), "hospitalizations\n"))
cat(paste("  Positive (sepsis_core + sepsis_extended): n =",
          sum(df_model_b_alt$outcome_b_alt), "\n"))
cat(paste("  Negative (no_sepsis): n =",
          sum(df_model_b_alt$outcome_b_alt == 0), "\n"))

formula_model_b_alt <- reformulate(fixed_rhs, response = "outcome_b_alt")

warn_alt_b  <- NULL
model_b_alt <- fit_binary(formula_model_b_alt, df_model_b_alt, model_path,
                           warn_var = "warn_alt_b")

cat(paste("Alternative Model B fit:", ifelse(is.null(model_b_alt), "FAILED", "OK"), "\n"))

vcov_b_alt     <- if (!is.null(model_b_alt))
  get_model_vcov(model_b_alt, model_path, df_model_b_alt) else NULL
coef_b_alt_raw <- tidy_binary(model_b_alt, vcov_b_alt)

coef_b_alt <- if (!is.null(coef_b_alt_raw))
  add_metadata(
    coef_df             = coef_b_alt_raw,
    model_version       = paste0(re_structure, "_alt_model_b_extended_def1_vs_nosepsis"),
    site_id             = SITE_ID,
    n_hospitals         = n_hospitals,
    n_hospitalizations  = nrow(df_model_b_alt),
    lactate_center      = lactate_center,
    lactate_scale       = lactate_scale,
    year_center         = year_center,
    centering_method    = centering_method,
    zero_var_covariates = zero_var_covariates,
    warn_a              = warn_primary_a,
    warn_b              = warn_alt_b
  )

# Fold alt-framing coefs into the primary coefs export (one file per analysis —
# primary and alt framing are both "the primary analysis", just different
# Model B definitions sharing the same Model A) instead of a separate file.
if (!is.null(coef_b_alt))
  coef_primary <- bind_rows(coef_primary, mutate(coef_b_alt, model_label = "model_b_alt"))

# Alternative contrast — reuses vcov_a from Section 4 (no new variance needed for Model A)
contrast_alt <- compute_contrast(coef_a_raw, coef_b_alt_raw, vcov_a, vcov_b_alt)

if (!is.null(contrast_alt)) {
  contrast_alt <- contrast_alt %>%
    mutate(
      site_id            = SITE_ID,
      model_version      = paste0(re_structure, "_alt_extended_def1_vs_nosepsis"),
      n_hospitals        = n_hospitals,
      n_hospitalizations = nrow(df_model_b_alt),
      blup_available     = (model_path == "glmer"),
      convergence_warn_a = !is.null(warn_primary_a),
      convergence_warn_b = !is.null(warn_alt_b),
      framing            = "alt_extended_def1"
    )
}

# Append alt-model RE variance to the primary RE variance export (defined in
# Section 4.9, before this Model B_alt fit existed)
re_var_primary <- bind_rows(
  re_var_primary,
  extract_re_variance(model_b_alt, "model_b_alt_extended_def1_vs_nosepsis", model_path, SITE_ID)
)

# Alternative Model B lactate coefficient
if (!is.null(coef_b_alt)) {
  cat("\nAlternative Model B — lactate_vol_scaled coefficient:\n")
  kable(
    coef_b_alt %>%
      filter(term == "lactate_vol_scaled") %>%
      select(term, estimate, std.error, statistic, p.value, conf.low, conf.high),
    digits  = 4,
    caption = "Alternative Model B (ASE_def_1==1 vs no_sepsis) — lactate coefficient (log-OR scale)"
  )
}

# Side-by-side directionality check
if (!is.null(contrast_primary) && !is.null(contrast_alt)) {
  contrast_comparison <- bind_rows(
    contrast_primary %>%
      select(contrast_estimate, contrast_se, contrast_ci_low, contrast_ci_high,
             contrast_p, lactate_coef_model_a, lactate_coef_model_b) %>%
      mutate(framing = "primary: lactate-only (sepsis_extended) vs no_sepsis",
             .before = 1),
    contrast_alt %>%
      select(contrast_estimate, contrast_se, contrast_ci_low, contrast_ci_high,
             contrast_p, lactate_coef_model_a, lactate_coef_model_b) %>%
      mutate(framing = "alternative: all extended (ASE_def_1==1) vs no_sepsis",
             .before = 1)
  )

  cat("\nPrimary vs alternative contrast — directionality check:\n")
  kable(
    contrast_comparison,
    digits  = 4,
    caption = paste0(
      "Directionality check: consistent sign across both framings indicates the ",
      "direction is not driven by how the extended group is bounded. ",
      "Divergence in sign or magnitude indicates the lactate-only marginal cases ",
      "behave differently from the combined extended population with respect to ",
      "lactate ordering intensity."
    )
  )
} else {
  warning("Directionality check skipped — one or both contrasts unavailable.")
}

# Figure: framing comparison — coefficient panel + contrast forest panel ──────
fig_framing_comparison <- NULL

if (!is.null(contrast_primary) && !is.null(contrast_alt) &&
    !is.null(coef_a_raw) && !is.null(coef_b_raw) && !is.null(coef_b_alt_raw)) {

  # Panel A data: Model A and Model B lactate coefficients under each framing.
  # Model A is identical across both framings (no refit) — shown once per
  # framing row for visual symmetry with Model B, which does differ.
  panel_a_data <- bind_rows(
    coef_a_raw %>%
      filter(term == "lactate_vol_scaled") %>%
      mutate(framing = "Primary",     model = "Model A (sepsis_core)"),
    coef_b_raw %>%
      filter(term == "lactate_vol_scaled") %>%
      mutate(framing = "Primary",     model = "Model B (sepsis_extended)"),
    coef_a_raw %>%
      filter(term == "lactate_vol_scaled") %>%
      mutate(framing = "Alternative", model = "Model A (sepsis_core)"),
    coef_b_alt_raw %>%
      filter(term == "lactate_vol_scaled") %>%
      mutate(framing = "Alternative", model = "Model B (ASE_def_1==1)")
  ) %>%
    mutate(
      framing = factor(framing, levels = c("Primary", "Alternative")),
      # Reverse levels so Model A (anchor) appears at top of y-axis
    model   = factor(model, levels = c("Model B (ASE_def_1==1)",
                                          "Model B (sepsis_extended)",
                                          "Model A (sepsis_core)"))
    )

  panel_a <- ggplot(panel_a_data,
                     aes(x = estimate, y = model, color = framing)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
    geom_pointrange(
      aes(xmin = estimate - 1.96 * std.error,
          xmax = estimate + 1.96 * std.error),
      position = position_dodge(width = 0.4), size = 0.6
    ) +
    labs(
      title = "Model-level lactate coefficients by framing",
      x     = "Log-OR (lactate ordering intensity)",
      y     = NULL,
      color = "Framing"
    ) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "top")

  # Panel B: contrast forest — primary vs alternative
  panel_b_data <- contrast_comparison %>%
    mutate(
      framing_short = if_else(str_detect(framing, "^primary"),
                               "Primary\n(lactate-only vs no_sepsis)",
                               "Alternative\n(all extended vs no_sepsis)"),
      framing_short = factor(framing_short,
                              levels = c("Alternative\n(all extended vs no_sepsis)",
                                         "Primary\n(lactate-only vs no_sepsis)"))
    )

  panel_b <- ggplot(panel_b_data,
                     aes(x = contrast_estimate, y = framing_short)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
    geom_pointrange(
      aes(xmin = contrast_ci_low, xmax = contrast_ci_high),
      size = 0.7, color = "black"
    ) +
    labs(
      title = "Cross-model contrast (β_B − β_A)",
      x     = "Contrast estimate, log-OR scale (95% CI)",
      y     = NULL
    ) +
    theme_minimal(base_size = 11)

  fig_framing_comparison <- panel_a / panel_b +
    plot_annotation(
      title    = paste0(SITE_ID, ": Primary vs alternative extended-definition framing"),
      subtitle = "Consistent sign across framings = directional stability. Magnitude attenuation in alternative framing reflects sepsis_core dilution."
    )

  ggsave(file.path(OUTPUT_DIR, "figures",
                    paste0(SITE_ID, "_fig5_framing_comparison.png")),
         plot = fig_framing_comparison, width = 10, height = 7, dpi = 300)

  fig_framing_comparison
} else {
  warning("fig_framing_comparison skipped — one or more required model objects unavailable.")
}
```


---

# Section 5 — Sensitivity Analyses

```{r sensitivity-sa1}
# SA1: Restrict to encounters with lactate ordered in the ASE window ────────────
cat("Fitting SA1: restrict to lactate ordered in ASE window (window-specific)\n")

df_sa1_a <- df_model %>%
  filter(lactate_ordered_in_window == 1,
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa1_b <- df_model %>%
  filter(lactate_ordered_in_window == 1,
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

cat(paste("SA1 Model A: n =", nrow(df_sa1_a),
          "| Model B: n =", nrow(df_sa1_b), "\n"))

warn_sa1_a <- NULL; warn_sa1_b <- NULL
model_sa1_a <- fit_binary(formula_model_a, df_sa1_a, model_path, "warn_sa1_a")
model_sa1_b <- fit_binary(formula_model_b, df_sa1_b, model_path, "warn_sa1_b")

vcov_sa1_a <- if (!is.null(model_sa1_a)) get_model_vcov(model_sa1_a, model_path, df_sa1_a) else NULL
vcov_sa1_b <- if (!is.null(model_sa1_b)) get_model_vcov(model_sa1_b, model_path, df_sa1_b) else NULL

coef_sa1 <- bind_rows(
  if (!is.null(model_sa1_a)) tidy_binary(model_sa1_a, vcov_sa1_a) %>%
    mutate(model_label = "model_a", model_version = "sa1_lactate_ordered_model_a",
           site_id = SITE_ID, n_rows = nrow(df_sa1_a)),
  if (!is.null(model_sa1_b)) tidy_binary(model_sa1_b, vcov_sa1_b) %>%
    mutate(model_label = "model_b", model_version = "sa1_lactate_ordered_model_b",
           site_id = SITE_ID, n_rows = nrow(df_sa1_b))
)

contrast_sa1 <- compute_contrast(
  tidy_binary(model_sa1_a, vcov_sa1_a),
  tidy_binary(model_sa1_b, vcov_sa1_b),
  vcov_sa1_a, vcov_sa1_b
)

if (!is.null(contrast_sa1))
  contrast_sa1 <- contrast_sa1 %>%
    mutate(site_id = SITE_ID, model_version = "sa1_lactate_ordered")

re_var_sa1 <- bind_rows(
  extract_re_variance(model_sa1_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_sa1_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("SA1 complete.\n")
if (nrow(coef_sa1) > 0)
  kable(coef_sa1 %>% filter(term == "lactate_vol_scaled") %>%
          select(model_label, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA1 — lactate_vol_scaled by model")
if (!is.null(contrast_sa1))
  kable(contrast_sa1, digits = 4, caption = "SA1 — primary contrast")

# SA1 alt framing — same lactate-ordered-in-window restriction, full cohort,
# outcome = ASE_def_1==1 vs no_sepsis. Model A reused from SA1 above (no refit).
df_sa1_b_alt <- df_model %>%
  filter(lactate_ordered_in_window == 1) %>%
  mutate(outcome_b_alt = as.integer(patient_group_alt == "ase_extended_any"))

warn_sa1_b_alt  <- NULL
model_sa1_b_alt <- fit_binary(formula_model_b_alt, df_sa1_b_alt, model_path, "warn_sa1_b_alt")
vcov_sa1_b_alt  <- if (!is.null(model_sa1_b_alt))
  get_model_vcov(model_sa1_b_alt, model_path, df_sa1_b_alt) else NULL
coef_sa1_b_alt_raw <- tidy_binary(model_sa1_b_alt, vcov_sa1_b_alt)

if (!is.null(coef_sa1_b_alt_raw))
  coef_sa1 <- bind_rows(
    coef_sa1,
    coef_sa1_b_alt_raw %>%
      mutate(model_label = "model_b_alt", model_version = "sa1_lactate_ordered_model_b_alt",
             site_id = SITE_ID, n_rows = nrow(df_sa1_b_alt))
  )

contrast_sa1_alt <- compute_contrast(
  tidy_binary(model_sa1_a, vcov_sa1_a),
  coef_sa1_b_alt_raw, vcov_sa1_a, vcov_sa1_b_alt
)
if (!is.null(contrast_sa1_alt))
  contrast_sa1_alt <- contrast_sa1_alt %>%
    mutate(site_id = SITE_ID, model_version = "sa1_lactate_ordered_alt",
           n_hospitalizations = nrow(df_sa1_b_alt))

re_var_sa1 <- bind_rows(
  re_var_sa1,
  extract_re_variance(model_sa1_b_alt, "model_b_alt_extended_def1_vs_nosepsis", model_path, SITE_ID)
)

cat("SA1 alt framing complete.\n")
```

```{r sensitivity-sa2a}
# SA2a: Exclude COVID years (2020–2021) ────────────────────────────────────────
cat("Fitting SA2a: exclude COVID years 2020-2021\n")

df_sa2a_a <- df_model %>%
  filter(!year %in% c(2020, 2021),
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa2a_b <- df_model %>%
  filter(!year %in% c(2020, 2021),
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

if (nrow(df_sa2a_a) == 0) {
  cat("SA2a: No data outside 2020-2021 — skipping.\n")
  coef_sa2a <- NULL; contrast_sa2a <- NULL; re_var_sa2a <- NULL
  contrast_sa2a_alt <- NULL
} else {
  cat(paste("SA2a Model A: n =", nrow(df_sa2a_a),
            "| Model B: n =", nrow(df_sa2a_b), "\n"))

  warn_sa2a_a <- NULL; warn_sa2a_b <- NULL
  model_sa2a_a <- fit_binary(formula_model_a, df_sa2a_a, model_path, "warn_sa2a_a")
  model_sa2a_b <- fit_binary(formula_model_b, df_sa2a_b, model_path, "warn_sa2a_b")

  vcov_sa2a_a <- if (!is.null(model_sa2a_a)) get_model_vcov(model_sa2a_a, model_path, df_sa2a_a) else NULL
  vcov_sa2a_b <- if (!is.null(model_sa2a_b)) get_model_vcov(model_sa2a_b, model_path, df_sa2a_b) else NULL

  coef_sa2a <- bind_rows(
    if (!is.null(model_sa2a_a)) tidy_binary(model_sa2a_a, vcov_sa2a_a) %>%
      mutate(model_label = "model_a", model_version = "sa2a_exclude_covid_model_a",
             site_id = SITE_ID, years_excluded = "2020, 2021", n_rows = nrow(df_sa2a_a)),
    if (!is.null(model_sa2a_b)) tidy_binary(model_sa2a_b, vcov_sa2a_b) %>%
      mutate(model_label = "model_b", model_version = "sa2a_exclude_covid_model_b",
             site_id = SITE_ID, years_excluded = "2020, 2021", n_rows = nrow(df_sa2a_b))
  )

  contrast_sa2a <- compute_contrast(
    tidy_binary(model_sa2a_a, vcov_sa2a_a),
    tidy_binary(model_sa2a_b, vcov_sa2a_b),
    vcov_sa2a_a, vcov_sa2a_b
  )
  if (!is.null(contrast_sa2a))
    contrast_sa2a <- contrast_sa2a %>%
      mutate(site_id = SITE_ID, model_version = "sa2a_exclude_covid")

  re_var_sa2a <- bind_rows(
    extract_re_variance(model_sa2a_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
    extract_re_variance(model_sa2a_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
  )

  cat("SA2a complete.\n")
  if (nrow(coef_sa2a) > 0)
    kable(coef_sa2a %>% filter(term == "lactate_vol_scaled") %>%
            select(model_label, estimate, std.error, p.value, conf.low, conf.high),
          digits = 4, caption = "SA2a — lactate_vol_scaled by model")
  if (!is.null(contrast_sa2a))
    kable(contrast_sa2a, digits = 4, caption = "SA2a — primary contrast")

  # SA2a alt framing — same COVID-year exclusion, full cohort, outcome = ASE_def_1==1
  # vs no_sepsis. Model A reused from SA2a above (no refit).
  df_sa2a_b_alt <- df_model %>%
    filter(!year %in% c(2020, 2021)) %>%
    mutate(outcome_b_alt = as.integer(patient_group_alt == "ase_extended_any"))

  warn_sa2a_b_alt  <- NULL
  model_sa2a_b_alt <- fit_binary(formula_model_b_alt, df_sa2a_b_alt, model_path, "warn_sa2a_b_alt")
  vcov_sa2a_b_alt  <- if (!is.null(model_sa2a_b_alt))
    get_model_vcov(model_sa2a_b_alt, model_path, df_sa2a_b_alt) else NULL
  coef_sa2a_b_alt_raw <- tidy_binary(model_sa2a_b_alt, vcov_sa2a_b_alt)

  if (!is.null(coef_sa2a_b_alt_raw))
    coef_sa2a <- bind_rows(
      coef_sa2a,
      coef_sa2a_b_alt_raw %>%
        mutate(model_label = "model_b_alt", model_version = "sa2a_exclude_covid_model_b_alt",
               site_id = SITE_ID, years_excluded = "2020, 2021", n_rows = nrow(df_sa2a_b_alt))
    )

  contrast_sa2a_alt <- compute_contrast(
    tidy_binary(model_sa2a_a, vcov_sa2a_a),
    coef_sa2a_b_alt_raw, vcov_sa2a_a, vcov_sa2a_b_alt
  )
  if (!is.null(contrast_sa2a_alt))
    contrast_sa2a_alt <- contrast_sa2a_alt %>%
      mutate(site_id = SITE_ID, model_version = "sa2a_exclude_covid_alt",
             n_hospitalizations = nrow(df_sa2a_b_alt))

  re_var_sa2a <- bind_rows(
    re_var_sa2a,
    extract_re_variance(model_sa2a_b_alt, "model_b_alt_extended_def1_vs_nosepsis", model_path, SITE_ID)
  )

  cat("SA2a alt framing complete.\n")
}
```

```{r sensitivity-sa2b}
# SA2b: Year-by-year stratification (exploratory) ──────────────────────────────
cat("Fitting SA2b: year-by-year stratified models\n")

years_available <- sort(unique(df_model$year))
cat(paste("SA2b years:", paste(years_available, collapse = ", "), "\n"))

sa2b_results <- map(years_available, function(yr) {
  d_a <- df_model %>%
    filter(year == yr, patient_group %in% c("no_sepsis", "sepsis_core")) %>%
    mutate(outcome_a = as.integer(patient_group == "sepsis_core"))
  d_b <- df_model %>%
    filter(year == yr, patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
    mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))
  # Alt framing: full within-year cohort (all three patient_group levels),
  # outcome = ASE_def_1==1 vs no_sepsis
  d_b_alt <- df_model %>%
    filter(year == yr) %>%
    mutate(outcome_b_alt = as.integer(patient_group_alt == "ase_extended_any"))

  cat(paste("SA2b year", yr, ": Model A n =", nrow(d_a),
            "| Model B n =", nrow(d_b), "| Model B_alt n =", nrow(d_b_alt), "\n"))

  # Drop zero-var covariates within year (year_centered always zero within a year)
  yr_zero_var <- c("hospital_type", "sex", "year_centered") %>%
    purrr::keep(~ {
      col <- d_a[[.x]]
      if (is.factor(col)) nlevels(droplevels(col)) < 2
      else length(unique(col[!is.na(col)])) < 2
    })
  yr_rhs <- c("lactate_vol_scaled",
               setdiff(covariate_terms, c(yr_zero_var, "year_centered")),
               if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL)
  yr_formula_a     <- reformulate(yr_rhs, response = "outcome_a")
  yr_formula_b     <- reformulate(yr_rhs, response = "outcome_b")
  yr_formula_b_alt <- reformulate(yr_rhs, response = "outcome_b_alt")

  warn_yr_a <- NULL; warn_yr_b <- NULL; warn_yr_b_alt <- NULL
  fit_a     <- fit_binary(yr_formula_a,     d_a,     model_path, "warn_yr_a")
  fit_b     <- fit_binary(yr_formula_b,     d_b,     model_path, "warn_yr_b")
  fit_b_alt <- fit_binary(yr_formula_b_alt, d_b_alt, model_path, "warn_yr_b_alt")

  if (is.null(fit_a) && is.null(fit_b) && is.null(fit_b_alt))
    warning("SA2b year ", yr, ": all three models (A, B, B_alt) failed to fit — ",
            "no coefs/contrast will be produced for this year. Check n and ",
            "covariate variance within year.")

  # A single failed model is enough to null out its contrast even when the
  # others succeed — flag that case specifically since it wouldn't otherwise
  # be visible until contrast_sa2b/contrast_sa2b_alt turn up empty downstream.
  if (is.null(fit_a) && (!is.null(fit_b) || !is.null(fit_b_alt)))
    warning("SA2b year ", yr, ": Model A failed to fit while Model B/B_alt ",
            "succeeded — primary and/or alt contrast for this year will be NA.")
  if (is.null(fit_b) && !is.null(fit_a))
    warning("SA2b year ", yr, ": Model B (primary framing) failed to fit — ",
            "primary contrast for this year will be NA.")
  if (is.null(fit_b_alt) && !is.null(fit_a))
    warning("SA2b year ", yr, ": Model B_alt (alt framing) failed to fit — ",
            "alt contrast for this year will be NA.")

  vcov_yr_a     <- if (!is.null(fit_a))     get_model_vcov(fit_a,     model_path, d_a)     else NULL
  vcov_yr_b     <- if (!is.null(fit_b))     get_model_vcov(fit_b,     model_path, d_b)     else NULL
  vcov_yr_b_alt <- if (!is.null(fit_b_alt)) get_model_vcov(fit_b_alt, model_path, d_b_alt) else NULL

  coefs <- bind_rows(
    if (!is.null(fit_a)) tidy_binary(fit_a, vcov_yr_a) %>%
      mutate(model_label = "model_a", year = yr, n_rows = nrow(d_a),
             site_id = SITE_ID, model_version = "sa2b_year_stratified"),
    if (!is.null(fit_b)) tidy_binary(fit_b, vcov_yr_b) %>%
      mutate(model_label = "model_b", year = yr, n_rows = nrow(d_b),
             site_id = SITE_ID, model_version = "sa2b_year_stratified"),
    if (!is.null(fit_b_alt)) tidy_binary(fit_b_alt, vcov_yr_b_alt) %>%
      mutate(model_label = "model_b_alt", year = yr, n_rows = nrow(d_b_alt),
             site_id = SITE_ID, model_version = "sa2b_year_stratified_alt")
  )

  contrast <- compute_contrast(
    tidy_binary(fit_a, vcov_yr_a),
    tidy_binary(fit_b, vcov_yr_b),
    vcov_yr_a, vcov_yr_b
  )
  if (!is.null(contrast))
    contrast <- contrast %>% mutate(year = yr, site_id = SITE_ID,
                                    model_version = "sa2b_year_stratified",
                                    framing = "primary_mutually_exclusive")

  contrast_alt <- compute_contrast(
    tidy_binary(fit_a, vcov_yr_a),
    tidy_binary(fit_b_alt, vcov_yr_b_alt),
    vcov_yr_a, vcov_yr_b_alt
  )
  if (!is.null(contrast_alt))
    contrast_alt <- contrast_alt %>% mutate(year = yr, site_id = SITE_ID,
                                            model_version = "sa2b_year_stratified_alt",
                                            framing = "alt_extended_def1")

  re_var <- bind_rows(
    extract_re_variance(fit_a,     "model_a_core_vs_nosepsis",             model_path, SITE_ID),
    extract_re_variance(fit_b,     "model_b_extended_vs_nosepsis",         model_path, SITE_ID),
    extract_re_variance(fit_b_alt, "model_b_alt_extended_def1_vs_nosepsis", model_path, SITE_ID)
  ) %>% mutate(year = yr)

  list(coefs = if (nrow(coefs) > 0) coefs else NULL,
       contrast = contrast, contrast_alt = contrast_alt, re_var = re_var)
})

coef_sa2b         <- bind_rows(map(sa2b_results, "coefs"))
contrast_sa2b     <- bind_rows(map(sa2b_results, "contrast"))
contrast_sa2b_alt <- bind_rows(map(sa2b_results, "contrast_alt"))
re_var_sa2b       <- bind_rows(map(sa2b_results, "re_var"))

cat(paste("SA2b complete:", length(years_available), "years attempted.\n"))
if (nrow(coef_sa2b) == 0)
  warning("SA2b: coef_sa2b is empty across all years — nothing will be written ",
          "for the SA2b coef file. See per-year warnings above for cause.")
if (nrow(contrast_sa2b) == 0)
  warning("SA2b: contrast_sa2b (primary framing) is empty across all years — ",
          "SA2b will not appear in contrast_estimates_all under the primary ",
          "framing. See per-year warnings above for which model failed each year.")
if (nrow(contrast_sa2b_alt) == 0)
  warning("SA2b: contrast_sa2b_alt (alt framing) is empty across all years — ",
          "SA2b will not appear in contrast_estimates_all under the alt ",
          "framing. See per-year warnings above for which model failed each year.")
if (nrow(coef_sa2b) > 0)
  kable(coef_sa2b %>% filter(term == "lactate_vol_scaled") %>%
          select(year, model_label, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA2b — lactate_vol_scaled by year and model")
if (nrow(contrast_sa2b) > 0)
  kable(contrast_sa2b, digits = 4, caption = "SA2b — primary contrast by year")
if (nrow(contrast_sa2b_alt) > 0)
  kable(contrast_sa2b_alt, digits = 4, caption = "SA2b — alt-framing contrast by year")
```

```{r sensitivity-sa3}
# SA3: Within-year centered lactate volume ─────────────────────────────────────
# Swaps lactate_vol_scaled for lactate_volume_centered; drops year_centered.
cat("Fitting SA3: within-year centered lactate volume\n")

sa3_rhs       <- c("lactate_volume_centered",
                    setdiff(covariate_terms, "year_centered"),
                    if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL)
formula_sa3_a <- reformulate(sa3_rhs, response = "outcome_a")
formula_sa3_b <- reformulate(sa3_rhs, response = "outcome_b")

df_sa3_a <- df_model %>%
  filter(!is.na(lactate_volume_centered),
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa3_b <- df_model %>%
  filter(!is.na(lactate_volume_centered),
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

if (nrow(df_sa3_a) < nrow(filter(df_model,
                                   patient_group %in% c("no_sepsis","sepsis_core"))))
  warning("SA3: rows dropped due to missing lactate_volume_centered.")

warn_sa3_a <- NULL; warn_sa3_b <- NULL
model_sa3_a <- fit_binary(formula_sa3_a, df_sa3_a, model_path, "warn_sa3_a")
model_sa3_b <- fit_binary(formula_sa3_b, df_sa3_b, model_path, "warn_sa3_b")

vcov_sa3_a <- if (!is.null(model_sa3_a)) get_model_vcov(model_sa3_a, model_path, df_sa3_a) else NULL
vcov_sa3_b <- if (!is.null(model_sa3_b)) get_model_vcov(model_sa3_b, model_path, df_sa3_b) else NULL

coef_sa3 <- bind_rows(
  if (!is.null(model_sa3_a)) tidy_binary(model_sa3_a, vcov_sa3_a) %>%
    mutate(model_label = "model_a", model_version = "sa3_centered_lactate_model_a",
           centering_method = centering_method, site_id = SITE_ID),
  if (!is.null(model_sa3_b)) tidy_binary(model_sa3_b, vcov_sa3_b) %>%
    mutate(model_label = "model_b", model_version = "sa3_centered_lactate_model_b",
           centering_method = centering_method, site_id = SITE_ID)
)

# Contrast uses lactate_volume_centered as the term
contrast_sa3 <- compute_contrast(
  tidy_binary(model_sa3_a, vcov_sa3_a),
  tidy_binary(model_sa3_b, vcov_sa3_b),
  vcov_sa3_a, vcov_sa3_b,
  lactate_term = "lactate_volume_centered"
)
if (!is.null(contrast_sa3))
  contrast_sa3 <- contrast_sa3 %>%
    mutate(site_id = SITE_ID, model_version = "sa3_centered_lactate",
           centering_method = centering_method)

re_var_sa3 <- bind_rows(
  extract_re_variance(model_sa3_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_sa3_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("SA3 complete.\n")
if (nrow(coef_sa3) > 0)
  kable(coef_sa3 %>% filter(grepl("lactate", term)) %>%
          select(model_label, term, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA3 — lactate terms by model")
if (!is.null(contrast_sa3))
  kable(contrast_sa3, digits = 4, caption = "SA3 — primary contrast")

# SA3 alt framing — same centered-lactate covariate set and missingness
# restriction, full cohort, outcome = ASE_def_1==1 vs no_sepsis.
# Model A reused from SA3 above (no refit).
formula_sa3_b_alt <- reformulate(sa3_rhs, response = "outcome_b_alt")

df_sa3_b_alt <- df_model %>%
  filter(!is.na(lactate_volume_centered)) %>%
  mutate(outcome_b_alt = as.integer(patient_group_alt == "ase_extended_any"))

warn_sa3_b_alt  <- NULL
model_sa3_b_alt <- fit_binary(formula_sa3_b_alt, df_sa3_b_alt, model_path, "warn_sa3_b_alt")
vcov_sa3_b_alt  <- if (!is.null(model_sa3_b_alt))
  get_model_vcov(model_sa3_b_alt, model_path, df_sa3_b_alt) else NULL
coef_sa3_b_alt_raw <- tidy_binary(model_sa3_b_alt, vcov_sa3_b_alt)

if (!is.null(coef_sa3_b_alt_raw))
  coef_sa3 <- bind_rows(
    coef_sa3,
    coef_sa3_b_alt_raw %>%
      mutate(model_label = "model_b_alt", model_version = "sa3_centered_lactate_model_b_alt",
             centering_method = centering_method, site_id = SITE_ID)
  )

contrast_sa3_alt <- compute_contrast(
  tidy_binary(model_sa3_a, vcov_sa3_a),
  coef_sa3_b_alt_raw, vcov_sa3_a, vcov_sa3_b_alt,
  lactate_term = "lactate_volume_centered"
)
if (!is.null(contrast_sa3_alt))
  contrast_sa3_alt <- contrast_sa3_alt %>%
    mutate(site_id = SITE_ID, model_version = "sa3_centered_lactate_alt",
           centering_method = centering_method,
           n_hospitalizations = nrow(df_sa3_b_alt))

re_var_sa3 <- bind_rows(
  re_var_sa3,
  extract_re_variance(model_sa3_b_alt, "model_b_alt_extended_def1_vs_nosepsis", model_path, SITE_ID)
)

cat("SA3 alt framing complete.\n")
```

```{r sensitivity-sa4}
# SA4: SOFA-dropped sensitivity ─────────────────────────────────────────────────
# Rationale:  SA4 refits both models without
# worst_sofa_admission_to_24h and computes the contrast to assess whether the
# primary finding is sensitive to this potential over-adjustment due to structurally low SOFA for sepsis_extended patients .
cat("Fitting SA4: SOFA-dropped sensitivity\n")

covariate_terms_sa4 <- setdiff(covariate_terms, "worst_sofa_admission_to_24h")

if ("worst_sofa_admission_to_24h" %in% covariate_terms) {
  cat(paste("SA4: dropping worst_sofa_admission_to_24h. Remaining:",
            paste(covariate_terms_sa4, collapse = ", "), "\n"))
} else {
  cat("SA4: worst_sofa_admission_to_24h already excluded — SA4 identical to primary.\n")
}

# Same datasets as primary; only the formula changes
formula_sa4_a <- reformulate(
  c("lactate_vol_scaled", covariate_terms_sa4,
    if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL),
  response = "outcome_a")
formula_sa4_b <- reformulate(
  c("lactate_vol_scaled", covariate_terms_sa4,
    if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL),
  response = "outcome_b")

warn_sa4_a <- NULL; warn_sa4_b <- NULL
model_sa4_a <- fit_binary(formula_sa4_a, df_model_a, model_path, "warn_sa4_a")
model_sa4_b <- fit_binary(formula_sa4_b, df_model_b, model_path, "warn_sa4_b")

vcov_sa4_a <- if (!is.null(model_sa4_a)) get_model_vcov(model_sa4_a, model_path, df_model_a) else NULL
vcov_sa4_b <- if (!is.null(model_sa4_b)) get_model_vcov(model_sa4_b, model_path, df_model_b) else NULL

coef_sa4_a_raw <- tidy_binary(model_sa4_a, vcov_sa4_a)
coef_sa4_b_raw <- tidy_binary(model_sa4_b, vcov_sa4_b)

coef_sa4 <- bind_rows(
  if (!is.null(coef_sa4_a_raw)) coef_sa4_a_raw %>%
    mutate(model_label    = "model_a",
           model_version  = paste0(re_structure, "_sa4_sofa_dropped_model_a"),
           site_id        = SITE_ID,
           convergence_warn = !is.null(warn_sa4_a)),
  if (!is.null(coef_sa4_b_raw)) coef_sa4_b_raw %>%
    mutate(model_label    = "model_b",
           model_version  = paste0(re_structure, "_sa4_sofa_dropped_model_b"),
           site_id        = SITE_ID,
           convergence_warn = !is.null(warn_sa4_b))
)

contrast_sa4 <- compute_contrast(coef_sa4_a_raw, coef_sa4_b_raw, vcov_sa4_a, vcov_sa4_b)
if (!is.null(contrast_sa4))
  contrast_sa4 <- contrast_sa4 %>%
    mutate(
      site_id              = SITE_ID,
      model_version        = paste0(re_structure, "_sa4_sofa_dropped"),
      n_hospitals          = n_hospitals,
      n_hospitalizations   = nrow(df_model),
      blup_available       = (model_path == "glmer"),
      convergence_warn_a   = !is.null(warn_sa4_a),
      convergence_warn_b   = !is.null(warn_sa4_b),
      sensitivity_analysis = "SA4_sofa_dropped"
    )

re_var_sa4 <- bind_rows(
  extract_re_variance(model_sa4_a, "model_a_core_vs_nosepsis_sa4",     model_path, SITE_ID),
  extract_re_variance(model_sa4_b, "model_b_extended_vs_nosepsis_sa4", model_path, SITE_ID)
)

cat("SA4 complete.\n")
if (nrow(coef_sa4) > 0)
  kable(coef_sa4 %>% filter(grepl("lactate", term)) %>%
          select(model_label, term, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA4 — lactate terms by model (SOFA dropped)")
if (!is.null(contrast_sa4))
  kable(contrast_sa4, digits = 4, caption = "SA4 — primary contrast (SOFA dropped)")

# SA4 alt framing — same SOFA-dropped covariate set, same full cohort as
# Section 4b's df_model_b_alt (no row restriction beyond primary), outcome =
# ASE_def_1==1 vs no_sepsis. Model A reused from SA4 above (no refit).
formula_sa4_b_alt <- reformulate(
  c("lactate_vol_scaled", covariate_terms_sa4,
    if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL),
  response = "outcome_b_alt")

warn_sa4_b_alt  <- NULL
model_sa4_b_alt <- fit_binary(formula_sa4_b_alt, df_model_b_alt, model_path, "warn_sa4_b_alt")
vcov_sa4_b_alt  <- if (!is.null(model_sa4_b_alt))
  get_model_vcov(model_sa4_b_alt, model_path, df_model_b_alt) else NULL
coef_sa4_b_alt_raw <- tidy_binary(model_sa4_b_alt, vcov_sa4_b_alt)

if (!is.null(coef_sa4_b_alt_raw))
  coef_sa4 <- bind_rows(
    coef_sa4,
    coef_sa4_b_alt_raw %>%
      mutate(model_label    = "model_b_alt",
             model_version  = paste0(re_structure, "_sa4_sofa_dropped_model_b_alt"),
             site_id        = SITE_ID,
             convergence_warn = !is.null(warn_sa4_b_alt))
  )

contrast_sa4_alt <- compute_contrast(coef_sa4_a_raw, coef_sa4_b_alt_raw, vcov_sa4_a, vcov_sa4_b_alt)
if (!is.null(contrast_sa4_alt))
  contrast_sa4_alt <- contrast_sa4_alt %>%
    mutate(
      site_id              = SITE_ID,
      model_version        = paste0(re_structure, "_sa4_sofa_dropped_alt"),
      n_hospitals          = n_hospitals,
      n_hospitalizations   = nrow(df_model_b_alt),
      blup_available       = (model_path == "glmer"),
      convergence_warn_a   = !is.null(warn_sa4_a),
      convergence_warn_b   = !is.null(warn_sa4_b_alt),
      sensitivity_analysis = "SA4_sofa_dropped_alt"
    )

re_var_sa4 <- bind_rows(
  re_var_sa4,
  extract_re_variance(model_sa4_b_alt, "model_b_alt_extended_def1_vs_nosepsis_sa4", model_path, SITE_ID)
)

cat("SA4 alt framing complete.\n")
```

---

# Section 6 — Output Assembly & Export

```{r export-compile}
# 6.1a Consolidated contrast export 

tag_contrast <- function(x, analysis, framing = NULL,
                        n_hospitalizations = NA_integer_, year = NA_integer_) {
  if (is.null(x)) return(NULL)
  if (!"analysis" %in% names(x))            x <- mutate(x, analysis = analysis)
  if (!is.null(framing) && !"framing" %in% names(x)) x <- mutate(x, framing = framing)
  if (!"year" %in% names(x))                x <- mutate(x, year = year)
  if (!"n_hospitalizations" %in% names(x))  x <- mutate(x, n_hospitalizations = n_hospitalizations)
  x
}

contrast_all <- bind_rows(
  tag_contrast(contrast_primary,  "primary",              "primary_mutually_exclusive", nrow(df_model)),
  tag_contrast(contrast_alt,      "primary",               n_hospitalizations = nrow(df_model_b_alt)),
  tag_contrast(contrast_sa1,      "sa1_lactate_ordered",  "primary_mutually_exclusive", nrow(df_sa1_b)),
  tag_contrast(contrast_sa1_alt,  "sa1_lactate_ordered",  "alt_extended_def1",          nrow(df_sa1_b_alt)),
  tag_contrast(contrast_sa2a,     "sa2a_exclude_covid",   "primary_mutually_exclusive", nrow(df_sa2a_b)),
  tag_contrast(contrast_sa2a_alt, "sa2a_exclude_covid",   "alt_extended_def1",          nrow(df_sa2a_b_alt)),
  tag_contrast(contrast_sa2b,     "sa2b_year_stratified"),
  tag_contrast(contrast_sa2b_alt, "sa2b_year_stratified"),
  tag_contrast(contrast_sa3,      "sa3_centered_lactate", "primary_mutually_exclusive", nrow(df_sa3_b)),
  tag_contrast(contrast_sa3_alt,  "sa3_centered_lactate", "alt_extended_def1",          nrow(df_sa3_b_alt)),
  tag_contrast(contrast_sa4,      "sa4_sofa_dropped",     "primary_mutually_exclusive", nrow(df_model)),
  tag_contrast(contrast_sa4_alt,  "sa4_sofa_dropped",     "alt_extended_def1",          nrow(df_model_b_alt))
) %>%
  select(site_id, analysis, framing, year, n_hospitalizations, everything())

if (nrow(contrast_all) == 0)
  warning("contrast_all is empty — every contrast in this run failed to compute. ",
          "Check model fit logs above before distributing.")

# 6.1b Consolidated RE variance export

tag_re_var <- function(x, analysis, year = NA_integer_) {
  if (is.null(x) || nrow(x) == 0) return(NULL)
  if (!"analysis" %in% names(x)) x <- mutate(x, analysis = analysis)
  if (!"year" %in% names(x))     x <- mutate(x, year = year)
  x %>% mutate(framing = if_else(grepl("alt", model_label),
                                 "alt_extended_def1", "primary_mutually_exclusive"))
}

re_var_all <- bind_rows(
  tag_re_var(re_var_primary, "primary"),
  tag_re_var(re_var_sa1,     "sa1_lactate_ordered"),
  tag_re_var(re_var_sa2a,    "sa2a_exclude_covid"),
  tag_re_var(re_var_sa2b,    "sa2b_year_stratified"),
  tag_re_var(re_var_sa3,     "sa3_centered_lactate"),
  tag_re_var(re_var_sa4,     "sa4_sofa_dropped")
) %>%
  select(site_id, analysis, framing, year, model_label, re_sigma2, re_sigma, re_available)

if (nrow(re_var_all) == 0)
  warning("re_var_all is empty — no RE variance rows produced across any analysis. ",
          "Expected for glm (single-hospital) path; unexpected for glmer path.")

# 6.1 Compile output list
output_list <- list(
  site_id              = SITE_ID,
  model_version_used   = re_structure,
  model_path           = model_path,
  interaction_type     = interaction_type,
  n_hospitals          = n_hospitals,
  n_hospitalizations   = nrow(df_model),
  n_dropped_check_dq   = n_check_dq,
  cor_lactate_year     = cor_lactate_year,
  dropped_covariates   = zero_var_covariates,
  lactate_mean         = lactate_center,
  lactate_sd           = lactate_scale,
  year_center          = year_center,
  centering_method     = centering_method,
  coef_primary         = coef_primary,
  vcov_model_a         = vcov_a,
  vcov_model_b         = vcov_b,
  contrast_all         = contrast_all,
  re_var_all           = re_var_all,
  blup_hospital        = blup_df,
  cohort_summary       = cohort_summary,
  ase_rate_by_year     = ase_rate_by_year,
  hosp_year_summary    = hosp_year_summary,
  hosp_year_detail     = hosp_year_detail,
  hosp_year_ase        = hosp_year_ase,
  group_summary        = group_summary,
  group_clinical       = group_clinical,
  coef_sa1             = coef_sa1,
  coef_sa2a            = coef_sa2a,
  coef_sa2b            = coef_sa2b,
  coef_sa3             = coef_sa3,
  coef_sa4             = coef_sa4,
  fig_lactate_trend    = fig_lactate_trend,
  fig_ase_gap          = fig_ase_gap,
  fig_group_dist       = fig_group_dist,
  fig_clinical_profile = fig_clinical_profile,
  fig_framing_comparison = fig_framing_comparison
)

# 6.2 Export CSVs
write_csv(baseline_completeness,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_01_baseline_completeness.csv")))
write_csv(qc_table,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_02_patient_group_qc.csv")))
write_csv(
  tibble(site_id = SITE_ID, cor_lactate_year = cor_lactate_year,
         collinearity_flag = abs(cor_lactate_year) > 0.7),
  file.path(OUTPUT_DIR, "diagnostics",
       paste0(SITE_ID, "_03_cor_lactate_year.csv")))

write_csv(cohort_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_01_cohort_summary.csv")))
write_csv(ase_rate_by_year,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_02_ase_rate_by_year.csv")))
write_csv(hosp_year_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_03_hosp_year_lactate_summary.csv")))
write_csv(hosp_year_detail,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_04_hosp_year_lactate_detail.csv")))
write_csv(hosp_year_ase,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_05_hosp_year_ase_rates.csv")))
write_csv(group_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_06_patient_group_distribution.csv")))
write_csv(group_clinical,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_07_clinical_profile_by_group.csv")))

# Coefs — one file per analysis (primary and alt framing folded in together
# as model_a / model_b / model_b_alt rows within each)
write_if(coef_primary,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_08_primary_model_coefs.csv")))
# contrast files (primary, alt, SA1, SA2a, SA2b, SA3, SA4); one row per
# analysis x framing (x year for SA2b)
write_if(contrast_all,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_09_contrast_estimates_all.csv")))
write_if(blup_df,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_10_hospital_level_blups.csv")))
write_if(coef_sa1,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_11_sa1_lactate_ordered_coefs.csv")))
write_if(coef_sa2a,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_12_sa2a_exclude_covid_coefs.csv")))
write_if(coef_sa2b,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_13_sa2b_year_stratified_coefs.csv")))
write_if(coef_sa3,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_14_sa3_centered_lactate_coefs.csv")))

# vcov exported as separate CSVs for coordinating center use
if (!is.null(vcov_a))
  write_csv(as.data.frame(vcov_a),
            file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_15_vcov_model_a.csv")))
if (!is.null(vcov_b))
  write_csv(as.data.frame(vcov_b),
            file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_16_vcov_model_b.csv")))

# RE variance — consolidated across all analyses (primary, SA1, SA2a, SA2b,
# SA3, SA4), each already carrying model_a/model_b/model_b_alt rows, tagged
# by analysis x framing (x year for SA2b). 

write_if(re_var_all,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_17_re_variance_all.csv")))

# SA4 coefs (SOFA-dropped sensitivity; contrast lives in contrast_all above)
write_if(coef_sa4,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_18_sa4_sofa_dropped_coefs.csv")))

cat("CSV exports complete.\n")

# 6.3 RDS + JSON
saveRDS(output_list,
        file = file.path(OUTPUT_DIR, "models",
                    paste0(SITE_ID, "_ASE_results.rds")))

output_json <- output_list
output_json[c("fig_lactate_trend", "fig_ase_gap",
              "fig_group_dist", "fig_clinical_profile",
              "fig_framing_comparison")] <- NULL
output_json$vcov_model_a <- if (!is.null(vcov_a)) as.data.frame(vcov_a) else NULL
output_json$vcov_model_b <- if (!is.null(vcov_b)) as.data.frame(vcov_b) else NULL

write_json(output_json,
           path       = file.path(OUTPUT_DIR, "models",
                             paste0(SITE_ID, "_ASE_results.json")),
           pretty     = TRUE, auto_unbox = TRUE, na = "null")

cat("RDS and JSON exports complete.\n")
cat(paste0("All outputs saved to ", OUTPUT_DIR, " — share entire folder with coordinating center.\n"))
```

---

# Session Info

```{r session-info}
writeLines(capture.output(sessionInfo()),
           file.path(OUTPUT_DIR, "diagnostics",
                paste0(SITE_ID, "_session_info.txt")))
sessionInfo()
```

---

# Output File Summary

The following files have been saved to the `<output_directory>/` directory (as configured in `clif_config.json`) for return to the coordinating center.

**Diagnostics (return all):**

- `<output_directory>/diagnostics/[SITE]_01_baseline_completeness.csv`
- `<output_directory>/diagnostics/[SITE]_02_patient_group_qc.csv` — long format: framing (primary/alt) x patient_group, n/pct pre-exclusion
- `<output_directory>/diagnostics/[SITE]_03_cor_lactate_year.csv`
- `<output_directory>/diagnostics/[SITE]_04_patient_group_hosp_year_crosstab.csv` — long format: framing x group n/pct by hospital x year
- `<output_directory>/diagnostics/[SITE]_session_info.txt`

**Tables (return all):**

- `<output_directory>/tables/[SITE]_01_cohort_summary.csv`
- `<output_directory>/tables/[SITE]_02_ase_rate_by_year.csv`
- `<output_directory>/tables/[SITE]_03_hosp_year_lactate_summary.csv`
- `<output_directory>/tables/[SITE]_04_hosp_year_lactate_detail.csv` — hospital-year detail ⭐
- `<output_directory>/tables/[SITE]_05_hosp_year_ase_rates.csv` — long format, primary + alt framing ⭐
- `<output_directory>/tables/[SITE]_06_patient_group_distribution.csv` — long format, primary + alt framing
- `<output_directory>/tables/[SITE]_07_clinical_profile_by_group.csv` — long format (framing x group x metric x value), primary + alt framing

**Models (return all):**

- `<output_directory>/models/[SITE]_08_primary_model_coefs.csv` — coefficients: model_a, model_b (primary), model_b_alt (alt framing) ⭐
- `<output_directory>/models/[SITE]_09_contrast_estimates_all.csv` — **all contrast estimands, one row per analysis x framing (x year for SA2b)** ⭐
- `<output_directory>/models/[SITE]_10_hospital_level_blups.csv` — hospital-level forest plot inputs ⭐
- `<output_directory>/models/[SITE]_11_sa1_lactate_ordered_coefs.csv` — model_a, model_b, model_b_alt
- `<output_directory>/models/[SITE]_12_sa2a_exclude_covid_coefs.csv` — model_a, model_b, model_b_alt
- `<output_directory>/models/[SITE]_13_sa2b_year_stratified_coefs.csv` — model_a, model_b, model_b_alt, one row set per year
- `<output_directory>/models/[SITE]_14_sa3_centered_lactate_coefs.csv` — model_a, model_b, model_b_alt
- `<output_directory>/models/[SITE]_15_vcov_model_a.csv` — vcov for Model A (coordinating center use)
- `<output_directory>/models/[SITE]_16_vcov_model_b.csv` — vcov for Model B (coordinating center use)
- `<output_directory>/models/[SITE]_17_re_variance_all.csv` — **all RE variance estimates, one row per analysis x framing x model_label (x year for SA2b)** ⭐. Between-hospital sigma^2/sigma from glmer; NA stubs on the glm (single-hospital) path.
- `<output_directory>/models/[SITE]_18_sa4_sofa_dropped_coefs.csv` — SA4 model_a, model_b, model_b_alt coefficients (SOFA dropped)
- `<output_directory>/models/[SITE]_ASE_results.rds` — full output bundle ⭐
- `<output_directory>/models/[SITE]_ASE_results.json`

Models folder renumbered to consecutive 08–18 as of this restructuring (previously had gaps from the contrast-file consolidation, then renumbered again when the 6 separate RE variance files were folded into one). This is a one-time renumbering done ahead of any cross-site results and before ASE_metaanalysis_v3.R has been updated to match — no downstream script depends on the old numbering yet. Once this version goes out to other sites and the CC script is built against it, any future consolidation should go back to leaving gaps rather than renumbering, so a stale CC script fails loudly on a missing file instead of silently reading the wrong one under a reused number.

**Figures (return if flagged issues):**

- `<output_directory>/figures/[SITE]_fig1_lactate_ase_trend.png`
- `<output_directory>/figures/[SITE]_fig2_ase_rate_gap.png`
- `<output_directory>/figures/[SITE]_fig3_patient_group_distribution.png`
- `<output_directory>/figures/[SITE]_fig4_clinical_profile.png`
- `<output_directory>/figures/[SITE]_fig5_framing_comparison.png` — primary vs alternative (§4b) framing comparison, model coefficients + contrast forest

**Do NOT share (local only):**

- Hospital de-identification crosswalk (printed to console only)
