---
title: "ASE Definition Comparison: Site-Level Analysis"

format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    theme: cosmo
    embed-resources: true
    fig-width: 9
    fig-height: 6
execute:
  warning: false
  message: false
  echo: true
---

# Overview

This document implements the pre-specified analysis for the ASE Definition Comparison study. Sites should run this document from top to bottom without modification. All outputs are saved to the directory specified by `output_directory` in `clif_config.json` for return to the coordinating center.

**Study Question:** Does hospital-level lactate ordering intensity explain the gap between core and extended CDC Adult Sepsis Event (ASE) rates?

**Design:**

- **Exposure:** Lactate ordering intensity (orders per 1,000 patient-days), hospital-year level
- **Outcome:** ASE case status under core vs. extended definition (two rows per encounter)
- **Method:** Logistic regression with clustered SEs at `hospitalization_id` level (sandwich estimator); hospital random intercept for multi-hospital sites
- **Key term:** `defined_w_lactic × lactate_vol_scaled` interaction

**Required data file:** `analysis_dataset.parquet` in the `phi_directory` specified in `clif_config.json`

**Required variables:**

| Variable | Description |
|---|---|
| `hospitalization_id` | Unique hospitalization identifier |
| `hospital_id` | Facility identifier |
| `defined_w_lactic` | 0 = core ASE definition, 1 = extended (includes lactate criterion) |
| `ASE` | 1 = meets ASE criteria under this definition, 0 = does not |
| `lactate_order_per_1000_patient_days` | Hospital-year lactate ordering intensity |
| `worst_sofa_admission_to_24h` | SOFA score (0–24h from blood culture/antibiotic anchor) |
| `age`, `sex`, `cci` | Patient demographics and comorbidity |
| `hospital_type` | community or academic |
| `year` | Calendar year |
| `hospitalizations_from_ed_per_year` | Hospital-year ED volume |
| `any_lactate_ordered` | 1 = any lactate ordered during hospitalization |

---

# Section 0 — Setup

```{r setup}
library(tidyverse)   # includes purrr
library(lme4)        # glmer for multi-hospital sites
library(sandwich)    # vcovCL clustered SEs
library(lmtest)      # coeftest
library(jsonlite)
library(arrow)
library(here)
library(gtsummary)
library(broom)
library(scales)
library(knitr)
# library(splines)   # available if needed for nonlinear terms
# library(tableone)  # optional: for descriptive tables

set.seed(20240101)

# ── Site configuration (from clif_config.json) ────────────────────────────────
config     <- fromJSON(here("clif_config.json"))
SITE_ID    <- config$site_name
DATA_PATH  <- here(config$phi_directory, "analysis_dataset.parquet")
OUTPUT_DIR <- here(config$output_directory)
# ─────────────────────────────────────────────────────────────────────────────

# Active modeling approach - two paths only:
#   >= 2 hospitals  ->  glmer with hospital RE (1 | hospital_id) + clustered SEs at encounter
#   1 hospital      ->  glm + clustered SEs at encounter
# Encounter-level pairing handled via clustered SEs throughout (not RE)

# NOTE: MIN_HOSPITALS_FOR_NESTED_RE retained for reference only (not used in active analysis path)
MIN_HOSPITALS_FOR_NESTED_RE <- 5

# Create output directories
dir.create(file.path(OUTPUT_DIR, "figures"),     showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "tables"),      showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "diagnostics"), showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "models"),      showWarnings = FALSE, recursive = TRUE)

# Load data
df_raw <- read_parquet(DATA_PATH)

cat("Data loaded:", nrow(df_raw), "rows,", ncol(df_raw), "columns\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")
```

---

# Section 1 — Data Quality Checks

```{r data-quality}
# 1.1 Overall structure
cat("Rows:", nrow(df_raw), "\n")
cat("Columns:", ncol(df_raw), "\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")

# 1.2 Baseline completeness
missing_summary <- df_raw %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(pct_missing = round(n_missing / nrow(df_raw) * 100, 1)) %>%
  filter(n_missing > 0)

cat("\nMissing data summary (variables with any missing):\n")
print(missing_summary)

baseline_completeness <- df_raw %>%
  summarise(
    n                     = n(),
    age_miss              = sum(is.na(age)),
    sex_miss              = sum(is.na(sex)),
    cci_miss              = sum(is.na(cci)),
    sofa_miss             = sum(is.na(worst_sofa_admission_to_24h)),
    hosp_type_miss        = sum(is.na(hospital_type)),
    lactate_vol_miss      = sum(is.na(lactate_order_per_1000_patient_days)),
    year_miss             = sum(is.na(year)),
    ASE_miss              = sum(is.na(ASE)),
    defined_w_lactic_miss = sum(is.na(defined_w_lactic))
  )

cat("\nBaseline completeness:\n")
kable(baseline_completeness, caption = "Baseline completeness — key analysis variables")
write_csv(baseline_completeness,
          file.path(OUTPUT_DIR, "diagnostics", "01_baseline_completeness.csv"))

# 1.3 Data structure check
cat("\nData structure:\n")
str(df_raw)

# 1.4 Confirm two-row structure per encounter (ASE + ASE w Lactic)
row_counts <- df_raw %>%
  count(hospitalization_id) %>%
  count(n, name = "n_encounters")

cat("\nRows per hospitalization_id (expect all = 2):\n")
kable(row_counts, caption = "Expected: all hospitalizations should have exactly 2 rows")
```

---

# Section 2 — Derived Variables

```{r derived-variables}
# 2.1 Patient group classification ─────────────────────────────────────────────
# Pivot to wide (one row per encounter) to classify patient group:
#   Core cases:          ASE == 1 on defined_w_lactic == 0 row
#   Extended cases:      ASE == 0 on defined_w_lactic == 0 AND ASE == 1 on defined_w_lactic == 1
#   No sepsis:           ASE == 0 on both rows
#   check_data_quality:  ASE == 1 core, ASE == 0 extended — theoretically impossible

df_groups <- df_raw %>%
  select(hospitalization_id, defined_w_lactic, ASE) %>%
  pivot_wider(
    names_from   = defined_w_lactic,
    values_from  = ASE,
    names_prefix = "ASE_def_"
  ) %>%
  mutate(
    patient_group = case_when(
      ASE_def_0 == 1 & ASE_def_1 == 1  ~ "sepsis_core",
      ASE_def_0 == 0 & ASE_def_1 == 1  ~ "sepsis_extended",
      ASE_def_0 == 0 & ASE_def_1 == 0  ~ "no_sepsis",
      ASE_def_0 == 1 & ASE_def_1 == 0  ~ "check_data_quality",
      TRUE                              ~ NA_character_
    )
  )

# Join group back onto long dataset
df <- df_raw %>%
  left_join(df_groups %>% select(hospitalization_id, patient_group),
            by = "hospitalization_id")

cat("Patient group distribution:\n")
count(df_groups, patient_group) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  kable(caption = "Patient group distribution")

# 2.2 Collinearity diagnostic: lactate volume vs year ──────────────────────────
# Pearson r reported descriptively to justify primary modeling approach.
# r > 0.7 = strong collinearity; SA3 (within-year centering) available as sensitivity check.
# Note: computed at row level — repeated within hospital-year by design.

cor_lactate_year <- cor(
  df$lactate_order_per_1000_patient_days,
  df$year,
  use = "complete.obs"
)
cat(paste("\nPearson r (lactate_order_per_1000_patient_days ~ year):",
          round(cor_lactate_year, 3), "\n"))
if (abs(cor_lactate_year) > 0.7) {
  warning("r > 0.7 — strong collinearity detected. Review SA3 (centered lactate) results carefully.")
}

# 2.3 Hospital count and modeling structure decision ────────────────────────────
n_hospitals <- df %>% distinct(hospital_id) %>% nrow()
cat(paste("Number of hospitals at this site:", n_hospitals, "\n"))

# Two tiers only in active analysis:
#   >= 2 hospitals  ->  glmer with hospital RE
#   1 hospital      ->  glm with clustered SEs
re_structure <- ifelse(n_hospitals >= 2, "hospital_re", "single_hospital")

# Interaction type affects interpretation at aggregation stage:
#   Between-hospital:        primary estimand — does the gap widen at higher-testing hospitals?
#   Within-hospital temporal: secondary — do years with higher ordering show a wider gap?
interaction_type <- ifelse(n_hospitals >= 2, "between_hospital", "within_hospital_temporal")

cat(paste("Random effects structure:", re_structure, "\n"))
cat(paste("Interaction type:", interaction_type, "\n"))

# 2.4 Within-year centering (SA3 only) ─────────────────────────────────────────
# Not used in primary model — retained for sensitivity analysis SA3.
# Single-hospital sites: grand-mean centering used instead, flagged in output metadata.

if (n_hospitals >= 2) {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    group_by(year) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    ) %>%
    ungroup()
  centering_method <- "within_year"
} else {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    )
  centering_method <- "grand_mean"
  cat("Single-hospital site: grand-mean centering used for SA3. Flagged in output metadata.\n")
}

df <- df %>%
  left_join(
    hospital_year_stats %>% select(hospital_id, year, lactate_volume_centered,
                                   lactate_volume_year_mean),
    by = c("hospital_id", "year")
  )

cat(paste("Centering method:", centering_method, "\n"))

# 2.5 Factor coding ─────────────────────────────────────────────────────────────
df <- df %>%
  mutate(
    defined_w_lactic = factor(defined_w_lactic, levels = c(0, 1),
                              labels = c("core", "extended")),
    hospital_type    = factor(hospital_type, levels = c("community", "academic")),
    sex              = factor(sex, levels = c("Male", "Female")),
    year_f           = factor(year)
  )
```

---

# Section 3 — Descriptive Statistics

```{r descriptives}
# 3.1 Cohort summary ────────────────────────────────────────────────────────────
cohort_summary <- df %>%
  distinct(hospitalization_id, .keep_all = TRUE) %>%
  summarise(
    n_encounters       = n_distinct(hospitalization_id),
    n_hospitals        = n_distinct(hospital_id),
    n_years            = n_distinct(year),
    year_range         = paste(min(year), max(year), sep = "-"),
    median_age         = median(age, na.rm = TRUE),
    pct_female         = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
    median_cci         = median(cci, na.rm = TRUE),
    pct_academic       = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1)
  )

kable(cohort_summary, caption = "Overall cohort summary")

# 3.2 ASE rate by definition and year ───────────────────────────────────────────
ase_rate_by_year <- df %>%
  group_by(year, defined_w_lactic) %>%
  summarise(
    n          = n(),
    n_sepsis   = sum(ASE == 1, na.rm = TRUE),
    pct_sepsis = round(mean(ASE == 1, na.rm = TRUE) * 100, 1),
    .groups    = "drop"
  )

kable(ase_rate_by_year, caption = "ASE rate by year and definition")

# 3.3 Hospital-year lactate volume summary ─────────────────────────────────────
hosp_year_summary <- df %>%
  distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
  group_by(year) %>%
  summarise(
    n_hospitals      = n(),
    mean_lactate_vol = round(mean(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    sd_lactate_vol   = round(sd(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    min_lactate_vol  = round(min(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    max_lactate_vol  = round(max(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    .groups          = "drop"
  )

kable(hosp_year_summary, caption = "Hospital-year lactate volume summary")

# 3.4 Patient group distribution ────────────────────────────────────────────────
group_summary <- df_groups %>%
  count(patient_group) %>%
  mutate(pct = round(n / sum(n) * 100, 1))

kable(group_summary, caption = "Patient group distribution")

# 3.5 Clinical profile by patient group ────────────────────────────────────────
# Restricted to sepsis cases only (core and extended)
group_clinical <- df %>%
  distinct(hospitalization_id, .keep_all = TRUE) %>%
  filter(patient_group %in% c("sepsis_core", "sepsis_extended")) %>%
  group_by(patient_group) %>%
  summarise(
    n              = n(),
    median_age     = median(age, na.rm = TRUE),
    pct_female     = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
    median_cci     = median(cci, na.rm = TRUE),
    median_sofa    = median(worst_sofa_admission_to_24h, na.rm = TRUE),
    pct_academic   = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1),
    .groups        = "drop"
  )

kable(group_clinical, caption = "Clinical profile by patient group (sepsis cases only)")
```

```{r fig-lactate-trend, fig.height=5.5}
# 3.6 Figure: Lactate ordering intensity over time ─────────────────────────────
# Spaghetti (one line per hospital) + site mean overlay

hosp_year_plot_data <- df %>%
  distinct(hospital_id, year, lactate_order_per_1000_patient_days)

site_mean_by_year <- hosp_year_plot_data %>%
  group_by(year) %>%
  summarise(site_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE), .groups = "drop")

ase_hosp_year <- df %>%
  mutate(definition = ifelse(as.character(defined_w_lactic) %in% c("0", "core"),
                             "core", "extended")) %>%
  group_by(hospital_id, year, definition) %>%
  summarise(ase_rate = mean(ASE == 1, na.rm = TRUE), .groups = "drop")

lactate_range <- range(hosp_year_plot_data$lactate_order_per_1000_patient_days, na.rm = TRUE)
scale_factor  <- diff(lactate_range)
scale_offset  <- lactate_range[1]

fig_lactate_trend <- ggplot() +
  geom_line(data  = hosp_year_plot_data,
            aes(x = year, y = lactate_order_per_1000_patient_days, group = hospital_id),
            color = "steelblue", alpha = 0.45, linewidth = 0.6) +
  geom_point(data  = hosp_year_plot_data,
             aes(x = year, y = lactate_order_per_1000_patient_days, group = hospital_id),
             color = "steelblue", alpha = 0.45, size = 1.2) +
  geom_line(data  = site_mean_by_year,
            aes(x = year, y = site_mean),
            color = "steelblue", linewidth = 1.2) +
  geom_point(data  = site_mean_by_year,
             aes(x = year, y = site_mean),
             color = "steelblue", size = 2.2) +
  geom_line(data  = filter(ase_hosp_year, definition == "core"),
            aes(x = year, y = ase_rate * scale_factor + scale_offset, group = hospital_id),
            color = "firebrick", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  geom_line(data  = filter(ase_hosp_year, definition == "extended"),
            aes(x = year, y = ase_rate * scale_factor + scale_offset, group = hospital_id),
            color = "darkorange", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  scale_y_continuous(
    name     = "Lactate Orders per 1,000 Patient-Days",
    sec.axis = sec_axis(transform = ~ (. - scale_offset) / scale_factor,
                        name      = "ASE Rate (proportion)")
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Lactate Ordering Intensity and ASE Rate Over Time (", SITE_ID, ")"),
       subtitle = "Blue = lactate volume (solid = site mean); Red dashed = core ASE rate; Orange dashed = extended ASE rate",
       x = "Year") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        axis.title.y.left  = element_text(color = "steelblue"),
        axis.text.y.left   = element_text(color = "steelblue"),
        axis.title.y.right = element_text(color = "firebrick"),
        axis.text.y.right  = element_text(color = "firebrick"))

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig1_lactate_ase_trend.png")),
       plot = fig_lactate_trend, width = 9, height = 5.5, dpi = 300)
fig_lactate_trend
```

```{r fig-ase-gap}
# 3.7 Figure: ASE rate gap over time ───────────────────────────────────────────
# Gap = extended minus core ASE rate (percentage points)

ase_gap_by_year <- ase_rate_by_year %>%
  mutate(definition = ifelse(as.character(defined_w_lactic) %in% c("0", "core"),
                             "core", "extended")) %>%
  group_by(year, definition) %>%
  summarise(pct_sepsis = mean(pct_sepsis, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(id_cols = year, names_from = definition, values_from = pct_sepsis) %>%
  mutate(gap = extended - core)

ase_gap_by_hosp_year <- df %>%
  group_by(hospital_id, year, defined_w_lactic) %>%
  summarise(pct_sepsis = mean(ASE == 1, na.rm = TRUE) * 100, .groups = "drop") %>%
  mutate(definition = ifelse(as.character(defined_w_lactic) %in% c("0", "core"),
                             "core", "extended")) %>%
  group_by(hospital_id, year, definition) %>%
  summarise(pct_sepsis = mean(pct_sepsis, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(id_cols = c(hospital_id, year),
              names_from = definition, values_from = pct_sepsis) %>%
  mutate(gap = extended - core)

fig_ase_gap <- ggplot() +
  { if (n_hospitals > 1)
    geom_line(data  = ase_gap_by_hosp_year,
              aes(x = year, y = gap, group = hospital_id),
              color = "grey65", alpha = 0.5, linewidth = 0.6)
  } +
  geom_line(data  = ase_gap_by_year,
            aes(x = year, y = gap),
            color = "darkorchid", linewidth = 1.2) +
  geom_point(data = ase_gap_by_year,
             aes(x = year, y = gap),
             color = "darkorchid", size = 2.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Extended vs Core ASE Rate Gap Over Time (", SITE_ID, ")"),
       subtitle = "Gap = extended ASE rate minus core ASE rate (percentage points)\nGrey = individual hospitals; Purple = site mean",
       x = "Year",
       y = "ASE Rate Gap (percentage points)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"), panel.grid.minor = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig2_ase_rate_gap.png")),
       plot = fig_ase_gap, width = 8, height = 5, dpi = 300)
fig_ase_gap
```

```{r fig-group-dist}
# 3.8 Figure: Patient group distribution ───────────────────────────────────────

fig_group_dist <- group_summary %>%
  filter(patient_group != "check_data_quality") %>%
  mutate(patient_group = factor(patient_group,
                                levels = c("no_sepsis", "sepsis_core", "sepsis_extended"),
                                labels = c("No Sepsis", "Core Sepsis", "Extended Only"))) %>%
  ggplot(aes(x = patient_group, y = pct, fill = patient_group)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = paste0(pct, "%\n(n=", scales::comma(n), ")")),
            vjust = -0.4, size = 3.5) +
  scale_fill_manual(values = c("No Sepsis"     = "grey75",
                               "Core Sepsis"   = "firebrick",
                               "Extended Only" = "darkorange")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  labs(title    = paste0("Patient Group Distribution (", SITE_ID, ")"),
       subtitle = paste0("N = ", scales::comma(sum(group_summary$n[group_summary$patient_group != "check_data_quality"])),
                         " unique encounters"),
       x = NULL, y = "Percentage of Encounters (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        panel.grid.major.x = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig3_patient_group_distribution.png")),
       plot = fig_group_dist, width = 7, height = 5, dpi = 300)
fig_group_dist
```

```{r fig-clinical-profile}
# 3.9 Figure: Clinical profile comparison ─────────────────────────────────────
# Only generated if both core and extended groups are present

if (nrow(group_clinical) == 2) {
  fig_clinical_profile <- group_clinical %>%
    mutate(patient_group = factor(patient_group,
                                  levels = c("sepsis_core", "sepsis_extended"),
                                  labels = c("Core Sepsis", "Extended Only"))) %>%
    select(patient_group, median_age, pct_female, median_cci, median_sofa) %>%
    pivot_longer(cols = -patient_group, names_to = "variable", values_to = "value") %>%
    mutate(variable = recode(variable,
                             "median_age"  = "Median Age (years)",
                             "pct_female"  = "Female (%)",
                             "median_cci"  = "Median CCI",
                             "median_sofa" = "Median SOFA (0-24h)")) %>%
    ggplot(aes(x = value, y = variable, color = patient_group, shape = patient_group)) +
    geom_point(size = 4) +
    scale_color_manual(values = c("Core Sepsis"   = "firebrick",
                                  "Extended Only" = "darkorange")) +
    labs(title    = paste0("Clinical Profile: Core vs Extended-Only Sepsis (", SITE_ID, ")"),
         subtitle = "Median values; Extended-only = meets ASE criteria via lactate only",
         x = "Value", y = NULL, color = NULL, shape = NULL) +
    facet_wrap(~ variable, scales = "free_x", ncol = 2) +
    theme_minimal(base_size = 13) +
    theme(plot.title      = element_text(face = "bold"),
          panel.grid.minor = element_blank(),
          legend.position  = "bottom",
          strip.text       = element_text(face = "bold"))

  ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig4_clinical_profile.png")),
         plot = fig_clinical_profile, width = 8, height = 6, dpi = 300)
  fig_clinical_profile

} else {
  cat("NOTE: Clinical profile figure skipped — one or both sepsis groups absent at this site.\n")
  fig_clinical_profile <- NULL
}
```

---

# Section 4 — Primary Analysis

Approach: `glm` (logistic) + clustered SEs at `hospitalization_id` level (sandwich estimator).

- Encounter-level pairing (two rows per hospitalization) handled via clustered SEs rather than a random intercept
- Hospital-level random intercept retained for multi-hospital sites via `glmer` with hospital RE only (no encounter RE)
- Decision rationale: `glmer` with ~112k encounter-level RE levels is computationally intractable; clustered SEs produce equivalent inference for the within-encounter pairing  compared to encounter level RE 



```{r primary-analysis}
# 4.1 Prepare model dataset ─────────────────────────────────────────────────────
df_model <- df %>%
  mutate(
    outcome            = as.integer(ASE == 1),
    lactate_vol_scaled = scale(lactate_order_per_1000_patient_days)[, 1]
  )

lactate_center <- round(attr(scale(df$lactate_order_per_1000_patient_days), "scaled:center"), 2)
lactate_scale  <- round(attr(scale(df$lactate_order_per_1000_patient_days), "scaled:scale"), 2)
cat(paste("Lactate volume scaling: mean =", lactate_center, "| SD =", lactate_scale, "\n"))

# 4.2 Zero-variance covariate check ─────────────────────────────────────────────
zero_var_covariates <- c("worst_sofa_admission_to_24h", "age", "sex", "cci",
                         "hospital_type", "year", "hospitalizations_from_ed_per_year") %>%
  purrr::keep(~ {
    col <- df_model[[.x]]
    if (is.factor(col)) nlevels(droplevels(col)) < 2
    else length(unique(col[!is.na(col)])) < 2
  })

if (length(zero_var_covariates) > 0) {
  warning("Zero-variance covariates dropped: ", paste(zero_var_covariates, collapse = ", "))
} else {
  cat("No zero-variance covariates detected.\n")
}

covariate_terms <- setdiff(
  c("worst_sofa_admission_to_24h", "age", "sex", "cci",
    "hospital_type", "year", "hospitalizations_from_ed_per_year"),
  zero_var_covariates
)

# 4.3 Fit primary model ──────────────────────────────────────────────────────────
formula_primary <- reformulate(
  termlabels = c(
    "defined_w_lactic * lactate_vol_scaled",
    covariate_terms,
    if (re_structure != "single_hospital") "(1 | hospital_id)" else NULL
  ),
  response = "outcome"
)

primary_warning <- NULL

if (re_structure == "single_hospital") {
  model_type    <- "single_hospital_glm_clustered_se"
  model_primary <- tryCatch(
    glm(formula_primary, data = df_model, family = binomial),
    error = function(e) { warning("Primary model ERROR: ", e$message); NULL }
  )
} else {
  model_type    <- "hospital_re_glmer_clustered_se"
  model_primary <- withCallingHandlers(
    tryCatch(
      glmer(formula_primary, data = df_model, family = binomial,
            control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))),
      error = function(e) { warning("Primary model ERROR: ", e$message); NULL }
    ),
    warning = function(w) {
      primary_warning <<- w$message
      message("Primary model WARNING: ", w$message)
      invokeRestart("muffleWarning")
    }
  )
}

if (!is.null(model_primary)) {
  vcov_matrix <- vcovCL(model_primary, cluster = df_model$hospitalization_id)
  coef_robust <- coeftest(model_primary, vcov = vcov_matrix)
  cat("Primary model fitted successfully.\n")
} else {
  vcov_matrix <- NULL
  coef_robust <- NULL
  warning("Primary model failed to fit.")
}

# 4.4 Extract model output ───────────────────────────────────────────────────────
# Helper: safely tidy a coeftest object into a clean data frame.
# Uses broom::tidy() which correctly handles the named coeftest matrix
# regardless of column name formatting (avoids x.estimate / dimnames issues).
tidy_coeftest <- function(ct) {
  broom::tidy(ct) %>%
    rename(std.error = std.error, statistic = statistic, p.value = p.value)
}

if (!is.null(model_primary)) {
  coef_table <- tidy_coeftest(coef_robust) %>%
    mutate(
      conf.low            = estimate - 1.96 * std.error,
      conf.high           = estimate + 1.96 * std.error,
      site_id             = SITE_ID,
      model_version       = model_type,
      interaction_type    = interaction_type,
      n_hospitals         = n_hospitals,
      centering_method    = centering_method,
      lactate_mean        = lactate_center,
      lactate_sd          = lactate_scale,
      dropped_covariates  = paste(zero_var_covariates, collapse = ", "),
      convergence_warning = !is.null(primary_warning)
    )

  cat("Primary model coefficients (clustered SEs):\n")
  kable(coef_table, digits = 4, caption = "Primary model — all coefficients (log-OR scale)")

} else {
  warning("Primary model failed to fit. coef_table and vcov_matrix set to NULL.")
  coef_table  <- NULL
  vcov_matrix <- NULL
}
```

---

# Section 5 — Sensitivity Analyses

```{r sensitivity-sa1}
# SA1: Restrict to encounters with any lactate ordered ─────────────────────────
cat("Fitting SA1: primary model restricted to encounters with lactate ordered\n")

df_sa1 <- df_model %>% filter(any_lactate_ordered == 1)
cat(paste("SA1 sample: n =", nrow(df_sa1), "rows (",
          n_distinct(df_sa1$hospitalization_id), "encounters)\n"))

if (re_structure == "single_hospital") {
  model_sa1 <- tryCatch(
    glm(formula_primary, data = df_sa1, family = binomial),
    error = function(e) { warning("SA1 ERROR: ", e$message); NULL }
  )
} else {
  sa1_warning <- NULL
  model_sa1 <- withCallingHandlers(
    tryCatch(
      glmer(formula_primary, data = df_sa1, family = binomial,
            control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))),
      error = function(e) { warning("SA1 ERROR: ", e$message); NULL }
    ),
    warning = function(w) {
      sa1_warning <<- w$message
      message("SA1 WARNING: ", w$message)
      invokeRestart("muffleWarning")
    }
  )
}

if (!is.null(model_sa1)) {
  vcov_sa1     <- vcovCL(model_sa1, cluster = df_sa1$hospitalization_id)
  coef_sa1_raw <- coeftest(model_sa1, vcov = vcov_sa1)
  coef_sa1 <- tidy_coeftest(coef_sa1_raw) %>%
    mutate(conf.low      = estimate - 1.96 * std.error,
           conf.high     = estimate + 1.96 * std.error,
           site_id       = SITE_ID,
           model_version = "sa1_lactate_ordered_only",
           n_rows        = nrow(df_sa1))
  cat("SA1 complete.\n")
  coef_sa1 %>% filter(grepl("defined_w_lactic", term)) %>%
    kable(digits = 4, caption = "SA1 — key terms (log-OR scale)")
} else {
  coef_sa1 <- NULL
  warning("SA1 failed to fit.")
}
```

```{r sensitivity-sa2a}
# SA2a: Exclude COVID years (2020–2021) ────────────────────────────────────────
cat("Fitting SA2a: primary model excluding COVID years (2020-2021)\n")

df_sa2a <- df_model %>% filter(!year %in% c(2020, 2021))
cat(paste("SA2a sample: n =", nrow(df_sa2a), "rows (",
          n_distinct(df_sa2a$hospitalization_id), "encounters); years excluded: 2020, 2021\n"))

if (nrow(df_sa2a) == 0) {
  cat("SA2a: No data outside 2020-2021 at this site — skipping.\n")
  coef_sa2a <- NULL
} else {
  if (re_structure == "single_hospital") {
    model_sa2a <- tryCatch(
      glm(formula_primary, data = df_sa2a, family = binomial),
      error = function(e) { warning("SA2a ERROR: ", e$message); NULL }
    )
  } else {
    sa2a_warning <- NULL
    model_sa2a <- withCallingHandlers(
      tryCatch(
        glmer(formula_primary, data = df_sa2a, family = binomial,
              control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))),
        error = function(e) { warning("SA2a ERROR: ", e$message); NULL }
      ),
      warning = function(w) {
        sa2a_warning <<- w$message
        message("SA2a WARNING: ", w$message)
        invokeRestart("muffleWarning")
      }
    )
  }
  if (!is.null(model_sa2a)) {
    vcov_sa2a     <- vcovCL(model_sa2a, cluster = df_sa2a$hospitalization_id)
    coef_sa2a_raw <- coeftest(model_sa2a, vcov = vcov_sa2a)
    coef_sa2a <- tidy_coeftest(coef_sa2a_raw) %>%
      mutate(conf.low       = estimate - 1.96 * std.error,
             conf.high      = estimate + 1.96 * std.error,
             site_id        = SITE_ID,
             model_version  = "sa2a_exclude_covid_2020_2021",
             years_excluded = "2020, 2021",
             n_rows         = nrow(df_sa2a))
    cat("SA2a complete.\n")
    coef_sa2a %>% filter(grepl("defined_w_lactic", term)) %>%
      kable(digits = 4, caption = "SA2a — key terms (log-OR scale)")
  } else {
    coef_sa2a <- NULL
    warning("SA2a failed to fit.")
  }
}
```

```{r sensitivity-sa2b}
# SA2b: Year-by-year stratification (exploratory) ──────────────────────────────
cat("Fitting SA2b: year-by-year stratified models\n")

years_available <- sort(unique(df_model$year))
cat(paste("SA2b: fitting models for years:", paste(years_available, collapse = ", "), "\n"))

coef_sa2b_list <- map(years_available, function(yr) {
  d <- filter(df_model, year == yr)
  cat(paste("SA2b - year", yr, ": n =", nrow(d), "rows\n"))

  yr_zero_var <- c("hospital_type", "sex", "year") %>%
    purrr::keep(~ {
      col <- d[[.x]]
      if (is.factor(col)) nlevels(droplevels(col)) < 2
      else length(unique(col[!is.na(col)])) < 2
    })

  yr_covariates <- setdiff(covariate_terms, c(yr_zero_var, "year"))
  yr_formula    <- reformulate(
    termlabels = c("defined_w_lactic * lactate_vol_scaled", yr_covariates,
                   if (re_structure != "single_hospital") "(1 | hospital_id)" else NULL),
    response = "outcome"
  )

  yr_warning <- NULL
  fit <- if (re_structure == "single_hospital") {
    tryCatch(
      glm(yr_formula, data = d, family = binomial),
      error = function(e) { warning("SA2b year ", yr, " ERROR: ", e$message); NULL }
    )
  } else {
    withCallingHandlers(
      tryCatch(
        glmer(yr_formula, data = d, family = binomial,
              control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))),
        error = function(e) { warning("SA2b year ", yr, " ERROR: ", e$message); NULL }
      ),
      warning = function(w) {
        yr_warning <<- w$message
        message("SA2b year ", yr, " WARNING: ", w$message)
        invokeRestart("muffleWarning")
      }
    )
  }

  if (is.null(fit)) return(NULL)

  vcov_yr     <- vcovCL(fit, cluster = d$hospitalization_id)
  coef_yr_raw <- coeftest(fit, vcov = vcov_yr)
  tidy_coeftest(coef_yr_raw) %>%
    mutate(conf.low            = estimate - 1.96 * std.error,
           conf.high           = estimate + 1.96 * std.error,
           site_id             = SITE_ID,
           model_version       = "sa2b_year_stratified",
           year                = yr,
           n_rows              = nrow(d),
           convergence_warning = !is.null(yr_warning))
})

coef_sa2b <- bind_rows(coef_sa2b_list)
cat(paste("SA2b complete:", length(coef_sa2b_list), "year-specific models attempted.\n"))
coef_sa2b %>% filter(grepl("defined_w_lactic", term)) %>%
  kable(digits = 4, caption = "SA2b — key terms by year (log-OR scale)")
```

```{r sensitivity-sa3}
# SA3: Within-year centered lactate volume ─────────────────────────────────────
cat("Fitting SA3: within-year centered lactate volume\n")

df_sa3 <- df_model
formula_sa3 <- reformulate(
  termlabels = c("defined_w_lactic * lactate_volume_centered",
                 setdiff(covariate_terms, "year"),
                 if (re_structure != "single_hospital") "(1 | hospital_id)" else NULL),
  response = "outcome"
)

sa3_warning <- NULL
model_sa3 <- withCallingHandlers(
  tryCatch(
    if (re_structure == "single_hospital")
      glm(formula_sa3, data = df_sa3, family = binomial)
    else
      glmer(formula_sa3, data = df_sa3, family = binomial,
            control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))),
    error = function(e) { warning("SA3 ERROR: ", e$message); NULL }
  ),
  warning = function(w) {
    sa3_warning <<- w$message
    message("SA3 WARNING: ", w$message)
    invokeRestart("muffleWarning")
  }
)

if (!is.null(model_sa3)) {
  vcov_sa3     <- vcovCL(model_sa3, cluster = df_sa3$hospitalization_id)
  coef_sa3_raw <- coeftest(model_sa3, vcov = vcov_sa3)
  coef_sa3 <- tidy_coeftest(coef_sa3_raw) %>%
    mutate(conf.low         = estimate - 1.96 * std.error,
           conf.high        = estimate + 1.96 * std.error,
           site_id          = SITE_ID,
           model_version    = "sa3_centered_lactate",
           centering_method = centering_method)
  cat("SA3 complete.\n")
  coef_sa3 %>% filter(grepl("defined_w_lactic", term)) %>%
    kable(digits = 4, caption = "SA3 — key terms (log-OR scale)")
} else {
  coef_sa3 <- NULL
  warning("SA3 failed to fit.")
}
```

```{r sensitivity-sa4}
# SA4: Hospital fixed effects (skipped at single-hospital sites) ───────────────
cat("Fitting SA4: hospital fixed effects + clustered SEs\n")

if (n_hospitals == 1) {
  cat("SA4 skipped: hospital fixed effects not estimable with a single hospital.\n")
  coef_sa4 <- NULL
} else {
  formula_sa4 <- reformulate(
    termlabels = c("defined_w_lactic * lactate_vol_scaled", covariate_terms, "hospital_id"),
    response   = "outcome"
  )
  model_sa4 <- tryCatch(
    glm(formula_sa4, data = df_model, family = binomial),
    error = function(e) { warning("SA4 ERROR: ", e$message); NULL }
  )
  if (!is.null(model_sa4)) {
    vcov_sa4     <- vcovCL(model_sa4, cluster = df_model$hospitalization_id)
    coef_sa4_raw <- coeftest(model_sa4, vcov = vcov_sa4)
    coef_sa4 <- tidy_coeftest(coef_sa4_raw) %>%
      mutate(conf.low      = estimate - 1.96 * std.error,
             conf.high     = estimate + 1.96 * std.error,
             site_id       = SITE_ID,
             model_version = "sa4_fixed_effects_hospital_clustered_se")
    cat("SA4 complete.\n")
    coef_sa4 %>% filter(grepl("defined_w_lactic", term)) %>%
      kable(digits = 4, caption = "SA4 — key terms (log-OR scale)")
  } else {
    coef_sa4 <- NULL
    warning("SA4 failed to fit.")
  }
}
```

---

# Section 6 — Output Assembly & Export

```{r export-compile}
# 6.1 Compile output list ───────────────────────────────────────────────────────
output_list <- list(
  # Site metadata
  site_id              = SITE_ID,
  model_version_used   = re_structure,
  interaction_type     = interaction_type,
  n_hospitals          = n_hospitals,
  cor_lactate_year     = cor_lactate_year,
  dropped_covariates   = zero_var_covariates,
  lactate_mean         = lactate_center,
  lactate_sd           = lactate_scale,
  # Primary model
  coef_primary         = coef_table,
  vcov_primary         = vcov_matrix,
  # Descriptive tables
  cohort_summary       = cohort_summary,
  ase_rate_by_year     = ase_rate_by_year,
  hosp_year_summary    = hosp_year_summary,
  group_summary        = group_summary,
  group_clinical       = group_clinical,
  # Sensitivity analyses
  coef_sa1             = coef_sa1,
  coef_sa2a            = coef_sa2a,
  coef_sa2b            = coef_sa2b,
  coef_sa3             = coef_sa3,
  coef_sa4             = coef_sa4,
  # Figures
  fig_lactate_trend    = fig_lactate_trend,
  fig_ase_gap          = fig_ase_gap,
  fig_group_dist       = fig_group_dist,
  fig_clinical_profile = fig_clinical_profile
)

# 6.2 Export CSVs ───────────────────────────────────────────────────────────────
write_csv(baseline_completeness,
          file.path(OUTPUT_DIR, "diagnostics", paste0(SITE_ID, "_01_baseline_completeness.csv")))
write_csv(
  tibble(site_id = SITE_ID, cor_lactate_year = cor_lactate_year,
         collinearity_flag = abs(cor_lactate_year) > 0.7),
  file.path(OUTPUT_DIR, "diagnostics", paste0(SITE_ID, "_02_cor_lactate_year.csv")))

write_csv(cohort_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_01_cohort_summary.csv")))
write_csv(ase_rate_by_year,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_02_ase_rate_by_year.csv")))
write_csv(hosp_year_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_03_hosp_year_lactate_summary.csv")))
write_csv(group_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_04_patient_group_distribution.csv")))
write_csv(group_clinical,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_05_clinical_profile_by_group.csv")))

if (!is.null(coef_table))  write_csv(coef_table,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_06_primary_model_coefs.csv")))
if (!is.null(vcov_matrix)) write_csv(as.data.frame(vcov_matrix),
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_07_primary_vcov_clustered.csv")))

if (!is.null(coef_sa1))  write_csv(coef_sa1,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_08_sa1_lactate_ordered_coefs.csv")))
if (!is.null(coef_sa2a)) write_csv(coef_sa2a,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_09_sa2a_exclude_covid_coefs.csv")))
if (!is.null(coef_sa2b) && nrow(coef_sa2b) > 0) write_csv(coef_sa2b,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_10_sa2b_year_stratified_coefs.csv")))
if (!is.null(coef_sa3))  write_csv(coef_sa3,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_11_sa3_centered_lactate_coefs.csv")))
if (!is.null(coef_sa4))  write_csv(coef_sa4,
  file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_12_sa4_hospital_fixed_effects_coefs.csv")))

cat("CSV exports complete.\n")

# 6.3 Save RDS + JSON bundle ────────────────────────────────────────────────────
saveRDS(output_list,
        file = file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_ASE_results.rds")))

output_json <- output_list
# Strip ggplot objects — not JSON-serializable; use PNG exports instead
output_json[c("fig_lactate_trend", "fig_ase_gap",
              "fig_group_dist", "fig_clinical_profile")] <- NULL
output_json$vcov_primary <- if (!is.null(vcov_matrix)) as.data.frame(vcov_matrix) else NULL

write_json(output_json,
           path   = file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_ASE_results.json")),
           pretty = TRUE, auto_unbox = TRUE, na = "null")

cat("RDS and JSON exports complete.\n")
cat(paste0("All outputs saved to ", OUTPUT_DIR, " — share entire folder with coordinating center.\n"))
```

---

# Session Info

```{r session-info}
writeLines(capture.output(sessionInfo()),
           file.path(OUTPUT_DIR, "diagnostics", paste0(SITE_ID, "_session_info.txt")))
sessionInfo()
```

---

# Output File Summary

The following files have been saved to the `<output_directory>/` directory (as configured in `clif_config.json`) for return to the coordinating center.

**Diagnostics (return all):**

- `<output_directory>/diagnostics/[SITE]_01_baseline_completeness.csv`
- `<output_directory>/diagnostics/[SITE]_02_cor_lactate_year.csv`
- `<output_directory>/diagnostics/[SITE]_session_info.txt`

**Tables (return all):**

- `<output_directory>/tables/[SITE]_01_cohort_summary.csv`
- `<output_directory>/tables/[SITE]_02_ase_rate_by_year.csv`
- `<output_directory>/tables/[SITE]_03_hosp_year_lactate_summary.csv`
- `<output_directory>/tables/[SITE]_04_patient_group_distribution.csv`
- `<output_directory>/tables/[SITE]_05_clinical_profile_by_group.csv`

**Models (return all):**

- `<output_directory>/models/[SITE]_06_primary_model_coefs.csv` — **primary result**
- `<output_directory>/models/[SITE]_07_primary_vcov_clustered.csv`
- `<output_directory>/models/[SITE]_08_sa1_lactate_ordered_coefs.csv`
- `<output_directory>/models/[SITE]_09_sa2a_exclude_covid_coefs.csv`
- `<output_directory>/models/[SITE]_10_sa2b_year_stratified_coefs.csv`
- `<output_directory>/models/[SITE]_11_sa3_centered_lactate_coefs.csv`
- `<output_directory>/models/[SITE]_12_sa4_hospital_fixed_effects_coefs.csv`
- `<output_directory>/models/[SITE]_ASE_results.rds` — full output bundle
- `<output_directory>/models/[SITE]_ASE_results.json`

**Figures (return if flagged issues):**

- `<output_directory>/figures/[SITE]_fig1_lactate_ase_trend.png`
- `<output_directory>/figures/[SITE]_fig2_ase_rate_gap.png`
- `<output_directory>/figures/[SITE]_fig3_patient_group_distribution.png`
- `<output_directory>/figures/[SITE]_fig4_clinical_profile.png`
