---
title: "ASE Definition Comparison: Site-Level Analysis"

format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    theme: cosmo
    embed-resources: true
    fig-width: 9
    fig-height: 6
execute:
  warning: false
  message: false
  echo: true
---

# Overview

This document implements the pre-specified analysis for the ASE Definition Comparison study. Sites should run this document from top to bottom without modification. All outputs are saved to the directory specified by `output_directory` in `clif_config.json` for return to the coordinating center.

**Study Question:** Does hospital-level lactate ordering intensity explain the gap between core and extended CDC Adult Sepsis Event (ASE) rates?

**Design:**

- **Exposure:** Lactate ordering intensity (orders per 1,000 patient-days), hospital-year level
- **Outcome:** Two separate binary logistic models on one-row-per-hospitalization data:
  - **Model A:** `sepsis_core` (1) vs `no_sepsis` (0)
  - **Model B:** `sepsis_extended` (1) vs `no_sepsis` (0)
- **Method:** `glmer` with hospital random intercept for multi-hospital sites; `glm` with clustered SEs for single-hospital sites
- **Primary estimand:** Contrast between `lactate_vol_scaled` coefficient in Model B minus Model A — does the gap between definitions widen at higher-testing hospitals?
- **Contrast SE:** Conservative approximation `sqrt(Var_B + Var_A)` — assumes independence between models; slightly wider than exact SE since positive cross-model covariance is not subtracted

**Required data file:** `analysis_dataset.parquet` in the `phi_directory` specified in `clif_config.json`

**Required variables:**

| Variable | Description |
|---|---|
| `hospitalization_id` | Unique hospitalization identifier |
| `hospital_id` | Facility identifier |
| `defined_w_lactic` | 0 = core ASE definition, 1 = extended (includes lactate criterion) |
| `ASE` | 1 = meets ASE criteria under this definition, 0 = does not |
| `lactate_order_per_1000_patient_days` | Hospital-year lactate ordering intensity |
| `worst_sofa_admission_to_24h` | SOFA score (0–24h from blood culture/antibiotic anchor) |
| `age`, `sex`, `cci` | Patient demographics and comorbidity |
| `hospital_type` | community or academic |
| `year` | Calendar year |
| `hospitalizations_from_ed_per_year` | Hospital-year ED volume |
| `any_lactate_ordered` | 1 = any lactate ordered during hospitalization |

---

# Section 0 — Setup

```{r setup}
library(tidyverse)
library(lme4)       # glmer() — binary logistic with RE (multi-hospital path)
library(sandwich)   # vcovCL() — clustered SEs (single-hospital path)
library(lmtest)     # coeftest()
library(jsonlite)
library(arrow)
library(here)
library(gtsummary)
library(broom)
library(broom.mixed)  # tidy() for glmerMod objects (glmer path)
library(scales)
library(knitr)

set.seed(20240101)

# ── Site configuration (from clif_config.json) ────────────────────────────────
config     <- fromJSON(here("clif_config.json"))
SITE_ID    <- config$site_name
DATA_PATH  <- here(config$phi_directory, "analysis_dataset.parquet")
OUTPUT_DIR <- here(config$output_directory)
# ─────────────────────────────────────────────────────────────────────────────

# Modeling approach — two paths:
#   >= 2 hospitals -> glmer with hospital RE (1 | hospital_id_deident), model-based SEs
#   1 hospital     -> glm with clustered SEs on hospitalization_id (sandwich HC0)


# Create output directories
dir.create(file.path(OUTPUT_DIR, "figures"),     showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "tables"),      showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "diagnostics"), showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(OUTPUT_DIR, "models"),      showWarnings = FALSE, recursive = TRUE)

# ── Helper functions ──────────────────────────────────────────────────────────

# Fit a single binary logistic model (glmer or glm) with consistent error/warning handling. Returns NULL on error.
# warn_var:   name of variable in parent frame to store convergence warning
fit_binary <- function(formula, data, model_path, warn_var = "fit_warning") {
  assign(warn_var, NULL, envir = parent.frame())

  if (model_path == "glmer") {
    withCallingHandlers(
      tryCatch(
        glmer(formula, data = data, family = binomial,
              control = glmerControl(optimizer = "bobyqa",
                                     optCtrl   = list(maxfun = 2e5))),
        error = function(e) { warning(e$message); NULL }
      ),
      warning = function(w) {
        assign(warn_var, w$message, envir = parent.frame(3))
        message(warn_var, " WARNING: ", w$message)
        invokeRestart("muffleWarning")
      }
    )
  } else {
    tryCatch(
      glm(formula, data = data, family = binomial),
      error = function(e) { warning(e$message); NULL }
    )
  }
}

# Extract vcov from a fitted model.
# glmer: model-based vcov from GLMM likelihood (fixed effects only).
# glm:   cluster-robust HC0 vcov via sandwich::vcovCL on hospitalization_id.
#        Subsets cluster vector to rows actually used in model fit (NA-safe).
get_model_vcov <- function(model, model_path, data) {
  if (model_path == "glmer") {
    as.matrix(vcov(model))
  } else {
    used_rows <- as.integer(rownames(model.frame(model)))
    sandwich::vcovCL(model,
                     cluster = data$hospitalization_id[used_rows],
                     type    = "HC0")
  }
}

# Tidy a fitted glmer or glm model into a clean data frame.
# Returns NULL if model is NULL.
#   SEs are model-based from the GLMM likelihood; vcov_mat is still returned
#   by get_model_vcov() and used downstream in compute_contrast().

tidy_binary <- function(model, vcov_mat) {
  if (is.null(model)) return(NULL)

  if (inherits(model, "glmerMod")) {
    broom.mixed::tidy(model, effects = "fixed") %>%
      select(term, estimate, std.error, statistic, p.value) %>%
      mutate(conf.low  = estimate - 1.96 * std.error,
             conf.high = estimate + 1.96 * std.error)
  } else {
    broom::tidy(lmtest::coeftest(model, vcov = vcov_mat)) %>%
      mutate(conf.low  = estimate - 1.96 * std.error,
             conf.high = estimate + 1.96 * std.error)
  }
}

# Compute primary contrast from two tidy coefficient tables.
# contrast = lactate_vol_scaled coef(model_b) - coef(model_a)
compute_contrast <- function(coef_a, coef_b, vcov_a, vcov_b,
                             lactate_term = "lactate_vol_scaled") {
  if (is.null(coef_a) || is.null(coef_b)) return(NULL)

  est_a <- coef_a %>% filter(term == lactate_term) %>% pull(estimate)
  est_b <- coef_b %>% filter(term == lactate_term) %>% pull(estimate)

  if (length(est_a) == 0 || length(est_b) == 0) {
    warning("compute_contrast: '", lactate_term, "' not found in one or both models.")
    return(NULL)
  }

  contrast_est <- est_b - est_a

  # SE from vcov diagonal — conservative (ignores cross-model covariance)
  var_a <- tryCatch(vcov_a[lactate_term, lactate_term],
                    error = function(e) NA_real_)
  var_b <- tryCatch(vcov_b[lactate_term, lactate_term],
                    error = function(e) NA_real_)
  contrast_se <- sqrt(var_a + var_b)

  tibble(
    contrast_estimate    = contrast_est,
    contrast_se          = contrast_se,
    contrast_ci_low      = contrast_est - 1.96 * contrast_se,
    contrast_ci_high     = contrast_est + 1.96 * contrast_se,
    contrast_z           = contrast_est / contrast_se,
    contrast_p           = 2 * pnorm(abs(contrast_est / contrast_se),
                                     lower.tail = FALSE),
    se_approximation     = "conservative — cross-model covariance not subtracted",
    lactate_coef_model_a = est_a,
    lactate_coef_model_b = est_b
  )
}

# Add standard metadata columns to a tidy coefficient table
add_metadata <- function(coef_df, model_version, site_id, n_hospitals,
                         n_hospitalizations, lactate_center, lactate_scale,
                         year_center, centering_method, zero_var_covariates,
                         warn_a = NULL, warn_b = NULL) {
  coef_df %>%
    mutate(
      site_id               = site_id,
      model_version         = model_version,
      n_hospitals           = n_hospitals,
      n_hospitalizations    = n_hospitalizations,
      lactate_mean          = lactate_center,
      lactate_sd            = lactate_scale,
      year_center           = year_center,
      centering_method      = centering_method,
      dropped_covariates    = paste(zero_var_covariates, collapse = ", "),
      convergence_warn_a    = !is.null(warn_a),
      convergence_warn_b    = !is.null(warn_b)
    )
}

# Helper: write CSV only if object is non-null and non-empty
write_if <- function(x, path) {
  if (!is.null(x) && is.data.frame(x) && nrow(x) > 0)
    write_csv(x, path)
}

# Extract between-hospital random-intercept variance from a glmer fit.
# Returns a one-row tibble with RE sigma^2 and sigma (SD).
# glm path (single-hospital): returns a stub row with NAs and re_available = FALSE.
# Used for two-level heterogeneity reporting at the coordinating center:
#   - Within-site between-hospital variance (this export, multi-hospital sites)
#   - Between-site variance (from meta-analytic pooling of contrast estimates)
extract_re_variance <- function(model, model_label, model_path, site_id) {
  if (model_path == "glmer" && !is.null(model)) {
    vc      <- as.data.frame(VarCorr(model))
    re_row  <- vc[vc$grp == "hospital_id_deident", ]
    tibble(
      site_id      = site_id,
      model_label  = model_label,
      re_sigma2    = if (nrow(re_row) > 0) re_row$vcov[1]  else NA_real_,
      re_sigma     = if (nrow(re_row) > 0) re_row$sdcor[1] else NA_real_,
      re_available = nrow(re_row) > 0
    )
  } else {
    tibble(
      site_id      = site_id,
      model_label  = model_label,
      re_sigma2    = NA_real_,
      re_sigma     = NA_real_,
      re_available = FALSE
    )
  }
}

# Load data
df_raw <- read_parquet(DATA_PATH)

cat("Data loaded:", nrow(df_raw), "rows,", ncol(df_raw), "columns\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")
```

---

# Section 1 — Data Quality Checks

```{r data-quality}
# 1.1 Overall structure
cat("Rows:", nrow(df_raw), "\n")
cat("Columns:", ncol(df_raw), "\n")
cat("Unique hospitalizations:", n_distinct(df_raw$hospitalization_id), "\n")
cat("Unique hospitals:", n_distinct(df_raw$hospital_id), "\n")

# 1.2 Missing data
missing_summary <- df_raw %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(pct_missing = round(n_missing / nrow(df_raw) * 100, 1)) %>%
  filter(n_missing > 0)

cat("\nMissing data summary (variables with any missing):\n")
print(missing_summary)

baseline_completeness <- df_raw %>%
  summarise(
    n                     = n(),
    age_miss              = sum(is.na(age)),
    sex_miss              = sum(is.na(sex)),
    cci_miss              = sum(is.na(cci)),
    sofa_miss             = sum(is.na(worst_sofa_admission_to_24h)),
    hosp_type_miss        = sum(is.na(hospital_type)),
    lactate_vol_miss      = sum(is.na(lactate_order_per_1000_patient_days)),
    year_miss             = sum(is.na(year)),
    ASE_miss              = sum(is.na(ASE)),
    defined_w_lactic_miss = sum(is.na(defined_w_lactic))
  )

kable(baseline_completeness, caption = "Baseline completeness — key analysis variables")
write_csv(baseline_completeness,
          file.path(OUTPUT_DIR, "diagnostics", "01_baseline_completeness.csv"))

# 1.3 Structure
cat("\nData structure:\n")
str(df_raw)

# 1.4 Two-row structure check (expected pre-pivot)
row_counts <- df_raw %>%
  count(hospitalization_id) %>%
  count(n, name = "n_encounters")

cat("\nRows per hospitalization_id in raw data (expect all = 2):\n")
kable(row_counts, caption = "Expected: all hospitalizations should have exactly 2 rows")
```

---

# Section 2 — Derived Variables & Wide Format Pivot

```{r derived-variables}
# 2.1 Pivot to wide — one row per hospitalization ──────────────────────────────
# patient_group:
#   sepsis_core         ASE=1 core AND ASE=1 extended (logically required)
#   sepsis_extended     ASE=0 core, ASE=1 extended — captured only by lactate criterion
#   no_sepsis           ASE=0 both definitions
#   check_data_quality  ASE=1 core, ASE=0 extended — logically impossible; flagged then dropped

df_wide <- df_raw %>%
  select(hospitalization_id, hospital_id, defined_w_lactic, ASE,
         lactate_order_per_1000_patient_days, worst_sofa_admission_to_24h,
         age, sex, cci, hospital_type, year,
         hospitalizations_from_ed_per_year, any_lactate_ordered) %>%
  pivot_wider(
    id_cols      = c(hospitalization_id, hospital_id,
                     lactate_order_per_1000_patient_days,
                     worst_sofa_admission_to_24h, age, sex, cci,
                     hospital_type, year,
                     hospitalizations_from_ed_per_year, any_lactate_ordered),
    names_from   = defined_w_lactic,
    values_from  = ASE,
    names_prefix = "ASE_def_"
  ) %>%
  mutate(
    patient_group = case_when(
      ASE_def_0 == 1 & ASE_def_1 == 1 ~ "sepsis_core",
      ASE_def_0 == 0 & ASE_def_1 == 1 ~ "sepsis_extended",
      ASE_def_0 == 0 & ASE_def_1 == 0 ~ "no_sepsis",
      ASE_def_0 == 1 & ASE_def_1 == 0 ~ "check_data_quality",
      TRUE                             ~ NA_character_
    )
  )

cat("Wide format: one row per hospitalization\n")
cat("Total hospitalizations:", nrow(df_wide), "\n")

# 2.2 QC table — flag check_data_quality before exclusion ──────────────────────
n_check_dq <- sum(df_wide$patient_group == "check_data_quality", na.rm = TRUE)
cat(paste("\ncheck_data_quality encounters:", n_check_dq, "\n"))

qc_table <- df_wide %>%
  count(patient_group) %>%
  mutate(
    pct                  = round(n / sum(n) * 100, 2),
    included_in_analysis = patient_group != "check_data_quality"
  )

kable(qc_table, caption = "Patient group distribution including QC flag (pre-exclusion)")
write_csv(qc_table,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_02_patient_group_qc.csv")))

if (n_check_dq > 0)
  warning(n_check_dq, " check_data_quality encounters excluded. ",
          "Review data pipeline if unexpectedly large.")

# 2.3 Exclude check_data_quality and set factor levels ─────────────────────────
df <- df_wide %>%
  filter(patient_group != "check_data_quality") %>%
  mutate(
    patient_group = factor(patient_group,
                           levels = c("no_sepsis", "sepsis_core", "sepsis_extended")),
    hospital_type = factor(hospital_type, levels = c("community", "academic")),
    sex           = factor(sex,           levels = c("Male", "Female")),
    year_f        = factor(year)
  )

cat(paste("Analytic dataset after exclusions:", nrow(df), "hospitalizations\n"))

# 2.4 Collinearity diagnostic: lactate volume vs year ──────────────────────────
cor_lactate_year <- cor(df$lactate_order_per_1000_patient_days, df$year,
                        use = "complete.obs")
cat(paste("\nPearson r (lactate_order_per_1000_patient_days ~ year):",
          round(cor_lactate_year, 3), "\n"))
if (abs(cor_lactate_year) > 0.7)
  warning("r > 0.7 — strong collinearity. Review SA3 (centered lactate) carefully.")

# 2.5 Hospital count and modeling path ─────────────────────────────────────────
n_hospitals      <- n_distinct(df$hospital_id)
re_structure     <- ifelse(n_hospitals >= 2, "glmer_re",            "glm_clustered_se")
model_path       <- ifelse(n_hospitals >= 2, "glmer",               "glm")
interaction_type <- ifelse(n_hospitals >= 2, "between_hospital",    "within_hospital_temporal")

cat(paste("Number of hospitals:", n_hospitals, "\n"))
cat(paste("Modeling path:", re_structure, "\n"))
cat(paste("Interaction type:", interaction_type, "\n"))

# 2.6 Within-year centering for SA3 ───────────────────────────────────────────
if (n_hospitals >= 2) {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    group_by(year) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    ) %>%
    ungroup()
  centering_method <- "within_year"
} else {
  hospital_year_stats <- df %>%
    distinct(hospital_id, year, lactate_order_per_1000_patient_days) %>%
    mutate(
      lactate_volume_year_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
      lactate_volume_centered  = lactate_order_per_1000_patient_days - lactate_volume_year_mean
    )
  centering_method <- "grand_mean"
  cat("Single-hospital site: grand-mean centering used for SA3.\n")
}

df <- df %>%
  left_join(
    hospital_year_stats %>%
      select(hospital_id, year, lactate_volume_centered, lactate_volume_year_mean),
    by = c("hospital_id", "year")
  )

n_missing_centered <- sum(is.na(df$lactate_volume_centered))
if (n_missing_centered > 0)
  warning(n_missing_centered, " rows missing lactate_volume_centered after join. ",
          "SA3 will run on reduced sample.")

cat(paste("Centering method:", centering_method, "\n"))

# 2.7 Hospital de-identification ───────────────────────────────────────────────
hosp_crosswalk <- df %>%
  distinct(hospital_id) %>%
  arrange(hospital_id) %>%
  mutate(hospital_id_deident = row_number())

cat("\nHospital de-identification crosswalk (local reference — not exported):\n")
print(hosp_crosswalk)
cat("DO NOT share hospital identity mapping with the coordinating center.\n")

df <- df %>% left_join(hosp_crosswalk, by = "hospital_id")
cat(paste("De-identified IDs assigned:", n_distinct(df$hospital_id_deident), "hospitals\n"))
```

---

# Section 3 — Descriptive Statistics

```{r descriptives}
# 3.1 Cohort summary
cohort_summary <- df %>%
  summarise(
    n_hospitalizations  = n(),
    n_hospitals         = n_distinct(hospital_id_deident),
    n_years             = n_distinct(year),
    year_range          = paste(min(year), max(year), sep = "-"),
    median_age          = median(age,  na.rm = TRUE),
    pct_female          = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
    median_cci          = median(cci,  na.rm = TRUE),
    pct_academic        = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1),
    n_sepsis_core       = sum(patient_group == "sepsis_core"),
    n_sepsis_extended   = sum(patient_group == "sepsis_extended"),
    n_no_sepsis         = sum(patient_group == "no_sepsis"),
    pct_sepsis_core     = round(mean(patient_group == "sepsis_core")     * 100, 1),
    pct_sepsis_extended = round(mean(patient_group == "sepsis_extended") * 100, 1)
  )

kable(cohort_summary, caption = "Overall cohort summary")

# 3.2 Patient group distribution
group_summary <- df %>%
  count(patient_group) %>%
  mutate(pct = round(n / sum(n) * 100, 1))

kable(group_summary, caption = "Patient group distribution (analytic dataset)")

# 3.3 ASE rate by year
ase_rate_by_year <- df %>%
  group_by(year) %>%
  summarise(
    n                   = n(),
    n_sepsis_core       = sum(patient_group == "sepsis_core"),
    n_sepsis_extended   = sum(patient_group == "sepsis_extended"),
    pct_sepsis_core     = round(mean(patient_group == "sepsis_core")     * 100, 1),
    pct_sepsis_extended = round(mean(patient_group == "sepsis_extended") * 100, 1),
    gap_pct_points      = pct_sepsis_extended - pct_sepsis_core,
    .groups             = "drop"
  )

kable(ase_rate_by_year, caption = "ASE rate by year and definition")

# 3.4 Hospital-year lactate volume summary (year-level)
hosp_year_summary <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days) %>%
  group_by(year) %>%
  summarise(
    n_hospitals      = n(),
    mean_lactate_vol = round(mean(lactate_order_per_1000_patient_days, na.rm = TRUE), 1),
    sd_lactate_vol   = round(sd(lactate_order_per_1000_patient_days,   na.rm = TRUE), 1),
    min_lactate_vol  = round(min(lactate_order_per_1000_patient_days,  na.rm = TRUE), 1),
    max_lactate_vol  = round(max(lactate_order_per_1000_patient_days,  na.rm = TRUE), 1),
    .groups          = "drop"
  )

kable(hosp_year_summary, caption = "Hospital-year lactate volume summary")

# 3.5 Clinical profile by patient group (sepsis cases only)
group_clinical <- df %>%
  filter(patient_group %in% c("sepsis_core", "sepsis_extended")) %>%
  group_by(patient_group) %>%
  summarise(
    n            = n(),
    median_age   = median(age,  na.rm = TRUE),
    pct_female   = round(mean(sex == "Female", na.rm = TRUE) * 100, 1),
    median_cci   = median(cci,  na.rm = TRUE),
    median_sofa  = median(worst_sofa_admission_to_24h, na.rm = TRUE),
    pct_academic = round(mean(hospital_type == "academic", na.rm = TRUE) * 100, 1),
    .groups      = "drop"
  )

kable(group_clinical, caption = "Clinical profile by patient group (sepsis cases only)")

# 3.6 Hospital-year lactate detail (one row per hospital per year)
hosp_year_detail <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days) %>%
  arrange(hospital_id_deident, year) %>%
  rename(lactate_vol = lactate_order_per_1000_patient_days)

kable(hosp_year_detail, caption = "Hospital-year lactate volume detail (de-identified)")

# 3.7 Hospital-year ASE rates (one row per hospital per year)
hosp_year_ase <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    n_hospitalizations  = n(),
    n_sepsis_core       = sum(patient_group == "sepsis_core"),
    n_sepsis_extended   = sum(patient_group == "sepsis_extended"),
    pct_sepsis_core     = round(mean(patient_group == "sepsis_core")     * 100, 1),
    pct_sepsis_extended = round(mean(patient_group == "sepsis_extended") * 100, 1),
    gap_pct_points      = pct_sepsis_extended - pct_sepsis_core,
    .groups             = "drop"
  ) %>%
  arrange(hospital_id_deident, year)

kable(hosp_year_ase, caption = "Hospital-year ASE rates by patient group (de-identified)")
```

```{r fig-lactate-trend, fig.height=5.5}
# 3.8 Figure: Lactate ordering intensity over time
hosp_year_plot_data <- df %>%
  distinct(hospital_id_deident, year, lactate_order_per_1000_patient_days)

site_mean_by_year <- hosp_year_plot_data %>%
  group_by(year) %>%
  summarise(site_mean = mean(lactate_order_per_1000_patient_days, na.rm = TRUE),
            .groups = "drop")

ase_rate_plot <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    rate_core     = mean(patient_group == "sepsis_core",     na.rm = TRUE),
    rate_extended = mean(patient_group == "sepsis_extended", na.rm = TRUE),
    .groups = "drop"
  )

lactate_range <- range(hosp_year_plot_data$lactate_order_per_1000_patient_days, na.rm = TRUE)
scale_factor  <- diff(lactate_range)
scale_offset  <- lactate_range[1]

fig_lactate_trend <- ggplot() +
  geom_line(data  = hosp_year_plot_data,
            aes(x = year, y = lactate_order_per_1000_patient_days,
                group = hospital_id_deident),
            color = "steelblue", alpha = 0.45, linewidth = 0.6) +
  geom_point(data = hosp_year_plot_data,
             aes(x = year, y = lactate_order_per_1000_patient_days,
                 group = hospital_id_deident),
             color = "steelblue", alpha = 0.45, size = 1.2) +
  geom_line(data  = site_mean_by_year,
            aes(x = year, y = site_mean),
            color = "steelblue", linewidth = 1.2) +
  geom_point(data = site_mean_by_year,
             aes(x = year, y = site_mean),
             color = "steelblue", size = 2.2) +
  geom_line(data  = ase_rate_plot,
            aes(x = year, y = rate_core * scale_factor + scale_offset,
                group = hospital_id_deident),
            color = "firebrick", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  geom_line(data  = ase_rate_plot,
            aes(x = year, y = rate_extended * scale_factor + scale_offset,
                group = hospital_id_deident),
            color = "darkorange", alpha = 0.45, linewidth = 0.6, linetype = "dashed") +
  scale_y_continuous(
    name     = "Lactate Orders per 1,000 Patient-Days",
    sec.axis = sec_axis(transform = ~ (. - scale_offset) / scale_factor,
                        name      = "ASE Rate (proportion)")
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Lactate Ordering Intensity and ASE Rate Over Time (", SITE_ID, ")"),
       subtitle = "Blue = lactate volume (solid = site mean); Red dashed = core ASE rate; Orange dashed = extended ASE rate",
       x = "Year") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        axis.title.y.left  = element_text(color = "steelblue"),
        axis.text.y.left   = element_text(color = "steelblue"),
        axis.title.y.right = element_text(color = "firebrick"),
        axis.text.y.right  = element_text(color = "firebrick"))

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig1_lactate_ase_trend.png")),
       plot = fig_lactate_trend, width = 9, height = 5.5, dpi = 300)
fig_lactate_trend
```

```{r fig-ase-gap}
# 3.9 Figure: ASE rate gap over time
ase_gap_by_hosp_year <- df %>%
  group_by(hospital_id_deident, year) %>%
  summarise(
    pct_core     = mean(patient_group == "sepsis_core",     na.rm = TRUE) * 100,
    pct_extended = mean(patient_group == "sepsis_extended", na.rm = TRUE) * 100,
    gap          = pct_extended - pct_core,
    .groups      = "drop"
  )

fig_ase_gap <- ggplot() +
  { if (n_hospitals > 1)
    geom_line(data  = ase_gap_by_hosp_year,
              aes(x = year, y = gap, group = hospital_id_deident),
              color = "grey65", alpha = 0.5, linewidth = 0.6)
  } +
  geom_line(data  = ase_rate_by_year,
            aes(x = year, y = gap_pct_points),
            color = "darkorchid", linewidth = 1.2) +
  geom_point(data = ase_rate_by_year,
             aes(x = year, y = gap_pct_points),
             color = "darkorchid", size = 2.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(title    = paste0("Extended vs Core ASE Rate Gap Over Time (", SITE_ID, ")"),
       subtitle = "Gap = extended minus core ASE rate (pp)\nGrey = individual hospitals; Purple = site mean",
       x = "Year", y = "ASE Rate Gap (percentage points)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"), panel.grid.minor = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig2_ase_rate_gap.png")),
       plot = fig_ase_gap, width = 8, height = 5, dpi = 300)
fig_ase_gap
```

```{r fig-group-dist}
# 3.10 Figure: Patient group distribution
fig_group_dist <- group_summary %>%
  mutate(patient_group = factor(patient_group,
                                levels = c("no_sepsis", "sepsis_core", "sepsis_extended"),
                                labels = c("No Sepsis", "Core Sepsis", "Extended Only"))) %>%
  ggplot(aes(x = patient_group, y = pct, fill = patient_group)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = paste0(pct, "%\n(n=", scales::comma(n), ")")),
            vjust = -0.4, size = 3.5) +
  scale_fill_manual(values = c("No Sepsis"     = "grey75",
                               "Core Sepsis"   = "firebrick",
                               "Extended Only" = "darkorange")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  labs(title    = paste0("Patient Group Distribution (", SITE_ID, ")"),
       subtitle = paste0("N = ", scales::comma(nrow(df)), " unique encounters"),
       x = NULL, y = "Percentage of Encounters (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title         = element_text(face = "bold"),
        panel.grid.minor   = element_blank(),
        panel.grid.major.x = element_blank())

ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig3_patient_group_distribution.png")),
       plot = fig_group_dist, width = 7, height = 5, dpi = 300)
fig_group_dist
```

```{r fig-clinical-profile}
# 3.11 Figure: Clinical profile comparison
if (nrow(group_clinical) == 2) {
  fig_clinical_profile <- group_clinical %>%
    mutate(patient_group = factor(patient_group,
                                  levels = c("sepsis_core", "sepsis_extended"),
                                  labels = c("Core Sepsis", "Extended Only"))) %>%
    select(patient_group, median_age, pct_female, median_cci, median_sofa) %>%
    pivot_longer(-patient_group, names_to = "variable", values_to = "value") %>%
    mutate(variable = recode(variable,
                             "median_age"  = "Median Age (years)",
                             "pct_female"  = "Female (%)",
                             "median_cci"  = "Median CCI",
                             "median_sofa" = "Median SOFA (0-24h)")) %>%
    ggplot(aes(x = value, y = variable, color = patient_group, shape = patient_group)) +
    geom_point(size = 4) +
    scale_color_manual(values = c("Core Sepsis"   = "firebrick",
                                  "Extended Only" = "darkorange")) +
    labs(title    = paste0("Clinical Profile: Core vs Extended-Only Sepsis (", SITE_ID, ")"),
         subtitle = "Median values; Extended-only = meets ASE criteria via lactate criterion only",
         x = "Value", y = NULL, color = NULL, shape = NULL) +
    facet_wrap(~ variable, scales = "free_x", ncol = 2) +
    theme_minimal(base_size = 13) +
    theme(plot.title       = element_text(face = "bold"),
          panel.grid.minor = element_blank(),
          legend.position  = "bottom",
          strip.text       = element_text(face = "bold"))

  ggsave(file.path(OUTPUT_DIR, "figures", paste0(SITE_ID, "_fig4_clinical_profile.png")),
         plot = fig_clinical_profile, width = 8, height = 6, dpi = 300)
  fig_clinical_profile
} else {
  cat("NOTE: Clinical profile figure skipped — one or both sepsis groups absent.\n")
  fig_clinical_profile <- NULL
}
```

---

# Section 4 — Primary Analysis

Two separate binary logistic models. Both fit on the wide-format dataset (one row per hospitalization). `sepsis_extended` cases excluded from Model A; `sepsis_core` cases excluded from Model B.

- **Multi-hospital:** `glmer` with `(1 | hospital_id_deident)`, model-based SEs
- **Single-hospital:** `glm` with sandwich cluster-robust SEs on `hospitalization_id`
- **Primary contrast:** `lactate_vol_scaled` coefficient, Model B minus Model A

```{r primary-analysis}
# 4.1 Prepare model dataset
year_center <- round(mean(df$year, na.rm = TRUE), 2)

df_model <- df %>%
  mutate(
    lactate_vol_scaled = scale(lactate_order_per_1000_patient_days)[, 1],
    year_centered      = year - year_center
  )

lactate_center <- round(attr(scale(df$lactate_order_per_1000_patient_days),
                              "scaled:center"), 2)
lactate_scale  <- round(attr(scale(df$lactate_order_per_1000_patient_days),
                              "scaled:scale"),  2)
cat(paste("Lactate scaling: mean =", lactate_center, "| SD =", lactate_scale, "\n"))
cat(paste("Year centering offset:", year_center, "\n"))

# 4.2 Zero-variance covariate check
zero_var_covariates <- c("worst_sofa_admission_to_24h", "age", "sex", "cci",
                         "hospital_type", "year_centered",
                         "hospitalizations_from_ed_per_year") %>%
  purrr::keep(~ {
    col <- df_model[[.x]]
    if (is.factor(col)) nlevels(droplevels(col)) < 2
    else length(unique(col[!is.na(col)])) < 2
  })

if (length(zero_var_covariates) > 0) {
  warning("Zero-variance covariates dropped: ",
          paste(zero_var_covariates, collapse = ", "))
} else {
  cat("No zero-variance covariates detected.\n")
}

covariate_terms <- setdiff(
  c("worst_sofa_admission_to_24h", "age", "sex", "cci",
    "hospital_type", "year_centered", "hospitalizations_from_ed_per_year"),
  zero_var_covariates
)

# 4.3 Build formulas
# Model A: sepsis_core vs no_sepsis (excludes sepsis_extended)
# Model B: sepsis_extended vs no_sepsis (excludes sepsis_core)
# RE term added only for glmer path
re_term        <- if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL
fixed_rhs      <- c("lactate_vol_scaled", covariate_terms, re_term)
formula_model_a <- reformulate(fixed_rhs, response = "outcome_a")
formula_model_b <- reformulate(fixed_rhs, response = "outcome_b")

cat(paste("Model formula RHS:", deparse(reformulate(fixed_rhs)), "\n"))
cat(paste("Modeling path:", re_structure, "\n"))

# 4.4 Prepare binary outcome datasets
df_model_a <- df_model %>%
  filter(patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_model_b <- df_model %>%
  filter(patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

cat(paste("Model A sample (core vs no_sepsis): n =",
          nrow(df_model_a), "hospitalizations\n"))
cat(paste("Model B sample (extended vs no_sepsis): n =",
          nrow(df_model_b), "hospitalizations\n"))

# 4.5 Fit models
warn_primary_a <- NULL
warn_primary_b <- NULL

model_a <- fit_binary(formula_model_a, df_model_a, model_path,
                      warn_var = "warn_primary_a")
model_b <- fit_binary(formula_model_b, df_model_b, model_path,
                      warn_var = "warn_primary_b")

cat(paste("Model A fit:", ifelse(is.null(model_a), "FAILED", "OK"), "\n"))
cat(paste("Model B fit:", ifelse(is.null(model_b), "FAILED", "OK"), "\n"))

# 4.6 Extract coefficients
vcov_a <- if (!is.null(model_a)) get_model_vcov(model_a, model_path, df_model_a) else NULL
vcov_b <- if (!is.null(model_b)) get_model_vcov(model_b, model_path, df_model_b) else NULL

coef_a_raw <- tidy_binary(model_a, vcov_a)
coef_b_raw <- tidy_binary(model_b, vcov_b)

metadata_args <- list(
  site_id            = SITE_ID,
  n_hospitals        = n_hospitals,
  n_hospitalizations = nrow(df_model),
  lactate_center     = lactate_center,
  lactate_scale      = lactate_scale,
  year_center        = year_center,
  centering_method   = centering_method,
  zero_var_covariates = zero_var_covariates,
  warn_a             = warn_primary_a,
  warn_b             = warn_primary_b
)

coef_a <- if (!is.null(coef_a_raw))
  do.call(add_metadata, c(list(coef_df = coef_a_raw,
                                model_version = paste0(re_structure, "_model_a_core_vs_nosepsis")),
                           metadata_args))

coef_b <- if (!is.null(coef_b_raw))
  do.call(add_metadata, c(list(coef_df = coef_b_raw,
                                model_version = paste0(re_structure, "_model_b_extended_vs_nosepsis")),
                           metadata_args))

# Combine for export
coef_primary <- bind_rows(
  if (!is.null(coef_a)) mutate(coef_a, model_label = "model_a_core_vs_nosepsis"),
  if (!is.null(coef_b)) mutate(coef_b, model_label = "model_b_extended_vs_nosepsis")
)

if (nrow(coef_primary) > 0) {
  cat("\nPrimary model — lactate_vol_scaled coefficients:\n")
  kable(coef_primary %>%
          filter(term == "lactate_vol_scaled") %>%
          select(model_label, estimate, std.error, statistic, p.value,
                 conf.low, conf.high),
        digits = 4,
        caption = "Primary models — lactate_vol_scaled by model (log-OR scale)")
}

# 4.7 Primary contrast
contrast_primary <- compute_contrast(coef_a_raw, coef_b_raw, vcov_a, vcov_b)

if (!is.null(contrast_primary)) {
  contrast_primary <- contrast_primary %>%
    mutate(
      site_id            = SITE_ID,
      model_version      = re_structure,
      n_hospitals        = n_hospitals,
      n_hospitalizations = nrow(df_model),
      blup_available     = (model_path == "glmer")
    )
  cat("\nPrimary contrast (Model B minus Model A lactate coefficient):\n")
  kable(contrast_primary, digits = 4,
        caption = "Primary estimand — contrast on lactate_vol_scaled")
} else {
  warning("Primary contrast could not be computed — one or both models failed.")
}
```

```{r hospital-level-export}
# 4.8 Hospital-level BLUP export
# Multi-hospital: BLUPs from glmer ranef() for both models.
# Single-hospital: one-row stub, blup_available = FALSE.
# All IDs de-identified. No hospital metadata exported.

if (model_path == "glmer" &&
    !is.null(model_a) && !is.null(model_b) &&
    !is.null(contrast_primary)) {

  blup_df <- tryCatch({
    blup_a <- ranef(model_a)$hospital_id_deident %>%
      rownames_to_column("hospital_id_deident") %>%
      rename(blup_a = `(Intercept)`) %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    blup_b <- ranef(model_b)$hospital_id_deident %>%
      rownames_to_column("hospital_id_deident") %>%
      rename(blup_b = `(Intercept)`) %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    hosp_n <- df_model %>%
      group_by(hospital_id_deident) %>%
      summarise(n_hospitalizations_hospital = n(), .groups = "drop") %>%
      mutate(hospital_id_deident = as.integer(hospital_id_deident))

    blup_a %>%
      left_join(blup_b, by = "hospital_id_deident") %>%
      left_join(hosp_n, by = "hospital_id_deident") %>%
      mutate(
        fixef_contrast         = contrast_primary$contrast_estimate,
        # Hospital-specific contrast = fixef contrast + blup_b - blup_a
        hosp_contrast_estimate = fixef_contrast + blup_b - blup_a,
        blup_available         = TRUE,
        blup_se_note           = "approximate — posterior variance not extracted; use for forest plot only",
        site_id                = SITE_ID,
        model_version          = re_structure
      )
  },
  error = function(e) {
    warning("BLUP extraction failed: ", e$message)
    NULL
  })

} else if (model_path == "glm" && !is.null(contrast_primary)) {

  blup_df <- tibble(
    hospital_id_deident         = 1L,
    blup_a                      = NA_real_,
    blup_b                      = NA_real_,
    fixef_contrast              = contrast_primary$contrast_estimate,
    hosp_contrast_estimate      = contrast_primary$contrast_estimate,
    n_hospitalizations_hospital = nrow(df_model),
    blup_available              = FALSE,
    blup_se_note                = "single-hospital — no shrinkage; use fixef_contrast for forest plot",
    site_id                     = SITE_ID,
    model_version               = re_structure
  )

} else {
  blup_df <- NULL
  warning("Hospital-level export could not be generated.")
}

if (!is.null(blup_df)) {
  cat("\nHospital-level export:\n")
  kable(blup_df, digits = 4,
        caption = "Hospital-level estimates (de-identified)")
}

# 4.9 RE variance export (primary models) ──────────────────────────────────────
# Between-hospital random intercept variance from glmer (multi-hospital path).
# Single-hospital path returns NA stubs so all sites return this file uniformly.
# Coordinating center combines within-site RE variance (this file) with
# between-site variance from meta-analytic pooling for two-level heterogeneity.
re_var_primary <- bind_rows(
  extract_re_variance(model_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("\nBetween-hospital RE variance — primary models:\n")
print(re_var_primary)
```

---

# Section 5 — Sensitivity Analyses

```{r sensitivity-sa1}
# SA1: Restrict to encounters with any lactate ordered ─────────────────────────
cat("Fitting SA1: restrict to encounters with any lactate ordered\n")

df_sa1_a <- df_model %>%
  filter(any_lactate_ordered == 1,
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa1_b <- df_model %>%
  filter(any_lactate_ordered == 1,
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

cat(paste("SA1 Model A: n =", nrow(df_sa1_a),
          "| Model B: n =", nrow(df_sa1_b), "\n"))

warn_sa1_a <- NULL; warn_sa1_b <- NULL
model_sa1_a <- fit_binary(formula_model_a, df_sa1_a, model_path, "warn_sa1_a")
model_sa1_b <- fit_binary(formula_model_b, df_sa1_b, model_path, "warn_sa1_b")

vcov_sa1_a <- if (!is.null(model_sa1_a)) get_model_vcov(model_sa1_a, model_path, df_sa1_a) else NULL
vcov_sa1_b <- if (!is.null(model_sa1_b)) get_model_vcov(model_sa1_b, model_path, df_sa1_b) else NULL

coef_sa1 <- bind_rows(
  if (!is.null(model_sa1_a)) tidy_binary(model_sa1_a, vcov_sa1_a) %>%
    mutate(model_label = "model_a", model_version = "sa1_lactate_ordered_model_a",
           site_id = SITE_ID, n_rows = nrow(df_sa1_a)),
  if (!is.null(model_sa1_b)) tidy_binary(model_sa1_b, vcov_sa1_b) %>%
    mutate(model_label = "model_b", model_version = "sa1_lactate_ordered_model_b",
           site_id = SITE_ID, n_rows = nrow(df_sa1_b))
)

contrast_sa1 <- compute_contrast(
  tidy_binary(model_sa1_a, vcov_sa1_a),
  tidy_binary(model_sa1_b, vcov_sa1_b),
  vcov_sa1_a, vcov_sa1_b
)

if (!is.null(contrast_sa1))
  contrast_sa1 <- contrast_sa1 %>%
    mutate(site_id = SITE_ID, model_version = "sa1_lactate_ordered")

re_var_sa1 <- bind_rows(
  extract_re_variance(model_sa1_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_sa1_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("SA1 complete.\n")
if (nrow(coef_sa1) > 0)
  kable(coef_sa1 %>% filter(term == "lactate_vol_scaled") %>%
          select(model_label, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA1 — lactate_vol_scaled by model")
if (!is.null(contrast_sa1))
  kable(contrast_sa1, digits = 4, caption = "SA1 — primary contrast")
```

```{r sensitivity-sa2a}
# SA2a: Exclude COVID years (2020–2021) ────────────────────────────────────────
cat("Fitting SA2a: exclude COVID years 2020-2021\n")

df_sa2a_a <- df_model %>%
  filter(!year %in% c(2020, 2021),
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa2a_b <- df_model %>%
  filter(!year %in% c(2020, 2021),
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

if (nrow(df_sa2a_a) == 0) {
  cat("SA2a: No data outside 2020-2021 — skipping.\n")
  coef_sa2a <- NULL; contrast_sa2a <- NULL; re_var_sa2a <- NULL
} else {
  cat(paste("SA2a Model A: n =", nrow(df_sa2a_a),
            "| Model B: n =", nrow(df_sa2a_b), "\n"))

  warn_sa2a_a <- NULL; warn_sa2a_b <- NULL
  model_sa2a_a <- fit_binary(formula_model_a, df_sa2a_a, model_path, "warn_sa2a_a")
  model_sa2a_b <- fit_binary(formula_model_b, df_sa2a_b, model_path, "warn_sa2a_b")

  vcov_sa2a_a <- if (!is.null(model_sa2a_a)) get_model_vcov(model_sa2a_a, model_path, df_sa2a_a) else NULL
  vcov_sa2a_b <- if (!is.null(model_sa2a_b)) get_model_vcov(model_sa2a_b, model_path, df_sa2a_b) else NULL

  coef_sa2a <- bind_rows(
    if (!is.null(model_sa2a_a)) tidy_binary(model_sa2a_a, vcov_sa2a_a) %>%
      mutate(model_label = "model_a", model_version = "sa2a_exclude_covid_model_a",
             site_id = SITE_ID, years_excluded = "2020, 2021", n_rows = nrow(df_sa2a_a)),
    if (!is.null(model_sa2a_b)) tidy_binary(model_sa2a_b, vcov_sa2a_b) %>%
      mutate(model_label = "model_b", model_version = "sa2a_exclude_covid_model_b",
             site_id = SITE_ID, years_excluded = "2020, 2021", n_rows = nrow(df_sa2a_b))
  )

  contrast_sa2a <- compute_contrast(
    tidy_binary(model_sa2a_a, vcov_sa2a_a),
    tidy_binary(model_sa2a_b, vcov_sa2a_b),
    vcov_sa2a_a, vcov_sa2a_b
  )
  if (!is.null(contrast_sa2a))
    contrast_sa2a <- contrast_sa2a %>%
      mutate(site_id = SITE_ID, model_version = "sa2a_exclude_covid")

  re_var_sa2a <- bind_rows(
    extract_re_variance(model_sa2a_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
    extract_re_variance(model_sa2a_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
  )

  cat("SA2a complete.\n")
  if (nrow(coef_sa2a) > 0)
    kable(coef_sa2a %>% filter(term == "lactate_vol_scaled") %>%
            select(model_label, estimate, std.error, p.value, conf.low, conf.high),
          digits = 4, caption = "SA2a — lactate_vol_scaled by model")
  if (!is.null(contrast_sa2a))
    kable(contrast_sa2a, digits = 4, caption = "SA2a — primary contrast")
}
```

```{r sensitivity-sa2b}
# SA2b: Year-by-year stratification (exploratory) ──────────────────────────────
cat("Fitting SA2b: year-by-year stratified models\n")

years_available <- sort(unique(df_model$year))
cat(paste("SA2b years:", paste(years_available, collapse = ", "), "\n"))

sa2b_results <- map(years_available, function(yr) {
  d_a <- df_model %>%
    filter(year == yr, patient_group %in% c("no_sepsis", "sepsis_core")) %>%
    mutate(outcome_a = as.integer(patient_group == "sepsis_core"))
  d_b <- df_model %>%
    filter(year == yr, patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
    mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

  cat(paste("SA2b year", yr, ": Model A n =", nrow(d_a),
            "| Model B n =", nrow(d_b), "\n"))

  # Drop zero-var covariates within year (year_centered always zero within a year)
  yr_zero_var <- c("hospital_type", "sex", "year_centered") %>%
    purrr::keep(~ {
      col <- d_a[[.x]]
      if (is.factor(col)) nlevels(droplevels(col)) < 2
      else length(unique(col[!is.na(col)])) < 2
    })
  yr_rhs <- c("lactate_vol_scaled",
               setdiff(covariate_terms, c(yr_zero_var, "year_centered")),
               if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL)
  yr_formula_a <- reformulate(yr_rhs, response = "outcome_a")
  yr_formula_b <- reformulate(yr_rhs, response = "outcome_b")

  warn_yr_a <- NULL; warn_yr_b <- NULL
  fit_a <- fit_binary(yr_formula_a, d_a, model_path, "warn_yr_a")
  fit_b <- fit_binary(yr_formula_b, d_b, model_path, "warn_yr_b")

  vcov_yr_a <- if (!is.null(fit_a)) get_model_vcov(fit_a, model_path, d_a) else NULL
  vcov_yr_b <- if (!is.null(fit_b)) get_model_vcov(fit_b, model_path, d_b) else NULL

  coefs <- bind_rows(
    if (!is.null(fit_a)) tidy_binary(fit_a, vcov_yr_a) %>%
      mutate(model_label = "model_a", year = yr, n_rows = nrow(d_a),
             site_id = SITE_ID, model_version = "sa2b_year_stratified"),
    if (!is.null(fit_b)) tidy_binary(fit_b, vcov_yr_b) %>%
      mutate(model_label = "model_b", year = yr, n_rows = nrow(d_b),
             site_id = SITE_ID, model_version = "sa2b_year_stratified")
  )

  contrast <- compute_contrast(
    tidy_binary(fit_a, vcov_yr_a),
    tidy_binary(fit_b, vcov_yr_b),
    vcov_yr_a, vcov_yr_b
  )
  if (!is.null(contrast))
    contrast <- contrast %>% mutate(year = yr, site_id = SITE_ID,
                                    model_version = "sa2b_year_stratified")

  re_var <- bind_rows(
    extract_re_variance(fit_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
    extract_re_variance(fit_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
  ) %>% mutate(year = yr)

  list(coefs = if (nrow(coefs) > 0) coefs else NULL, contrast = contrast,
       re_var = re_var)
})

coef_sa2b     <- bind_rows(map(sa2b_results, "coefs"))
contrast_sa2b <- bind_rows(map(sa2b_results, "contrast"))
re_var_sa2b   <- bind_rows(map(sa2b_results, "re_var"))

cat(paste("SA2b complete:", length(years_available), "years attempted.\n"))
if (nrow(coef_sa2b) > 0)
  kable(coef_sa2b %>% filter(term == "lactate_vol_scaled") %>%
          select(year, model_label, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA2b — lactate_vol_scaled by year and model")
if (nrow(contrast_sa2b) > 0)
  kable(contrast_sa2b, digits = 4, caption = "SA2b — primary contrast by year")
```

```{r sensitivity-sa3}
# SA3: Within-year centered lactate volume ─────────────────────────────────────
# Swaps lactate_vol_scaled for lactate_volume_centered; drops year_centered.
cat("Fitting SA3: within-year centered lactate volume\n")

sa3_rhs       <- c("lactate_volume_centered",
                    setdiff(covariate_terms, "year_centered"),
                    if (model_path == "glmer") "(1 | hospital_id_deident)" else NULL)
formula_sa3_a <- reformulate(sa3_rhs, response = "outcome_a")
formula_sa3_b <- reformulate(sa3_rhs, response = "outcome_b")

df_sa3_a <- df_model %>%
  filter(!is.na(lactate_volume_centered),
         patient_group %in% c("no_sepsis", "sepsis_core")) %>%
  mutate(outcome_a = as.integer(patient_group == "sepsis_core"))

df_sa3_b <- df_model %>%
  filter(!is.na(lactate_volume_centered),
         patient_group %in% c("no_sepsis", "sepsis_extended")) %>%
  mutate(outcome_b = as.integer(patient_group == "sepsis_extended"))

if (nrow(df_sa3_a) < nrow(filter(df_model,
                                   patient_group %in% c("no_sepsis","sepsis_core"))))
  warning("SA3: rows dropped due to missing lactate_volume_centered.")

warn_sa3_a <- NULL; warn_sa3_b <- NULL
model_sa3_a <- fit_binary(formula_sa3_a, df_sa3_a, model_path, "warn_sa3_a")
model_sa3_b <- fit_binary(formula_sa3_b, df_sa3_b, model_path, "warn_sa3_b")

vcov_sa3_a <- if (!is.null(model_sa3_a)) get_model_vcov(model_sa3_a, model_path, df_sa3_a) else NULL
vcov_sa3_b <- if (!is.null(model_sa3_b)) get_model_vcov(model_sa3_b, model_path, df_sa3_b) else NULL

coef_sa3 <- bind_rows(
  if (!is.null(model_sa3_a)) tidy_binary(model_sa3_a, vcov_sa3_a) %>%
    mutate(model_label = "model_a", model_version = "sa3_centered_lactate_model_a",
           centering_method = centering_method, site_id = SITE_ID),
  if (!is.null(model_sa3_b)) tidy_binary(model_sa3_b, vcov_sa3_b) %>%
    mutate(model_label = "model_b", model_version = "sa3_centered_lactate_model_b",
           centering_method = centering_method, site_id = SITE_ID)
)

# Contrast uses lactate_volume_centered as the term
contrast_sa3 <- compute_contrast(
  tidy_binary(model_sa3_a, vcov_sa3_a),
  tidy_binary(model_sa3_b, vcov_sa3_b),
  vcov_sa3_a, vcov_sa3_b,
  lactate_term = "lactate_volume_centered"
)
if (!is.null(contrast_sa3))
  contrast_sa3 <- contrast_sa3 %>%
    mutate(site_id = SITE_ID, model_version = "sa3_centered_lactate",
           centering_method = centering_method)

re_var_sa3 <- bind_rows(
  extract_re_variance(model_sa3_a, "model_a_core_vs_nosepsis",     model_path, SITE_ID),
  extract_re_variance(model_sa3_b, "model_b_extended_vs_nosepsis", model_path, SITE_ID)
)

cat("SA3 complete.\n")
if (nrow(coef_sa3) > 0)
  kable(coef_sa3 %>% filter(grepl("lactate", term)) %>%
          select(model_label, term, estimate, std.error, p.value, conf.low, conf.high),
        digits = 4, caption = "SA3 — lactate terms by model")
if (!is.null(contrast_sa3))
  kable(contrast_sa3, digits = 4, caption = "SA3 — primary contrast")
```

---

# Section 6 — Output Assembly & Export

```{r export-compile}
# 6.1 Compile output list
output_list <- list(
  site_id              = SITE_ID,
  model_version_used   = re_structure,
  model_path           = model_path,
  interaction_type     = interaction_type,
  n_hospitals          = n_hospitals,
  n_hospitalizations   = nrow(df_model),
  n_dropped_check_dq   = n_check_dq,
  cor_lactate_year     = cor_lactate_year,
  dropped_covariates   = zero_var_covariates,
  lactate_mean         = lactate_center,
  lactate_sd           = lactate_scale,
  year_center          = year_center,
  centering_method     = centering_method,
  coef_primary         = coef_primary,
  vcov_model_a         = vcov_a,
  vcov_model_b         = vcov_b,
  contrast_primary     = contrast_primary,
  blup_hospital        = blup_df,
  cohort_summary       = cohort_summary,
  ase_rate_by_year     = ase_rate_by_year,
  hosp_year_summary    = hosp_year_summary,
  hosp_year_detail     = hosp_year_detail,
  hosp_year_ase        = hosp_year_ase,
  group_summary        = group_summary,
  group_clinical       = group_clinical,
  coef_sa1             = coef_sa1,
  contrast_sa1         = contrast_sa1,
  coef_sa2a            = coef_sa2a,
  contrast_sa2a        = contrast_sa2a,
  coef_sa2b            = coef_sa2b,
  contrast_sa2b        = contrast_sa2b,
  coef_sa3             = coef_sa3,
  contrast_sa3         = contrast_sa3,
  re_var_primary       = re_var_primary,
  re_var_sa1           = re_var_sa1,
  re_var_sa2a          = re_var_sa2a,
  re_var_sa2b          = re_var_sa2b,
  re_var_sa3           = re_var_sa3,
  fig_lactate_trend    = fig_lactate_trend,
  fig_ase_gap          = fig_ase_gap,
  fig_group_dist       = fig_group_dist,
  fig_clinical_profile = fig_clinical_profile
)

# 6.2 Export CSVs
write_csv(baseline_completeness,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_01_baseline_completeness.csv")))
write_csv(qc_table,
          file.path(OUTPUT_DIR, "diagnostics",
               paste0(SITE_ID, "_02_patient_group_qc.csv")))
write_csv(
  tibble(site_id = SITE_ID, cor_lactate_year = cor_lactate_year,
         collinearity_flag = abs(cor_lactate_year) > 0.7),
  file.path(OUTPUT_DIR, "diagnostics",
       paste0(SITE_ID, "_03_cor_lactate_year.csv")))

write_csv(cohort_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_01_cohort_summary.csv")))
write_csv(ase_rate_by_year,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_02_ase_rate_by_year.csv")))
write_csv(hosp_year_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_03_hosp_year_lactate_summary.csv")))
write_csv(hosp_year_detail,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_04_hosp_year_lactate_detail.csv")))
write_csv(hosp_year_ase,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_05_hosp_year_ase_rates.csv")))
write_csv(group_summary,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_06_patient_group_distribution.csv")))
write_csv(group_clinical,
          file.path(OUTPUT_DIR, "tables", paste0(SITE_ID, "_07_clinical_profile_by_group.csv")))

write_if(coef_primary,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_08_primary_model_coefs.csv")))
write_if(contrast_primary,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_09_primary_contrast.csv")))
write_if(blup_df,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_10_hospital_level_blups.csv")))
write_if(coef_sa1,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_11_sa1_lactate_ordered_coefs.csv")))
write_if(contrast_sa1,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_12_sa1_lactate_ordered_contrast.csv")))
write_if(coef_sa2a,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_13_sa2a_exclude_covid_coefs.csv")))
write_if(contrast_sa2a,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_14_sa2a_exclude_covid_contrast.csv")))
write_if(coef_sa2b,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_15_sa2b_year_stratified_coefs.csv")))
write_if(contrast_sa2b,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_16_sa2b_year_stratified_contrast.csv")))
write_if(coef_sa3,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_17_sa3_centered_lactate_coefs.csv")))
write_if(contrast_sa3,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_18_sa3_centered_lactate_contrast.csv")))

# vcov exported as separate CSVs for coordinating center use
if (!is.null(vcov_a))
  write_csv(as.data.frame(vcov_a),
            file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_19_vcov_model_a.csv")))
if (!is.null(vcov_b))
  write_csv(as.data.frame(vcov_b),
            file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_20_vcov_model_b.csv")))

# RE variance exports — between-hospital sigma^2 from glmer (NAs for single-hospital path)
write_if(re_var_primary,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_21_re_variance_primary.csv")))
write_if(re_var_sa1,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_22_re_variance_sa1.csv")))
write_if(re_var_sa2a,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_23_re_variance_sa2a.csv")))
write_if(re_var_sa2b,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_24_re_variance_sa2b.csv")))
write_if(re_var_sa3,
         file.path(OUTPUT_DIR, "models", paste0(SITE_ID, "_25_re_variance_sa3.csv")))

cat("CSV exports complete.\n")

# 6.3 RDS + JSON
saveRDS(output_list,
        file = file.path(OUTPUT_DIR, "models",
                    paste0(SITE_ID, "_ASE_results.rds")))

output_json <- output_list
output_json[c("fig_lactate_trend", "fig_ase_gap",
              "fig_group_dist", "fig_clinical_profile")] <- NULL
output_json$vcov_model_a <- if (!is.null(vcov_a)) as.data.frame(vcov_a) else NULL
output_json$vcov_model_b <- if (!is.null(vcov_b)) as.data.frame(vcov_b) else NULL

write_json(output_json,
           path       = file.path(OUTPUT_DIR, "models",
                             paste0(SITE_ID, "_ASE_results.json")),
           pretty     = TRUE, auto_unbox = TRUE, na = "null")

cat("RDS and JSON exports complete.\n")
cat(paste0("All outputs saved to ", OUTPUT_DIR, " — share entire folder with coordinating center.\n"))
```

---

# Session Info

```{r session-info}
writeLines(capture.output(sessionInfo()),
           file.path(OUTPUT_DIR, "diagnostics",
                paste0(SITE_ID, "_session_info.txt")))
sessionInfo()
```

---

# Output File Summary

The following files have been saved to the `<output_directory>/` directory (as configured in `clif_config.json`) for return to the coordinating center.

**Diagnostics (return all):**

- `<output_directory>/diagnostics/[SITE]_01_baseline_completeness.csv`
- `<output_directory>/diagnostics/[SITE]_02_patient_group_qc.csv`
- `<output_directory>/diagnostics/[SITE]_03_cor_lactate_year.csv`
- `<output_directory>/diagnostics/[SITE]_session_info.txt`

**Tables (return all):**

- `<output_directory>/tables/[SITE]_01_cohort_summary.csv`
- `<output_directory>/tables/[SITE]_02_ase_rate_by_year.csv`
- `<output_directory>/tables/[SITE]_03_hosp_year_lactate_summary.csv`
- `<output_directory>/tables/[SITE]_04_hosp_year_lactate_detail.csv` — hospital-year detail ⭐
- `<output_directory>/tables/[SITE]_05_hosp_year_ase_rates.csv` — hospital-year ASE rates ⭐
- `<output_directory>/tables/[SITE]_06_patient_group_distribution.csv`
- `<output_directory>/tables/[SITE]_07_clinical_profile_by_group.csv`

**Models (return all):**

- `<output_directory>/models/[SITE]_08_primary_model_coefs.csv` — coefficients, both models ⭐
- `<output_directory>/models/[SITE]_09_primary_contrast.csv` — **primary estimand** ⭐
- `<output_directory>/models/[SITE]_10_hospital_level_blups.csv` — hospital-level forest plot inputs ⭐
- `<output_directory>/models/[SITE]_11_sa1_lactate_ordered_coefs.csv`
- `<output_directory>/models/[SITE]_12_sa1_lactate_ordered_contrast.csv`
- `<output_directory>/models/[SITE]_13_sa2a_exclude_covid_coefs.csv`
- `<output_directory>/models/[SITE]_14_sa2a_exclude_covid_contrast.csv`
- `<output_directory>/models/[SITE]_15_sa2b_year_stratified_coefs.csv`
- `<output_directory>/models/[SITE]_16_sa2b_year_stratified_contrast.csv`
- `<output_directory>/models/[SITE]_17_sa3_centered_lactate_coefs.csv`
- `<output_directory>/models/[SITE]_18_sa3_centered_lactate_contrast.csv`
- `<output_directory>/models/[SITE]_19_vcov_model_a.csv` — vcov for Model A (coordinating center use)
- `<output_directory>/models/[SITE]_20_vcov_model_b.csv` — vcov for Model B (coordinating center use)
- `<output_directory>/models/[SITE]_21_re_variance_primary.csv` — between-hospital RE variance, primary models (glmer: sigma^2 + sigma; glm: NA stubs) ⭐
- `<output_directory>/models/[SITE]_22_re_variance_sa1.csv` — RE variance, SA1 (lactate ordered only)
- `<output_directory>/models/[SITE]_23_re_variance_sa2a.csv` — RE variance, SA2a (exclude COVID years)
- `<output_directory>/models/[SITE]_24_re_variance_sa2b.csv` — RE variance, SA2b (year-stratified, one row per year per model)
- `<output_directory>/models/[SITE]_25_re_variance_sa3.csv` — RE variance, SA3 (centered lactate)
- `<output_directory>/models/[SITE]_ASE_results.rds` — full output bundle ⭐
- `<output_directory>/models/[SITE]_ASE_results.json`

**Figures (return if flagged issues):**

- `<output_directory>/figures/[SITE]_fig1_lactate_ase_trend.png`
- `<output_directory>/figures/[SITE]_fig2_ase_rate_gap.png`
- `<output_directory>/figures/[SITE]_fig3_patient_group_distribution.png`
- `<output_directory>/figures/[SITE]_fig4_clinical_profile.png`

**Do NOT share (local only):**

- Hospital de-identification crosswalk (printed to console only)
